\documentclass[10pt]{article}
\usepackage{amssymb,amsfonts,mathrsfs,amsmath,amsthm,mathtools,bm,dsfont, thmtools}\allowdisplaybreaks
\usepackage[dvipsnames]{xcolor}
\usepackage{array, graphicx, graphics,float,multirow,tabularx,tikz,pgfplots, ctable, longtable, threeparttable}
\usepackage[top=1.25in, bottom=1.25in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
%\usepackage[sort]{natbib}
%\usepackage{bibentry}
\usepackage{bibentry, natbib} % reference
\usepackage{paralist}  % intermize and enumerate as paragraph
\usepackage{appendix} % appendix
\usepackage{setspace}
\usepackage[hang,flushmargin]{footmisc} % no indent in footnote
\usepackage{mathrsfs}
\usepackage{appendix}
\usepackage{enumitem}
%\usepackage{authblk}
\usepackage[font=small]{caption}
\usepackage{titlesec}
\usepackage{textcase,relsize}

\usepackage{wrapfig}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{epstopdf}
\usepackage{lscape}

\usepackage{adjustbox}
\usepackage{lipsum}% example text
\usepackage{siunitx}
\usepackage{appendix}


\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}} 
\newenvironment{Hblue}[1]{{\color{blue}#1}}

\setlength{\bibsep}{0pt plus 0.3ex}

\makeatletter
\def\blfootnote{\xdef\@thefnmark{}\@footnotetext}
\makeatother

%\textheight=21cm
%\def\baselinestretch{1.2}

\textwidth=6in
\oddsidemargin=0cm \evensidemargin=0cm
\topmargin=-20pt
\numberwithin{equation}{section}
\baselineskip=100pt
\textheight=21cm
\def\baselinestretch{1.5}

\begin{document}

			%Appendix
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------		
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------	
			
    \begin{center} {\bf \Large{Supplemental Appendix for ``Macroeconomic and Financial Uncertainty Measures in a Big Data Environment''}}
    	
    	
    		\bigskip
    	
    	Weijia Peng$^1$, Norman R. Swanson$^2$, Xiye Yang$^2$, Chun Yao$^3$\\
    	%EndAName
    	{$^1$Sacred Heart University, $^{2}$Rutgers University and $^{3}$Barclays}
    	\bigskip
    	
    	{October 2023}
    	
    	\bigskip
    	
    	Abstract
    	
    	
      \end{center}  
  	
  {\footnotesize This Supplemental Appendix contains a more detailed description of the state space modeling framework used in the paper, followed by a discussion of the methods used to address temporal aggregation of our stock and flow variables. Thereafter, supplemental tables are collected. These tables summarize various forecast accuracy and model confidence set results for a variety of ``target variables'' that are not included in the main paper (Tables A1a-B6B). These target variables include IP, PAY, CPI, PCE, SI, and HS. Additional tabulated results are also included for 12- and 24-month forecast horizons, for the HS variable (Tables RR1-RR3). Longer horizon forecasting results for the other variables are available upon request from the authors.\blfootnote{\scriptsize \noindent $^{\ast }$ Weijia Peng, Department of Finance, Jack Welch College of Business \& Technology, Sacred Heart University, 5151 Park Avenue Fairfield, CT 06825, USA, pengw@sacredheart.edu; Norman R. Swanson, Department of Economics, Rutgers University, 75 Hamilton Street, New Brunswick, NJ 08901, USA, nswanson@economics.rutgers.edu; Xiye Yang, Department of Economics, Rutgers University, 75 Hamilton Street, New Brunswick, NJ 08901, USA, 
  		xiyeyang@economics.rutgers.edu; Chun Yao, US Economics Research, Barclays, 745 Seventh Avenue, New York, NY 10019, USA, chunyao.economics@gmail.com. We are grateful to the editor, Janine Illian, the associate editor, two anonymous referees, Mingmian Cheng, Valentina Corradi, Frank Diebold, Xu Jiang, Hyun Hak Kim, Yuan Liao, and Greg Tkacz for useful comments and suggestions on the topics explored in this paper. The views expressed here are those of the authors and not necessarily those of any affiliated institution. Declarations of interest: none.} 
   }
  		\bigskip	
    	

 	   	
    	
			\renewcommand{\baselinestretch}{1.4}%
%TCIMACRO{\TeXButton{nomalsize}{\normalsize{}}}%
%BeginExpansion
\normalsize{}%
%EndExpansion
\thispagestyle{empty}
\setcounter {page} {0}\newpage

\bigskip

\section{Further notes on the state space model used in the main paper}

We begin by providing details on our state space modeling setup and our factor estimation procedure. State-space modeling and Kalman factor have been extensively discussed in literature (see e.g. \cite{anderson2012optimal}, \cite{cargnoni1997bayesian}, \cite{prado2010time}, \cite{westharrison1997}. Since our setup involves mixed frequency input signals, missing values can occur in the signal vector $y_t$. Despite this, the state equation will continue to update the state variable based on the state equation alone, assuming no new information in the signal equation. Therefore, the estimation of this state space model with mixed frequency signals is similar to the universal frequency case, with some accommodation made for missing values from lower frequency variables.\\

Let $y_t^*$ denote a mixed-frequency dataset and let the corresponding signal vector be denoted by $y_t = [y_t^{d}, y_t^{2d}, y_t^{3d}, y_t^{w}]'$. In the univariate frequency setup, we have $y_t^* = y_t$, whereas in the mixed frequency setup, we have $y_t^*=M_ty_t$, where the elements of the matrix $M_t$ are 0 for missing values in the signal vector and 1 for non-missing values. The estimation procedure for the mixed-frequency model is similar to the univariate scenario. Specifically, we let $S_t$ be a $m \times q$ vector of state variables, and for $t = 1, \cdots, T$, the state space model can be compactly expressed as:

\begin{equation}
	y_t^* = H^* S_t
\end{equation}
\begin{equation}
	S_{t+1} = A S_t + B \eta_t, 
\end{equation}

where $\eta_t \overset{i.i.d.}\sim N(0,Q)$. When observation $y_t$ becomes available in the standard state space model, the joint distribution between $\displaystyle y_t-E(y_t|y_{t-1})$ and $S_t$ updates $S_{t|t}$, where we use the notation \textquotedblleft $|t$\textquotedblright{} to denote conditional expectation with respect to the filtration at period $t$. The state equation then yields $S_{t+1}$. By incorporating the mapping from $y_t$ to $y_t^*$, we can apply the estimation procedure used in the standard state space model to our mixed-frequency dataset. More specifically, we have
\begin{align}
	y_t^* = \displaystyle M_ty_t, \quad H^* = \displaystyle M_tH_t .  %, \quad  \beta_t^* = \displaystyle M_t\beta_t.
\end{align}
Then, similar to the standard state space model, we obtain the following joint distribution:
\begin{align}
	\begin{pmatrix}
		S_{t}\\
		y_t^*-E(y_t^*|y_{t-1}^*)
	\end{pmatrix} \sim  N\left[\left(\begin{array}{c}
		S_{t|t -1}\\
		0
	\end{array}\right),\left(\begin{array}{cc}
		P_t H^{*'} & P_t H^{*'} \\
		P_t H^{*'} & V_t 
	\end{array}\right)\right],
\end{align}
where $P_t$ denotes the variance of $S_t$ given $y_{t-1}^*$, and $V_t$ denotes the variance of $y_t^*-E(y_t^*|y_{t-1}^*)$. (Refer to \cite{anderson2012optimal} for a detailed derivation of the mean, covariance, and variance in the above discussion.) From the joint distribution of these variables, we obtain:
\begin{equation}
	\alpha_{t|t} = S_t + P_t H^{*'} F_t^{-1} [y_t^*-E(y_t^*|y_{t-1}^*)]
\end{equation}
\begin{equation}
	P_{t|t} = P_t + P_t H^{*'} F_t^{-1} H P_t^{'}.
\end{equation}
According to the state equation, we can then forecast the next step state vector as:
\begin{equation}
	\alpha_{t+1} = A \alpha_{t|t}
\end{equation}
\begin{equation}
	P_{t+1} = A P_t A'+ BQB'
\end{equation}
Alternatively, when $y_{t}$ has missing values due to different updating frequencies, the state vector will not update and instead adheres to the following law of motion:
\begin{equation}
	\alpha_{t+1} = A \alpha_{t}
\end{equation}
\begin{equation}
	P_{t+1} = A P_t A'+ BQB'.
\end{equation}

To match our monthly forecasting experiment of macroeconomic variables, we perform a model and factor re-estimation every month. Sequentially updating initial parameters with values from the previous month's estimation as prior. 
As an example, consider the setup for our volatility factors (MFV), where matrices $H$ and A can be expressed as follows\footnote{Details about the MFV state space model and parameter matrices are given in Section 2.3 of the paper.}:

\begin{align}
	\small
	\begin{array}{l}
		H
	\end{array} =
	\left(\begin{array}{llllllll}
		\beta_{1} & 0& 0& 0& 1& 0& 0& 0\\
		0& \beta_{2}& 0& 0& 0& 1& 0& 0\\
		0& 0& \beta_{3}& 0& 0& 0& 1& 0 \\
		0& 0& 0& \beta_{4} & 0& 0& 0& 1\\
	\end{array}\right)
\end{align}


\begin{align}
	\small
	\begin{array}{l}
		A
	\end{array} =
	\left(\begin{array}{llllllll}
		\rho & 0& 0& 0& 0& 0& 0& 0\\
		\rho & \psi_{t+1}^1& 0& 0& 0& 0& 0& 0\\
		\rho & 0& \psi_{t+1}^2& 0& 0& 0& 0& 0\\
		\rho & 0& 0& \psi_{t+1}^3& 0& 0& 0& 0\\
		0 & 0& 0& 0 & \eta_{1}& 0& 0& 0\\
		0 & 0& 0& 0 &0& \eta_{2}& 0& 0\\
		0 & 0& 0& 0 &0& 0& \eta_{3}& 0\\
		0 & 0& 0& 0 &0& 0& 0& \eta_{4}
	\end{array}\right)
\end{align} 

Matrices $H$ and $A$ involve several parameters of interest that need to be estimated, namely $\beta_{1}$, $\beta_{2}$, $\beta_{3}$, $\beta_{4}$, $\rho$, $\eta_{1}$, $\eta_{2}$, $\eta_{3}$, and $\eta_{4}$. To estimate these parameters and extract the factor, we use the following procedure:

1) Estimate the state space model using the initial $k$ months of data with respect to equation (1) to (10), where $k$ is set to 36 in our study, and initial parameters $\beta_{1}^{(0)}$, $\beta_{2}^{(0)}$, $\beta_{3}^{(0)}$, $\beta_{4}^{(0)}$, $\rho^{(0)}$, $\eta_{1}^{(0)}$, $\eta_{2}^{(0)}$, $\eta_{3}^{(0)}$, $\eta_{4}^{(0)}$. 

2) For months $k+1, k+2, \cdots, k+i, \cdots$, where $i=1,2,\cdots,m$ and $k+m$ denotes the last month of sample data, we re-estimate the parameters after each month using priors based on the previous round:

a) set $\beta_{1}^{(i)}$, $\beta_{2}^{(i)}$, $\beta_{3}^{(i)}$, $\beta_{4}^{(i)}$, $\rho^{(i)}$, $\eta_{1}^{(i)}$, $\eta_{2}^{(i)}$, $\eta_{3}^{(i)}$, $\eta_{4}^{(i)}$ to $\hat\beta_{1}^{(i-1)}$, $\hat\beta_{2}^{(i-1)}$, $\hat\beta_{3}^{(i-1)}$, $\hat\beta_{4}^{(i-1)}$, $\hat\rho^{(i-1)}$, $\hat\eta_{1}^{(i-1)}$, $\hat\eta_{2}^{(i-1)}$, $\hat\eta_{3}^{(i-1)}$, $\hat\eta_{4}^{(i-1)}$, where the parameters with $(i-1)$ notation represent estimated values from the previous round of estimation

b) estimate parameter values via BFGS algorithm

c) extract the common factor ${MF}_{t}^{vol}$ using the Kalman smoother 
\\

\section{Temporal Aggregation}
			
			The temporal aggregation of variables of different frequencies and the stock and flow features of the variables that we examine have been discussed in previous research, such as \cite{aruoba2009real} and \cite{aruoba2009updates}. It is important to address these issues in the specification of our state space models.
			
			We first differentiate between flow and stock variables and consider their impact on our state space models. Flow variables are accumulated within each period, while stock variables reflect quantities measured at a particular point in time. When the state space model is evolving at a higher frequency than the flow variable, accumulated values can result in regular shocks to the state variable. For instance, if the state space model is evolving at a daily frequency, and we observe a monthly flow variable, its accumulated values over the past 30 days will result in a shock to the state variable each time a new value is updated. To account for this, proper incorporation of flow variable observations into the system is necessary for accurate estimation of the latent factors.
			
			For stock variables, this complication does not arise. The observed value for a stock variable can simply be expressed as a function of the current state variable and the stochastic disturbance term. As an example, let ${F}_{t}$ denote the state variable at time $t$, and let the stock variable be $y_{t}^s$, then:
			\begin{align}
			y_{t}^s=\beta F_{t}+u_{t},
			\end{align}
			where $F_t$ is state variable, and $u_t$ is a stochastic disturbance term. 
			
			On the other hand, and as discussed above, the value of flow variables reflects the aggregated value through each time period. Thus, flow variable $y_{t}^f$ can be defined as follows:
			\begin{align}
			y_{t}^f=\sum_{i=0}^{K_{j}-1} y_{t-i}^f,
		\end{align}
			where indices $i$ and $j$ denote the $i^{th}$ time point within the $j^{th}$ observational interval, and $K_{j}$ is the length of the interval between two observational time points (i.e., time points for which observations are available - namely, between the $(j-1)^{th}$ and $j^{th}$ time points).
			Since the value of flow variable is inter-temporally accumulated over a given period of time, one straightforward way to handle inter-temporal aggregation is by defining a state vector that sums all lags of states within each period. For example, a monthly flow variable in a daily state space model can be specified as:
		\begin{align}
			y_{t}^f=\beta (F_{t}+F_{t-1}+F_{t-2}+\cdots+F_{t-m})+u_{t},
		\end{align}
			where $F_t$, $F_{t-1}$,$\cdots$, $F_{t-m}$ are state variable components, and $u_t$ is a stochastic disturbance term.
			
			However, given that our state space is evolving at a daily frequency, and the lowest frequency flow variable is quarterly real GDP, this approach will result in the specification of a very large state variable with more than 90 lag terms, and a large number of parameters to be estimated, causing excessive calculation and convergence issues. For this reason, we instead implement the aggregated states approach of \cite{aruoba2009updates} in order to account for flow variables in our system. Namely, we define
			\begin{align}
			y_{t}^f=\beta{C}_{t}+\gamma y_{t-M}^f+w_{t},
			\end{align}
			where ${C}_{t}$ is a latent state variable defined specifically for flow variables, $M$ is the observational lag length, and the $w_{t}$ are serially uncorrelated error terms. Here, ${C}_{t}$ sums over its past values within the observational period of the flow variables. Namely,  
		\begin{align}
		{C}_{t+1} = \psi_{t+1}{C}_{t} + \rho{F}_{t}, 
			\end{align}
			where
			\begin{center}
				$\psi_{t}= \displaystyle
				\begin{cases}
				0, & \text{if $t$ is the first observation of the period } \\
				1, & \text{otherwise},
				\end{cases}$ 
			\end{center} 
			and where $\psi_{t}$ is an indicator that controls for the observational frequency of the flow variable. Hence, if a flow variable is updated at time $t$, then the value of ${C}_{t+1}$ will be refreshed to be $0 + \rho{F}_{t}$, while if a flow variable is not updated at time $t$, then ${C}_{t+1} = {C}_{t} + \rho{F}_{t}$, which includes its past value in the sum.
			
			
			%\begin{center} {\Large{Appendix: Additional Tables}}

			
			%\newpage

			\renewcommand{\thetable}{A1A} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Industrial Production (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA1A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							AR  & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 \\
							MMF  & 1.013\textsuperscript{ } & 1.003\textsuperscript{**} & 0.979\textsuperscript{***} & \textbf{1.01\textsuperscript{ }} & 1.199\textsuperscript{***} & 1.022\textsuperscript{ } \\
							RV   & 1.007\textsuperscript{*} & 0.958\textsuperscript{***} & 1.089\textsuperscript{ } & 1.225\textsuperscript{***} & 1.089\textsuperscript{***} & 1\textsuperscript{***} \\
							TRV   & 1.009\textsuperscript{*} & 0.966\textsuperscript{***} & 1.112\textsuperscript{**} & 1.215\textsuperscript{***} & 1.084\textsuperscript{***} & \textbf{0.997\textsuperscript{***}} \\
							BPV  & 0.999\textsuperscript{***} & 0.953\textsuperscript{***} & 1.069\textsuperscript{ } & 1.225\textsuperscript{***} & 1.1\textsuperscript{***} & 1.005\textsuperscript{ } \\
							JV  & 2.902\textsuperscript{***} & 2.798\textsuperscript{***} & 2.289\textsuperscript{***} & 1.902\textsuperscript{***} & 1.828\textsuperscript{***} & 1.816\textsuperscript{***} \\
							CMRV1   & 1.004\textsuperscript{*} & 1.05\textsuperscript{ } & 1.043\textsuperscript{ } & 1.155\textsuperscript{***} & 1.08\textsuperscript{***} & 1.074\textsuperscript{***} \\
							CMTRV1   & \textbf{0.987\textsuperscript{***}} & 1.059\textsuperscript{***} & 1.031\textsuperscript{***} & 1.032\textsuperscript{***} & 1.081\textsuperscript{***} & 1.071\textsuperscript{***} \\
							CMBPV1   & 1.005\textsuperscript{*} & 1.046\textsuperscript{ } & 1.042\textsuperscript{ } & 1.152\textsuperscript{***} & 1.085\textsuperscript{***} & 1.074\textsuperscript{***} \\
							CMJV1  & 1.043\textsuperscript{ } & 1.112\textsuperscript{***} & 1.097\textsuperscript{***} & 1.064\textsuperscript{***} & 1.021\textsuperscript{ } & 1.103\textsuperscript{***} \\
							CMRV2   & 1.026\textsuperscript{ } & 1.114\textsuperscript{***} & 1.034\textsuperscript{***} & 1.019\textsuperscript{ } & 1.09\textsuperscript{***} & 1.037\textsuperscript{***} \\
							CMTRV2   & 1.013\textsuperscript{ } & 1.053\textsuperscript{***} & 1.037\textsuperscript{***} & 1.046\textsuperscript{***} & 1.031\textsuperscript{ } & 1.071\textsuperscript{***} \\
							CMBPV2  & 1.024\textsuperscript{ } & 1.082\textsuperscript{***} & 1.052\textsuperscript{***} & 1.025\textsuperscript{ } & 1.059\textsuperscript{***} & 1.047\textsuperscript{***} \\
							CMJV2  & 1.053\textsuperscript{ } & 1.004\textsuperscript{*} & 1.048\textsuperscript{ } & 1.036\textsuperscript{ } & \textbf{0.973\textsuperscript{***}} & 1.089\textsuperscript{***} \\
							VRV   & 1.028\textsuperscript{ } & 1.108\textsuperscript{**} & 1.037\textsuperscript{ } & 1.038\textsuperscript{ } & 1.045\textsuperscript{***} & 1.055\textsuperscript{***} \\
							VTRV  & 1.03\textsuperscript{ } & 1.106\textsuperscript{*} & 1.025\textsuperscript{ } & 1.045\textsuperscript{ } & 1.046\textsuperscript{***} & 1.052\textsuperscript{***} \\
							VBPV   & 1.028\textsuperscript{ } & 1.109\textsuperscript{*} & 1.046\textsuperscript{ } & 1.035\textsuperscript{ } & 1.046\textsuperscript{***} & 1.058\textsuperscript{***} \\
							VJV  & 1.123\textsuperscript{ } & 1.024\textsuperscript{ } & 0.984\textsuperscript{***} & 1.017\textsuperscript{ } & 1.028\textsuperscript{***} & 1.025\textsuperscript{ } \\
							MRV  & 1.107\textsuperscript{ } & 1.045\textsuperscript{ } & 1.219\textsuperscript{***} & 1.284\textsuperscript{***} & 1.335\textsuperscript{***} & 1.133\textsuperscript{***} \\
							MTRV  & 1.11\textsuperscript{ } & 1.06\textsuperscript{ } & 1.234\textsuperscript{***} & 1.285\textsuperscript{***} & 1.339\textsuperscript{***} & 1.134\textsuperscript{***} \\
							MBPV   & 1.104\textsuperscript{ } & 1.034\textsuperscript{ } & 1.198\textsuperscript{***} & 1.292\textsuperscript{***} & 1.338\textsuperscript{***} & 1.132\textsuperscript{***} \\
							MJV   & 1.337\textsuperscript{***} & 1.481\textsuperscript{***} & 1.32\textsuperscript{***} & 1.275\textsuperscript{***} & 1.455\textsuperscript{***} & 1.36\textsuperscript{***} \\
							MVRV  & 1.164\textsuperscript{***} & 0.957\textsuperscript{***} & \textbf{0.952\textsuperscript{***}} & 1.04\textsuperscript{ } & 1.226\textsuperscript{***} & 1.06\textsuperscript{ } \\
							MVTRV   & 1.169\textsuperscript{***} & 0.957\textsuperscript{***} & 0.959\textsuperscript{***} & 1.043\textsuperscript{ } & 1.219\textsuperscript{***} & 1.056\textsuperscript{ } \\
							MVBPV  & 1.158\textsuperscript{***} & 0.97\textsuperscript{***} & 0.953\textsuperscript{***} & 1.041\textsuperscript{ } & 1.228\textsuperscript{***} & 1.062\textsuperscript{ } \\
							MVJV   & 1.13\textsuperscript{***} & \textbf{0.939\textsuperscript{***}} & 0.973\textsuperscript{***} & 1.047\textsuperscript{ } & 1.209\textsuperscript{***} & 1.066\textsuperscript{ } \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 \\
							MMF  & \textbf{0.954\textsuperscript{***}} & 1.014\textsuperscript{ } & 0.945\textsuperscript{***} & 0.956\textsuperscript{***} & 0.993\textsuperscript{***} & 0.949\textsuperscript{***} \\
							RV   & 1.068\textsuperscript{*} & 1.028\textsuperscript{ } & 1.022\textsuperscript{ } & 1.029\textsuperscript{ } & 1.012\textsuperscript{ } & 0.99\textsuperscript{***} \\
							TRV   & 1.079\textsuperscript{***} & 1.051\textsuperscript{ } & 1.032\textsuperscript{ } & 1.028\textsuperscript{ } & 1.012\textsuperscript{ } & 0.982\textsuperscript{***} \\
							BPV  & 1.07\textsuperscript{*} & 1.031\textsuperscript{ } & 1.029\textsuperscript{ } & 1.034\textsuperscript{ } & 1.014\textsuperscript{ } & 0.992\textsuperscript{***} \\
							JV  & 2.524\textsuperscript{***} & 1.877\textsuperscript{***} & 1.647\textsuperscript{***} & 1.751\textsuperscript{***} & 1.396\textsuperscript{***} & 1.197\textsuperscript{***} \\
							CMRV1   & 1.039\textsuperscript{***} & 1.012\textsuperscript{ } & 0.951\textsuperscript{***} & 1.018\textsuperscript{ } & 0.967\textsuperscript{***} & 1.008\textsuperscript{ } \\
							CMTRV1   & 1.157\textsuperscript{***} & 1.013\textsuperscript{ } & 1.004\textsuperscript{*} & 1.063\textsuperscript{ } & 1.052\textsuperscript{ } & 1.102\textsuperscript{***} \\
							CMBPV1   & 1.037\textsuperscript{***} & 1.012\textsuperscript{ } & 0.94\textsuperscript{***} & 1.02\textsuperscript{ } & 0.966\textsuperscript{***} & 1.009\textsuperscript{ } \\
							CMJV1  & 1.042\textsuperscript{***} & 1.013\textsuperscript{ } & 0.976\textsuperscript{***} & 0.97\textsuperscript{***} & 0.958\textsuperscript{***} & 0.995\textsuperscript{***} \\
							CMRV2   & 1.213\textsuperscript{***} & \textbf{0.985\textsuperscript{***}} & 0.955\textsuperscript{***} & 1.059\textsuperscript{ } & 1.005\textsuperscript{*} & 1.084\textsuperscript{***} \\
							CMTRV2   & 1.12\textsuperscript{***} & 1.085\textsuperscript{***} & 1.057\textsuperscript{ } & 1.059\textsuperscript{ } & 1.097\textsuperscript{***} & 1.128\textsuperscript{***} \\
							CMBPV2  & 1.144\textsuperscript{***} & 1.063\textsuperscript{ } & 1.015\textsuperscript{ } & 1.045\textsuperscript{ } & 1.038\textsuperscript{ } & 1.097\textsuperscript{***} \\
							CMJV2  & 0.992\textsuperscript{***} & 1.01\textsuperscript{ } & 1.006\textsuperscript{ } & 0.939\textsuperscript{***} & 0.963\textsuperscript{***} & 0.98\textsuperscript{***} \\
							VRV   & 1.016\textsuperscript{ } & 1.039\textsuperscript{ } & 0.992\textsuperscript{***} & 0.936\textsuperscript{***} & 0.987\textsuperscript{***} & 0.995\textsuperscript{***} \\
							VTRV  & 1.012\textsuperscript{ } & 1.035\textsuperscript{ } & 0.994\textsuperscript{***} & 0.941\textsuperscript{***} & 0.984\textsuperscript{***} & 0.992\textsuperscript{***} \\
							VBPV   & 1.019\textsuperscript{ } & 1.044\textsuperscript{ } & 0.995\textsuperscript{***} & 0.935\textsuperscript{***} & 0.989\textsuperscript{***} & 0.995\textsuperscript{***} \\
							VJV  & 0.991\textsuperscript{***} & 1.005\textsuperscript{ } & 0.976\textsuperscript{***} & 0.991\textsuperscript{***} & 0.959\textsuperscript{***} & 0.99\textsuperscript{***} \\
							MRV  & 1.045\textsuperscript{ } & 1.042\textsuperscript{ } & 0.957\textsuperscript{***} & 0.995\textsuperscript{***} & 1.002\textsuperscript{**} & 0.955\textsuperscript{***} \\
							MTRV  & 1.057\textsuperscript{ } & 1.042\textsuperscript{ } & 0.967\textsuperscript{***} & 0.992\textsuperscript{***} & 1.003\textsuperscript{**} & 0.955\textsuperscript{***} \\
							MBPV   & 1.05\textsuperscript{ } & 1.037\textsuperscript{ } & 0.959\textsuperscript{***} & 0.998\textsuperscript{***} & 1.004\textsuperscript{**} & 0.956\textsuperscript{***} \\
							MJV   & 1.416\textsuperscript{***} & 1.136\textsuperscript{***} & 1.038\textsuperscript{ } & 1.153\textsuperscript{***} & 1.134\textsuperscript{***} & 1.072\textsuperscript{ } \\
							MVRV  & 0.965\textsuperscript{***} & 1.068\textsuperscript{ } & 0.892\textsuperscript{***} & \textbf{0.924\textsuperscript{***}} & \textbf{0.956\textsuperscript{***}} & \textbf{0.912\textsuperscript{***}} \\
							MVTRV   & 0.957\textsuperscript{***} & 1.058\textsuperscript{ } & 0.899\textsuperscript{***} & 0.94\textsuperscript{***} & 0.957\textsuperscript{***} & 0.913\textsuperscript{***} \\
							MVBPV  & 0.964\textsuperscript{***} & 1.071\textsuperscript{ } & \textbf{0.89\textsuperscript{***}} & 0.925\textsuperscript{***} & 0.956\textsuperscript{***} & 0.912\textsuperscript{***} \\
							MVJV   & 0.987\textsuperscript{***} & 0.998\textsuperscript{***} & 0.947\textsuperscript{***} & 0.96\textsuperscript{***} & 0.958\textsuperscript{***} & 0.915\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{A1B} 
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Industrial Production (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA1B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 \\
							MMF  & 1.01\textsuperscript{ } & 1.016\textsuperscript{ } & 0.989\textsuperscript{***} & 1.055\textsuperscript{ } & 1.333\textsuperscript{***} & 1.08\textsuperscript{ } \\
							RV   & 0.956\textsuperscript{***} & 0.936\textsuperscript{***} & 1.106\textsuperscript{ } & 1.294\textsuperscript{***} & 1.143\textsuperscript{***} & 0.976\textsuperscript{***} \\
							TRV   & 0.959\textsuperscript{***} & 0.948\textsuperscript{***} & 1.14\textsuperscript{ } & 1.302\textsuperscript{***} & 1.136\textsuperscript{***} & \textbf{0.975\textsuperscript{***}} \\
							BPV  & 0.949\textsuperscript{***} & 0.93\textsuperscript{***} & 1.075\textsuperscript{ } & 1.293\textsuperscript{***} & 1.155\textsuperscript{***} & 0.98\textsuperscript{***} \\
							JV  & 3.349\textsuperscript{***} & 3.542\textsuperscript{***} & 2.762\textsuperscript{***} & 2.353\textsuperscript{***} & 2.272\textsuperscript{***} & 2.203\textsuperscript{***} \\
							CMRV1   & 1.017\textsuperscript{ } & 1.089\textsuperscript{ } & 1.063\textsuperscript{ } & 1.252\textsuperscript{***} & 1.136\textsuperscript{***} & 1.09\textsuperscript{ } \\
							CMTRV1   & \textbf{0.931\textsuperscript{***}} & 1.1\textsuperscript{***} & 1.043\textsuperscript{***} & 1.037\textsuperscript{*} & 1.104\textsuperscript{***} & 1.104\textsuperscript{***} \\
							CMBPV1   & 1.013\textsuperscript{ } & 1.082\textsuperscript{ } & 1.059\textsuperscript{ } & 1.243\textsuperscript{***} & 1.141\textsuperscript{***} & 1.09\textsuperscript{ } \\
							CMJV1  & 1.043\textsuperscript{ } & 1.159\textsuperscript{***} & 1.144\textsuperscript{***} & 1.108\textsuperscript{***} & 1.036\textsuperscript{ } & 1.119\textsuperscript{***} \\
							CMRV2   & 0.958\textsuperscript{***} & 1.223\textsuperscript{***} & 1.047\textsuperscript{***} & \textbf{1.018\textsuperscript{ }} & 1.123\textsuperscript{***} & 1.044\textsuperscript{*} \\
							CMTRV2   & 0.967\textsuperscript{***} & 1.089\textsuperscript{***} & 1.051\textsuperscript{***} & 1.073\textsuperscript{***} & 1.024\textsuperscript{ } & 1.114\textsuperscript{***} \\
							CMBPV2  & 0.957\textsuperscript{***} & 1.133\textsuperscript{***} & 1.082\textsuperscript{***} & 1.033\textsuperscript{ } & 1.08\textsuperscript{***} & 1.06\textsuperscript{***} \\
							CMJV2  & 1.071\textsuperscript{ } & 0.989\textsuperscript{***} & 1.091\textsuperscript{**} & 1.076\textsuperscript{***} & \textbf{0.975\textsuperscript{***}} & 1.083\textsuperscript{***} \\
							VRV   & 1.049\textsuperscript{ } & 1.119\textsuperscript{ } & 1.055\textsuperscript{ } & 1.02\textsuperscript{ } & 1.083\textsuperscript{***} & 1.07\textsuperscript{***} \\
							VTRV  & 1.052\textsuperscript{ } & 1.116\textsuperscript{ } & 1.037\textsuperscript{ } & 1.031\textsuperscript{ } & 1.085\textsuperscript{***} & 1.066\textsuperscript{***} \\
							VBPV   & 1.05\textsuperscript{ } & 1.121\textsuperscript{ } & 1.066\textsuperscript{ } & 1.018\textsuperscript{ } & 1.086\textsuperscript{***} & 1.074\textsuperscript{***} \\
							VJV  & 1.151\textsuperscript{ } & 1.001\textsuperscript{**} & 0.985\textsuperscript{***} & 1.039\textsuperscript{ } & 1.043\textsuperscript{***} & 1.017\textsuperscript{ } \\
							MRV  & 1.084\textsuperscript{ } & 1.041\textsuperscript{ } & 1.266\textsuperscript{***} & 1.444\textsuperscript{***} & 1.515\textsuperscript{***} & 1.193\textsuperscript{***} \\
							MTRV  & 1.091\textsuperscript{ } & 1.059\textsuperscript{ } & 1.284\textsuperscript{***} & 1.442\textsuperscript{***} & 1.521\textsuperscript{***} & 1.192\textsuperscript{***} \\
							MBPV   & 1.078\textsuperscript{ } & 1.023\textsuperscript{ } & 1.255\textsuperscript{***} & 1.453\textsuperscript{***} & 1.518\textsuperscript{***} & 1.189\textsuperscript{***} \\
							MJV   & 1.515\textsuperscript{***} & 1.772\textsuperscript{***} & 1.458\textsuperscript{***} & 1.443\textsuperscript{***} & 1.644\textsuperscript{***} & 1.554\textsuperscript{***} \\
							MVRV  & 1.184\textsuperscript{**} & 0.948\textsuperscript{***} & \textbf{0.956\textsuperscript{***}} & 1.096\textsuperscript{ } & 1.381\textsuperscript{***} & 1.135\textsuperscript{ } \\
							MVTRV   & 1.192\textsuperscript{**} & 0.948\textsuperscript{***} & 0.965\textsuperscript{***} & 1.099\textsuperscript{ } & 1.371\textsuperscript{***} & 1.129\textsuperscript{ } \\
							MVBPV  & 1.176\textsuperscript{*} & 0.948\textsuperscript{***} & 0.959\textsuperscript{***} & 1.097\textsuperscript{ } & 1.385\textsuperscript{***} & 1.138\textsuperscript{ } \\
							MVJV   & 1.147\textsuperscript{***} & \textbf{0.876\textsuperscript{***}} & 0.963\textsuperscript{***} & 1.12\textsuperscript{**} & 1.344\textsuperscript{***} & 1.14\textsuperscript{ } \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 \\
							MMF  & \textbf{0.95\textsuperscript{***}} & 0.976\textsuperscript{***} & 0.98\textsuperscript{***} & 0.986\textsuperscript{***} & 1.049\textsuperscript{ } & \textbf{0.938\textsuperscript{***}} \\
							RV   & 0.999\textsuperscript{***} & 0.963\textsuperscript{***} & 1.019\textsuperscript{ } & 1.029\textsuperscript{ } & 0.973\textsuperscript{***} & 0.968\textsuperscript{***} \\
							TRV   & 0.993\textsuperscript{***} & \textbf{0.962\textsuperscript{***}} & 1.021\textsuperscript{ } & 1.024\textsuperscript{ } & 0.97\textsuperscript{***} & 0.966\textsuperscript{***} \\
							BPV  & 1.003\textsuperscript{*} & 0.966\textsuperscript{***} & 1.028\textsuperscript{ } & 1.032\textsuperscript{ } & 0.973\textsuperscript{***} & 0.967\textsuperscript{***} \\
							JV  & 1.208\textsuperscript{**} & 1.199\textsuperscript{*} & 1.248\textsuperscript{***} & 1.24\textsuperscript{***} & 1.155\textsuperscript{ } & 1.143\textsuperscript{ } \\
							CMRV1   & 1.092\textsuperscript{***} & 1.039\textsuperscript{ } & 1.058\textsuperscript{***} & 1.102\textsuperscript{***} & 0.986\textsuperscript{***} & 0.993\textsuperscript{***} \\
							CMTRV1   & 1.015\textsuperscript{ } & 0.994\textsuperscript{***} & 1.007\textsuperscript{ } & 1.013\textsuperscript{***} & 0.996\textsuperscript{***} & 0.985\textsuperscript{***} \\
							CMBPV1   & 1.092\textsuperscript{***} & 1.04\textsuperscript{*} & 1.051\textsuperscript{*} & 1.105\textsuperscript{***} & 0.986\textsuperscript{***} & 0.994\textsuperscript{***} \\
							CMJV1  & 1.061\textsuperscript{**} & 1.015\textsuperscript{ } & 1.053\textsuperscript{***} & 1.028\textsuperscript{*} & \textbf{0.962\textsuperscript{***}} & 0.992\textsuperscript{***} \\
							CMRV2   & 1.016\textsuperscript{ } & 1.008\textsuperscript{ } & 0.99\textsuperscript{***} & 1.019\textsuperscript{ } & 0.969\textsuperscript{***} & 0.991\textsuperscript{***} \\
							CMTRV2   & 1.024\textsuperscript{ } & 0.997\textsuperscript{***} & 0.997\textsuperscript{***} & 1.018\textsuperscript{***} & 0.967\textsuperscript{***} & 0.992\textsuperscript{***} \\
							CMBPV2  & 1.018\textsuperscript{ } & 0.996\textsuperscript{***} & 0.995\textsuperscript{***} & 1.006\textsuperscript{ } & 0.967\textsuperscript{***} & 0.97\textsuperscript{***} \\
							CMJV2  & 0.994\textsuperscript{***} & 0.99\textsuperscript{***} & 1.047\textsuperscript{***} & 1.003\textsuperscript{*} & 0.97\textsuperscript{***} & 0.988\textsuperscript{***} \\
							VRV   & 1.055\textsuperscript{***} & 1.065\textsuperscript{ } & 1.075\textsuperscript{**} & \textbf{0.963\textsuperscript{***}} & 1.003\textsuperscript{ } & 1.017\textsuperscript{ } \\
							VTRV  & 1.049\textsuperscript{***} & 1.059\textsuperscript{ } & 1.064\textsuperscript{ } & 0.969\textsuperscript{***} & 1\textsuperscript{***} & 1.016\textsuperscript{ } \\
							VBPV   & 1.059\textsuperscript{***} & 1.073\textsuperscript{ } & 1.083\textsuperscript{***} & 0.963\textsuperscript{***} & 1.006\textsuperscript{ } & 1.018\textsuperscript{ } \\
							VJV  & 0.973\textsuperscript{***} & 0.994\textsuperscript{***} & 1.019\textsuperscript{ } & 1.014\textsuperscript{ } & 0.967\textsuperscript{***} & 1.007\textsuperscript{ } \\
							MRV  & 0.962\textsuperscript{***} & 0.983\textsuperscript{***} & 1.016\textsuperscript{ } & 1.048\textsuperscript{ } & 1.052\textsuperscript{ } & 0.961\textsuperscript{***} \\
							MTRV  & 0.958\textsuperscript{***} & 0.983\textsuperscript{***} & 1.017\textsuperscript{ } & 1.046\textsuperscript{ } & 1.052\textsuperscript{ } & 0.961\textsuperscript{***} \\
							MBPV   & 0.966\textsuperscript{***} & 0.983\textsuperscript{***} & 1.019\textsuperscript{ } & 1.049\textsuperscript{ } & 1.053\textsuperscript{ } & 0.961\textsuperscript{***} \\
							MJV   & 0.963\textsuperscript{***} & 1.029\textsuperscript{ } & 1.03\textsuperscript{ } & 1.051\textsuperscript{ } & 1.096\textsuperscript{*} & 1.029\textsuperscript{ } \\
							MVRV  & 0.959\textsuperscript{***} & 1.075\textsuperscript{ } & 0.974\textsuperscript{***} & 0.989\textsuperscript{***} & 1.037\textsuperscript{ } & 0.939\textsuperscript{***} \\
							MVTRV   & 0.956\textsuperscript{***} & 1.069\textsuperscript{ } & 0.978\textsuperscript{***} & 0.988\textsuperscript{***} & 1.042\textsuperscript{ } & 0.939\textsuperscript{***} \\
							MVBPV  & 0.959\textsuperscript{***} & 1.08\textsuperscript{ } & \textbf{0.972\textsuperscript{***}} & 0.99\textsuperscript{***} & 1.037\textsuperscript{ } & 0.939\textsuperscript{***} \\
							MVJV   & 0.983\textsuperscript{***} & 0.974\textsuperscript{***} & 1.013\textsuperscript{ } & 1.021\textsuperscript{ } & 1.068\textsuperscript{ } & 0.938\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
					
				\end{threeparttable}
			\end{table}
			
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{A1C} 
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Industrial Production (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA1C}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 69.6\% \textsuperscript{} & 70.9\% \textsuperscript{} & 57\% \textsuperscript{*} & 70.9\% \textsuperscript{} & 73.4\% \textsuperscript{} & 57\% \textsuperscript{} \\
							MMF  & 67.1\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 65.8\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 59.5\% \textsuperscript{ } \\
							RV   & 68.4\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 60.8\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 55.7\% \textsuperscript{**} \\
							TRV   & 68.4\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 60.8\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 57\% \textsuperscript{ } \\
							BPV  & 68.4\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 62\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							JV  & 58.2\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 58.2\% \textsuperscript{**} & 65.8\% \textsuperscript{***} & 62\% \textsuperscript{***} & 58.2\% \textsuperscript{ } \\
							CMRV1   & 69.6\% \textsuperscript{*} & 70.9\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 57\% \textsuperscript{*} \\
							CMTRV1   & 68.4\% \textsuperscript{***} & \textbf{73.4\% \textsuperscript{***}} & 64.6\% \textsuperscript{***} & 65.8\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 57\% \textsuperscript{ } \\
							CMBPV1   & 69.6\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 57\% \textsuperscript{ } \\
							CMJV1  & \textbf{72.2\% \textsuperscript{***}} & 70.9\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							CMRV2   & 67.1\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 65.8\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							CMTRV2   & 67.1\% \textsuperscript{***} & 73.4\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							CMBPV2  & 67.1\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & \textbf{65.8\% \textsuperscript{***}} & 64.6\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 57\% \textsuperscript{ } \\
							CMJV2  & 70.9\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 60.8\% \textsuperscript{**} & 68.4\% \textsuperscript{***} & 73.4\% \textsuperscript{***} & 59.5\% \textsuperscript{ } \\
							VRV   & 70.9\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 62\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 55.7\% \textsuperscript{**} \\
							VTRV  & 70.9\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 62\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							VBPV   & 70.9\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 62\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 57\% \textsuperscript{ } \\
							VJV  & 72.2\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 60.8\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 62\% \textsuperscript{ } \\
							MRV  & 65.8\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & \textbf{64.6\% \textsuperscript{**}} \\
							MTRV  & 65.8\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 63.3\% \textsuperscript{***} \\
							MBPV   & 65.8\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 63.3\% \textsuperscript{***} \\
							MJV   & 69.6\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 60.8\% \textsuperscript{***} & \textbf{72.2\% \textsuperscript{***}} & 69.6\% \textsuperscript{***} & 60.8\% \textsuperscript{***} \\
							MVRV  & 60.8\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & \textbf{74.7\% \textsuperscript{***}} & 59.5\% \textsuperscript{**} \\
							MVTRV   & 60.8\% \textsuperscript{**} & 68.4\% \textsuperscript{***} & 62\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 73.4\% \textsuperscript{***} & 59.5\% \textsuperscript{**} \\
							MVBPV  & 60.8\% \textsuperscript{**} & 68.4\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 74.7\% \textsuperscript{***} & 59.5\% \textsuperscript{**} \\
							MVJV   & 63.3\% \textsuperscript{**} & 72.2\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 60.8\% \textsuperscript{**} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & \textbf{75.9\% \textsuperscript{}} & 68.4\% \textsuperscript{} & 60.8\% \textsuperscript{} & 70.9\% \textsuperscript{} & 67.1\% \textsuperscript{} & 53.2\% \textsuperscript{} \\
							MMF  & 70.9\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 64.6\% \textsuperscript{**} & 72.2\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 62\% \textsuperscript{ } \\
							RV   & 65.8\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 58.2\% \textsuperscript{***} \\
							TRV   & 65.8\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 62\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 58.2\% \textsuperscript{*} \\
							BPV  & 65.8\% \textsuperscript{***} & \textbf{70.9\% \textsuperscript{***}} & 63.3\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 58.2\% \textsuperscript{*} \\
							JV  & 64.6\% \textsuperscript{***} & 60.8\% \textsuperscript{***} & 60.8\% \textsuperscript{***} & 58.2\% \textsuperscript{***} & 74.7\% \textsuperscript{***} & \textbf{65.8\% \textsuperscript{*}} \\
							CMRV1   & 73.4\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 70.9\% \textsuperscript{**} & 69.6\% \textsuperscript{***} & 51.9\% \textsuperscript{***} \\
							CMTRV1   & 70.9\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							CMBPV1   & 73.4\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 53.2\% \textsuperscript{ } \\
							CMJV1  & 73.4\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 62\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 54.4\% \textsuperscript{ } \\
							CMRV2   & 70.9\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							CMTRV2   & 69.6\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 54.4\% \textsuperscript{ } \\
							CMBPV2  & 72.2\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & \textbf{69.6\% \textsuperscript{***}} & 65.8\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 54.4\% \textsuperscript{ } \\
							CMJV2  & 74.7\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 59.5\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 54.4\% \textsuperscript{ } \\
							VRV   & 73.4\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 64.6\% \textsuperscript{**} & 68.4\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							VTRV  & 73.4\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 65.8\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							VBPV   & 73.4\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 55.7\% \textsuperscript{ } \\
							VJV  & 73.4\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 58.2\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 54.4\% \textsuperscript{ } \\
							MRV  & 63.3\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 63.3\% \textsuperscript{**} & 77.2\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 60.8\% \textsuperscript{ } \\
							MTRV  & 63.3\% \textsuperscript{***} & 65.8\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 77.2\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 60.8\% \textsuperscript{**} \\
							MBPV   & 63.3\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 77.2\% \textsuperscript{***} & 73.4\% \textsuperscript{***} & 60.8\% \textsuperscript{**} \\
							MJV   & 65.8\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 55.7\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & \textbf{75.9\% \textsuperscript{***}} & 55.7\% \textsuperscript{**} \\
							MVRV  & 67.1\% \textsuperscript{***} & 68.4\% \textsuperscript{***} & 64.6\% \textsuperscript{**} & \textbf{78.5\% \textsuperscript{***}} & 69.6\% \textsuperscript{***} & 63.3\% \textsuperscript{ } \\
							MVTRV   & 67.1\% \textsuperscript{***} & 65.8\% \textsuperscript{***} & 65.8\% \textsuperscript{***} & 78.5\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 63.3\% \textsuperscript{***} \\
							MVBPV  & 67.1\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 64.6\% \textsuperscript{***} & 78.5\% \textsuperscript{***} & 69.6\% \textsuperscript{***} & 63.3\% \textsuperscript{***} \\
							MVJV   & 70.9\% \textsuperscript{***} & 67.1\% \textsuperscript{***} & 63.3\% \textsuperscript{***} & 72.2\% \textsuperscript{***} & 70.9\% \textsuperscript{***} & 63.3\% \textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			
			
			\newpage
			\renewcommand{\thetable}{A1D} 
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Industrial Production (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA1D}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 67.4\%\textsuperscript{} & 72.1\%\textsuperscript{} & 55.8\%\textsuperscript{} & 69.8\%\textsuperscript{} & 74.4\%\textsuperscript{} & 53.5\%\textsuperscript{} \\
							MMF  & 65.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{ } & 67.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 58.1\%\textsuperscript{ } \\
							RV   & 62.8\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 60.5\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							TRV   & 62.8\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 60.5\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							BPV  & 62.8\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							JV  & 46.5\%\textsuperscript{**} & 58.1\%\textsuperscript{***} & 53.5\%\textsuperscript{***} & 58.1\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 53.5\%\textsuperscript{ } \\
							CMRV1   & 67.4\%\textsuperscript{ } & 72.1\%\textsuperscript{*} & \textbf{67.4\%\textsuperscript{*}} & 65.1\%\textsuperscript{ } & 69.8\%\textsuperscript{**} & 55.8\%\textsuperscript{ } \\
							CMTRV1   & \textbf{72.1\%\textsuperscript{***}} & 74.4\%\textsuperscript{***} & 60.5\%\textsuperscript{***} & 67.4\%\textsuperscript{**} & 74.4\%\textsuperscript{***} & 53.5\%\textsuperscript{ } \\
							CMBPV1   & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{*} & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							CMJV1  & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 67.4\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 53.5\%\textsuperscript{ } \\
							CMRV2   & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 58.1\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 53.5\%\textsuperscript{ } \\
							CMTRV2   & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 60.5\%\textsuperscript{ } & 65.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 48.8\%\textsuperscript{ } \\
							CMBPV2  & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 58.1\%\textsuperscript{*} & 65.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 53.5\%\textsuperscript{ } \\
							CMJV2  & 72.1\%\textsuperscript{***} & \textbf{76.7\%\textsuperscript{***}} & 60.5\%\textsuperscript{ } & 67.4\%\textsuperscript{**} & 74.4\%\textsuperscript{***} & 58.1\%\textsuperscript{ } \\
							VRV   & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 62.8\%\textsuperscript{*} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 53.5\%\textsuperscript{ } \\
							VTRV  & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 62.8\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 53.5\%\textsuperscript{ } \\
							VBPV   & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 62.8\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							VJV  & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{**} & 62.8\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 60.5\%\textsuperscript{ } \\
							MRV  & 62.8\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 60.5\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & \textbf{65.1\%\textsuperscript{*}} \\
							MTRV  & 62.8\%\textsuperscript{**} & 65.1\%\textsuperscript{**} & 60.5\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							MBPV   & 62.8\%\textsuperscript{**} & 65.1\%\textsuperscript{**} & 60.5\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							MJV   & 62.8\%\textsuperscript{**} & 65.1\%\textsuperscript{**} & 58.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 55.8\%\textsuperscript{**} \\
							MVRV  & 60.5\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & \textbf{76.7\%\textsuperscript{***}} & \textbf{86\%\textsuperscript{***}} & 60.5\%\textsuperscript{ } \\
							MVTRV   & 60.5\%\textsuperscript{*} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 60.5\%\textsuperscript{*} \\
							MVBPV  & 60.5\%\textsuperscript{*} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 86\%\textsuperscript{***} & 60.5\%\textsuperscript{*} \\
							MVJV   & 58.1\%\textsuperscript{*} & 76.7\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 65.1\%\textsuperscript{*} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & \textbf{74.4\%\textsuperscript{}} & 72.1\%\textsuperscript{} & 62.8\%\textsuperscript{} & 69.8\%\textsuperscript{} & 76.7\%\textsuperscript{} & 53.5\%\textsuperscript{} \\
							MMF  & 72.1\%\textsuperscript{***} & \textbf{74.4\%\textsuperscript{***}} & 62.8\%\textsuperscript{**} & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{ } \\
							RV   & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & \textbf{67.4\%\textsuperscript{***}} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 55.8\%\textsuperscript{**} \\
							TRV   & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							BPV  & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							JV  & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & \textbf{81.4\%\textsuperscript{***}} & \textbf{67.4\%\textsuperscript{ }} \\
							CMRV1   & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 53.5\%\textsuperscript{***} \\
							CMTRV1   & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 60.5\%\textsuperscript{ } \\
							CMBPV1   & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 53.5\%\textsuperscript{*} \\
							CMJV1  & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							CMRV2   & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 58.1\%\textsuperscript{ } \\
							CMTRV2   & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 58.1\%\textsuperscript{ } \\
							CMBPV2  & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 58.1\%\textsuperscript{ } \\
							CMJV2  & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 60.5\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							VRV   & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							VTRV  & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							VBPV   & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							VJV  & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							MRV  & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & \textbf{76.7\%\textsuperscript{***}} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{ } \\
							MTRV  & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MBPV   & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MJV   & 74.4\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 58.1\%\textsuperscript{**} \\
							MVRV  & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{**} & 65.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{ } \\
							MVTRV   & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVBPV  & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVJV   & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			
			\newpage
			\renewcommand{\thetable}{A2A} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Nonfarm Payroll Employment (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA2A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 0.977\textsuperscript{***} & 1.151\textsuperscript{***} & \textbf{0.978\textsuperscript{***}} & 0.992\textsuperscript{***} & \textbf{0.956\textsuperscript{***}} & 1.037\textsuperscript{ } \\
							RV   & 1.124\textsuperscript{***} & 1.07\textsuperscript{**} & 1.183\textsuperscript{***} & 1.249\textsuperscript{***} & 1.196\textsuperscript{***} & 1.287\textsuperscript{***} \\
							TRV   & 1.128\textsuperscript{***} & 1.075\textsuperscript{***} & 1.189\textsuperscript{***} & 1.256\textsuperscript{***} & 1.206\textsuperscript{***} & 1.292\textsuperscript{***} \\
							BPV  & 1.113\textsuperscript{***} & 1.063\textsuperscript{*} & 1.174\textsuperscript{***} & 1.244\textsuperscript{***} & 1.184\textsuperscript{***} & 1.281\textsuperscript{***} \\
							JV  & 3.043\textsuperscript{***} & 3.937\textsuperscript{***} & 4.257\textsuperscript{***} & 3.569\textsuperscript{***} & 2.547\textsuperscript{***} & 2.539\textsuperscript{***} \\
							CMRV1   & 1.012\textsuperscript{*} & 1.065\textsuperscript{ } & 1.039\textsuperscript{*} & 1.058\textsuperscript{***} & 1.048\textsuperscript{***} & 1.104\textsuperscript{***} \\
							CMTRV1   & 0.992\textsuperscript{***} & 1.134\textsuperscript{***} & 1.059\textsuperscript{***} & \textbf{0.926\textsuperscript{***}} & 0.978\textsuperscript{***} & 1.033\textsuperscript{ } \\
							CMBPV1   & 1.002\textsuperscript{***} & 1.066\textsuperscript{ } & 1.037\textsuperscript{*} & 1.055\textsuperscript{***} & 1.043\textsuperscript{***} & 1.096\textsuperscript{***} \\
							CMJV1  & 1.026\textsuperscript{ } & 1.04\textsuperscript{ } & 1.102\textsuperscript{***} & 1.033\textsuperscript{ } & 1.076\textsuperscript{***} & 1.07\textsuperscript{***} \\
							CMRV2   & \textbf{0.912\textsuperscript{***}} & 1.042\textsuperscript{ } & 1.024\textsuperscript{ } & 0.939\textsuperscript{***} & 0.973\textsuperscript{***} & 1.064\textsuperscript{***} \\
							CMTRV2   & 0.92\textsuperscript{***} & 1.032\textsuperscript{ } & 1.029\textsuperscript{ } & 0.964\textsuperscript{***} & 0.972\textsuperscript{***} & 1.043\textsuperscript{**} \\
							CMBPV2  & 0.968\textsuperscript{***} & 1.073\textsuperscript{ } & 1.072\textsuperscript{***} & 0.938\textsuperscript{***} & 0.974\textsuperscript{***} & 1.016\textsuperscript{ } \\
							CMJV2  & 1.032\textsuperscript{ } & 1.035\textsuperscript{ } & 1.086\textsuperscript{***} & 1.05\textsuperscript{ } & 1.021\textsuperscript{ } & 1.043\textsuperscript{ } \\
							VRV   & 1.046\textsuperscript{ } & 1.028\textsuperscript{ } & 1.023\textsuperscript{ } & 1.118\textsuperscript{***} & 1.124\textsuperscript{***} & 1.046\textsuperscript{ } \\
							VTRV  & 1.044\textsuperscript{ } & 1.029\textsuperscript{ } & 1.022\textsuperscript{ } & 1.12\textsuperscript{***} & 1.129\textsuperscript{***} & 1.051\textsuperscript{ } \\
							VBPV   & 1.046\textsuperscript{ } & \textbf{1.024\textsuperscript{ }} & 1.021\textsuperscript{ } & 1.116\textsuperscript{***} & 1.121\textsuperscript{***} & 1.04\textsuperscript{ } \\
							VJV  & 0.951\textsuperscript{***} & 1.064\textsuperscript{***} & 1.113\textsuperscript{***} & 1.085\textsuperscript{***} & 1.06\textsuperscript{***} & \textbf{1.01\textsuperscript{*}} \\
							MRV  & 1.146\textsuperscript{ } & 1.459\textsuperscript{***} & 1.207\textsuperscript{***} & 1.157\textsuperscript{***} & 1.094\textsuperscript{***} & 1.134\textsuperscript{***} \\
							MTRV  & 1.16\textsuperscript{ } & 1.468\textsuperscript{***} & 1.213\textsuperscript{***} & 1.164\textsuperscript{***} & 1.101\textsuperscript{***} & 1.134\textsuperscript{***} \\
							MBPV   & 1.133\textsuperscript{ } & 1.455\textsuperscript{***} & 1.197\textsuperscript{***} & 1.153\textsuperscript{***} & 1.092\textsuperscript{***} & 1.144\textsuperscript{***} \\
							MJV   & 1.333\textsuperscript{***} & 1.697\textsuperscript{***} & 1.637\textsuperscript{***} & 1.481\textsuperscript{***} & 1.316\textsuperscript{***} & 1.275\textsuperscript{***} \\
							MVRV  & 1.054\textsuperscript{ } & 1.256\textsuperscript{***} & 1.09\textsuperscript{**} & 1.095\textsuperscript{***} & 1.019\textsuperscript{ } & 1.061\textsuperscript{ } \\
							MVTRV   & 1.052\textsuperscript{ } & 1.257\textsuperscript{***} & 1.083\textsuperscript{*} & 1.102\textsuperscript{***} & 1.027\textsuperscript{ } & 1.061\textsuperscript{ } \\
							MVBPV  & 1.05\textsuperscript{ } & 1.255\textsuperscript{***} & 1.088\textsuperscript{**} & 1.102\textsuperscript{***} & 1.018\textsuperscript{ } & 1.066\textsuperscript{ } \\
							MVJV   & 1.059\textsuperscript{ } & 1.139\textsuperscript{***} & 1.048\textsuperscript{ } & 1.173\textsuperscript{***} & 0.96\textsuperscript{***} & 1.035\textsuperscript{ } \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & \textbf{0.832\textsuperscript{***}} & 0.996\textsuperscript{***} & 0.93\textsuperscript{***} & 0.803\textsuperscript{***} & 0.872\textsuperscript{***} & 0.718\textsuperscript{***} \\
							RV   & 1.068\textsuperscript{ } & 1.096\textsuperscript{ } & 1.183\textsuperscript{*} & 0.926\textsuperscript{***} & 0.841\textsuperscript{***} & \textbf{0.678\textsuperscript{***}} \\
							TRV   & 1.107\textsuperscript{*} & 1.16\textsuperscript{**} & 1.266\textsuperscript{***} & 0.997\textsuperscript{***} & 0.898\textsuperscript{***} & 0.703\textsuperscript{***} \\
							BPV  & 1.065\textsuperscript{ } & 1.097\textsuperscript{ } & 1.189\textsuperscript{*} & 0.934\textsuperscript{***} & 0.848\textsuperscript{***} & 0.681\textsuperscript{***} \\
							JV  & 5.114\textsuperscript{***} & 7.589\textsuperscript{***} & 10.525\textsuperscript{***} & 9.278\textsuperscript{***} & 9.378\textsuperscript{***} & 7.462\textsuperscript{***} \\
							CMRV1   & 0.912\textsuperscript{***} & 0.976\textsuperscript{***} & 0.96\textsuperscript{***} & 0.824\textsuperscript{***} & 0.898\textsuperscript{***} & 0.934\textsuperscript{***} \\
							CMTRV1   & 1.071\textsuperscript{ } & 1.322\textsuperscript{***} & 1.44\textsuperscript{***} & 1.269\textsuperscript{***} & 1.46\textsuperscript{***} & 1.496\textsuperscript{***} \\
							CMBPV1   & 0.908\textsuperscript{***} & 0.983\textsuperscript{***} & 0.927\textsuperscript{***} & 0.798\textsuperscript{***} & 0.903\textsuperscript{***} & 0.938\textsuperscript{***} \\
							CMJV1  & 0.916\textsuperscript{***} & 0.989\textsuperscript{***} & 0.981\textsuperscript{***} & 0.867\textsuperscript{***} & 0.91\textsuperscript{***} & 0.96\textsuperscript{***} \\
							CMRV2   & 1.038\textsuperscript{ } & 1.182\textsuperscript{***} & 1.229\textsuperscript{***} & 0.991\textsuperscript{***} & 1.309\textsuperscript{***} & 1.229\textsuperscript{***} \\
							CMTRV2   & 0.989\textsuperscript{***} & 1.112\textsuperscript{ } & 1.341\textsuperscript{***} & 1.197\textsuperscript{***} & 1.384\textsuperscript{***} & 1.552\textsuperscript{***} \\
							CMBPV2  & 0.965\textsuperscript{***} & 1.204\textsuperscript{***} & 1.293\textsuperscript{***} & 1.181\textsuperscript{***} & 1.372\textsuperscript{***} & 1.456\textsuperscript{***} \\
							CMJV2  & 1.016\textsuperscript{ } & 0.953\textsuperscript{***} & 1.047\textsuperscript{ } & 0.917\textsuperscript{***} & 0.982\textsuperscript{***} & 0.948\textsuperscript{***} \\
							VRV   & 0.951\textsuperscript{***} & 0.94\textsuperscript{***} & 0.863\textsuperscript{***} & 0.797\textsuperscript{***} & 0.789\textsuperscript{***} & 0.752\textsuperscript{***} \\
							VTRV  & 0.957\textsuperscript{***} & \textbf{0.931\textsuperscript{***}} & 0.866\textsuperscript{***} & \textbf{0.795\textsuperscript{***}} & 0.798\textsuperscript{***} & 0.744\textsuperscript{***} \\
							VBPV   & 0.954\textsuperscript{***} & 0.934\textsuperscript{***} & 0.869\textsuperscript{***} & 0.799\textsuperscript{***} & \textbf{0.788\textsuperscript{***}} & 0.754\textsuperscript{***} \\
							VJV  & 0.91\textsuperscript{***} & 0.988\textsuperscript{***} & \textbf{0.837\textsuperscript{***}} & 0.866\textsuperscript{***} & 0.918\textsuperscript{***} & 0.831\textsuperscript{***} \\
							MRV  & 0.982\textsuperscript{***} & 1.12\textsuperscript{ } & 0.999\textsuperscript{***} & 0.8\textsuperscript{***} & 0.873\textsuperscript{***} & 0.818\textsuperscript{***} \\
							MTRV  & 1.001\textsuperscript{***} & 1.142\textsuperscript{ } & 1.01\textsuperscript{*} & 0.804\textsuperscript{***} & 0.884\textsuperscript{***} & 0.834\textsuperscript{***} \\
							MBPV   & 0.986\textsuperscript{***} & 1.124\textsuperscript{ } & 0.996\textsuperscript{***} & 0.801\textsuperscript{***} & 0.874\textsuperscript{***} & 0.82\textsuperscript{***} \\
							MJV   & 1.254\textsuperscript{***} & 1.572\textsuperscript{***} & 1.379\textsuperscript{***} & 1.031\textsuperscript{ } & 1.124\textsuperscript{*} & 0.87\textsuperscript{***} \\
							MVRV  & 0.955\textsuperscript{***} & 1.011\textsuperscript{*} & 0.995\textsuperscript{***} & 0.864\textsuperscript{***} & 0.866\textsuperscript{***} & 0.792\textsuperscript{***} \\
							MVTRV   & 0.95\textsuperscript{***} & 1.015\textsuperscript{*} & 0.996\textsuperscript{***} & 0.864\textsuperscript{***} & 0.862\textsuperscript{***} & 0.802\textsuperscript{***} \\
							MVBPV  & 0.955\textsuperscript{***} & 1.011\textsuperscript{*} & 0.996\textsuperscript{***} & 0.867\textsuperscript{***} & 0.866\textsuperscript{***} & 0.795\textsuperscript{***} \\
							MVJV   & 0.878\textsuperscript{***} & 1.001\textsuperscript{***} & 0.963\textsuperscript{***} & 0.848\textsuperscript{***} & 0.883\textsuperscript{***} & 0.76\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			\newpage
			\renewcommand{\thetable}{A2B} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Nonfarm Payroll Employment (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA2B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.035\textsuperscript{ } & 1.282\textsuperscript{***} & 1\textsuperscript{***} & 1.025\textsuperscript{ } & \textbf{0.993\textsuperscript{***}} & 1.119\textsuperscript{ } \\
							RV   & 1.232\textsuperscript{***} & 1.134\textsuperscript{***} & 1.168\textsuperscript{***} & 1.2\textsuperscript{***} & 1.194\textsuperscript{***} & 1.375\textsuperscript{***} \\
							TRV   & 1.236\textsuperscript{***} & 1.135\textsuperscript{***} & 1.177\textsuperscript{***} & 1.21\textsuperscript{***} & 1.205\textsuperscript{***} & 1.381\textsuperscript{***} \\
							BPV  & 1.216\textsuperscript{***} & 1.123\textsuperscript{***} & 1.156\textsuperscript{***} & 1.193\textsuperscript{***} & 1.188\textsuperscript{***} & 1.366\textsuperscript{***} \\
							JV  & 3.307\textsuperscript{***} & 4.678\textsuperscript{***} & 5.391\textsuperscript{***} & 4.468\textsuperscript{***} & 3.081\textsuperscript{***} & 3.221\textsuperscript{***} \\
							CMRV1   & 1.007\textsuperscript{**} & 1.178\textsuperscript{**} & \textbf{0.996\textsuperscript{***}} & 1.022\textsuperscript{ } & 1.103\textsuperscript{***} & 1.129\textsuperscript{***} \\
							CMTRV1   & 0.957\textsuperscript{***} & 1.219\textsuperscript{***} & 1.023\textsuperscript{ } & \textbf{0.91\textsuperscript{***}} & 1.018\textsuperscript{ } & 1.037\textsuperscript{ } \\
							CMBPV1   & 0.997\textsuperscript{***} & 1.174\textsuperscript{**} & 0.996\textsuperscript{***} & 1.027\textsuperscript{**} & 1.096\textsuperscript{***} & 1.122\textsuperscript{***} \\
							CMJV1  & 1.111\textsuperscript{ } & 1.165\textsuperscript{***} & 1.034\textsuperscript{ } & 0.966\textsuperscript{***} & 1.156\textsuperscript{***} & 1.082\textsuperscript{***} \\
							CMRV2   & \textbf{0.828\textsuperscript{***}} & 1.069\textsuperscript{***} & 1.003\textsuperscript{**} & 0.946\textsuperscript{***} & 1.016\textsuperscript{ } & 1.027\textsuperscript{ } \\
							CMTRV2   & 0.844\textsuperscript{***} & 1.042\textsuperscript{ } & 1.002\textsuperscript{**} & 0.968\textsuperscript{***} & 0.999\textsuperscript{***} & 1.022\textsuperscript{ } \\
							CMBPV2  & 0.912\textsuperscript{***} & 1.091\textsuperscript{***} & 1.043\textsuperscript{ } & 0.924\textsuperscript{***} & 1.008\textsuperscript{ } & 1.02\textsuperscript{ } \\
							CMJV2  & 1.034\textsuperscript{ } & 1.091\textsuperscript{***} & 1.027\textsuperscript{ } & 1.005\textsuperscript{**} & 1.032\textsuperscript{*} & \textbf{0.994\textsuperscript{***}} \\
							VRV   & 1.087\textsuperscript{ } & 1.064\textsuperscript{ } & 1.021\textsuperscript{ } & 1.046\textsuperscript{***} & 1.14\textsuperscript{***} & 1.022\textsuperscript{ } \\
							VTRV  & 1.088\textsuperscript{ } & 1.065\textsuperscript{ } & 1.019\textsuperscript{ } & 1.047\textsuperscript{***} & 1.146\textsuperscript{***} & 1.03\textsuperscript{ } \\
							VBPV   & 1.084\textsuperscript{ } & 1.062\textsuperscript{ } & 1.019\textsuperscript{ } & 1.047\textsuperscript{***} & 1.134\textsuperscript{***} & 1.011\textsuperscript{*} \\
							VJV  & 0.956\textsuperscript{***} & \textbf{1.04\textsuperscript{ }} & 1.18\textsuperscript{***} & 1.02\textsuperscript{ } & 1.039\textsuperscript{ } & 1.015\textsuperscript{*} \\
							MRV  & 1.272\textsuperscript{ } & 1.687\textsuperscript{***} & 1.174\textsuperscript{***} & 1.173\textsuperscript{***} & 1.154\textsuperscript{***} & 1.265\textsuperscript{***} \\
							MTRV  & 1.288\textsuperscript{ } & 1.698\textsuperscript{***} & 1.18\textsuperscript{***} & 1.179\textsuperscript{***} & 1.165\textsuperscript{***} & 1.266\textsuperscript{***} \\
							MBPV   & 1.251\textsuperscript{ } & 1.677\textsuperscript{***} & 1.157\textsuperscript{***} & 1.168\textsuperscript{***} & 1.148\textsuperscript{***} & 1.282\textsuperscript{***} \\
							MJV   & 1.325\textsuperscript{***} & 1.934\textsuperscript{***} & 1.835\textsuperscript{***} & 1.681\textsuperscript{***} & 1.542\textsuperscript{***} & 1.478\textsuperscript{***} \\
							MVRV  & 1.187\textsuperscript{ } & 1.413\textsuperscript{***} & 1.085\textsuperscript{ } & 1.17\textsuperscript{***} & 1.073\textsuperscript{ } & 1.135\textsuperscript{*} \\
							MVTRV   & 1.181\textsuperscript{ } & 1.411\textsuperscript{***} & 1.084\textsuperscript{ } & 1.179\textsuperscript{***} & 1.084\textsuperscript{ } & 1.136\textsuperscript{*} \\
							MVBPV  & 1.182\textsuperscript{ } & 1.413\textsuperscript{***} & 1.086\textsuperscript{ } & 1.183\textsuperscript{***} & 1.068\textsuperscript{ } & 1.145\textsuperscript{***} \\
							MVJV   & 1.125\textsuperscript{ } & 1.255\textsuperscript{***} & 1.028\textsuperscript{ } & 1.256\textsuperscript{***} & 1.005\textsuperscript{**} & 1.076\textsuperscript{ } \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 0.949\textsuperscript{***} & 1.304\textsuperscript{***} & 1.201\textsuperscript{***} & 1.095\textsuperscript{***} & 0.968\textsuperscript{***} & 1.031\textsuperscript{ } \\
							RV   & 1.041\textsuperscript{ } & 1.061\textsuperscript{ } & 1.027\textsuperscript{ } & 0.993\textsuperscript{***} & 1.016\textsuperscript{ } & 1.025\textsuperscript{ } \\
							TRV   & 1.047\textsuperscript{ } & 1.064\textsuperscript{ } & 1.032\textsuperscript{ } & 0.996\textsuperscript{***} & 1.018\textsuperscript{ } & 1.026\textsuperscript{ } \\
							BPV  & 1.036\textsuperscript{ } & 1.057\textsuperscript{ } & 1.023\textsuperscript{ } & 0.994\textsuperscript{***} & 1.017\textsuperscript{ } & 1.027\textsuperscript{ } \\
							JV  & 1.999\textsuperscript{***} & 2.128\textsuperscript{***} & 2.324\textsuperscript{***} & 1.744\textsuperscript{***} & 1.452\textsuperscript{***} & 1.445\textsuperscript{***} \\
							CMRV1   & 0.912\textsuperscript{***} & 1.148\textsuperscript{***} & 1.013\textsuperscript{ } & 0.972\textsuperscript{***} & 1.001\textsuperscript{*} & 0.97\textsuperscript{***} \\
							CMTRV1   & 1.005\textsuperscript{**} & 1.232\textsuperscript{***} & 1.042\textsuperscript{ } & 0.963\textsuperscript{***} & 1.005\textsuperscript{ } & 1.027\textsuperscript{***} \\
							CMBPV1   & 0.911\textsuperscript{***} & 1.153\textsuperscript{***} & 1.017\textsuperscript{ } & 0.973\textsuperscript{***} & 1.003\textsuperscript{ } & 0.971\textsuperscript{***} \\
							CMJV1  & 0.928\textsuperscript{***} & 1.154\textsuperscript{***} & 1.005\textsuperscript{*} & 0.974\textsuperscript{***} & 0.997\textsuperscript{***} & 0.971\textsuperscript{***} \\
							CMRV2   & 0.922\textsuperscript{***} & 1.157\textsuperscript{***} & \textbf{0.975\textsuperscript{***}} & 0.987\textsuperscript{***} & 0.996\textsuperscript{***} & 1.013\textsuperscript{ } \\
							CMTRV2   & \textbf{0.864\textsuperscript{***}} & 1.079\textsuperscript{***} & 1.018\textsuperscript{ } & 1.011\textsuperscript{ } & 1.009\textsuperscript{ } & 1.025\textsuperscript{***} \\
							CMBPV2  & 0.884\textsuperscript{***} & 1.136\textsuperscript{***} & 1.054\textsuperscript{ } & 0.965\textsuperscript{***} & 0.992\textsuperscript{***} & 1.008\textsuperscript{ } \\
							CMJV2  & 0.993\textsuperscript{***} & \textbf{1.048\textsuperscript{*}} & 1.007\textsuperscript{ } & \textbf{0.957\textsuperscript{***}} & 0.978\textsuperscript{***} & 0.994\textsuperscript{***} \\
							VRV   & 1.006\textsuperscript{*} & 1.082\textsuperscript{***} & 1.079\textsuperscript{***} & 0.977\textsuperscript{***} & 0.979\textsuperscript{***} & 0.955\textsuperscript{***} \\
							VTRV  & 1.019\textsuperscript{ } & 1.082\textsuperscript{***} & 1.074\textsuperscript{***} & 0.978\textsuperscript{***} & 0.982\textsuperscript{***} & \textbf{0.953\textsuperscript{***}} \\
							VBPV   & 1.007\textsuperscript{ } & 1.082\textsuperscript{***} & 1.086\textsuperscript{***} & 0.978\textsuperscript{***} & 0.982\textsuperscript{***} & 0.954\textsuperscript{***} \\
							VJV  & 0.927\textsuperscript{***} & 1.056\textsuperscript{***} & 1.019\textsuperscript{ } & 0.988\textsuperscript{***} & 1.003\textsuperscript{**} & 0.99\textsuperscript{***} \\
							MRV  & 1.065\textsuperscript{ } & 1.344\textsuperscript{***} & 1.213\textsuperscript{***} & 1.117\textsuperscript{***} & \textbf{0.902\textsuperscript{***}} & 1.038\textsuperscript{ } \\
							MTRV  & 1.066\textsuperscript{ } & 1.344\textsuperscript{***} & 1.212\textsuperscript{***} & 1.113\textsuperscript{***} & 0.902\textsuperscript{***} & 1.037\textsuperscript{ } \\
							MBPV   & 1.07\textsuperscript{ } & 1.344\textsuperscript{***} & 1.202\textsuperscript{***} & 1.119\textsuperscript{***} & 0.903\textsuperscript{***} & 1.041\textsuperscript{ } \\
							MJV   & 1.022\textsuperscript{ } & 1.413\textsuperscript{***} & 1.168\textsuperscript{ } & 1.145\textsuperscript{***} & 1.002\textsuperscript{**} & 1.11\textsuperscript{***} \\
							MVRV  & 1.144\textsuperscript{ } & 1.315\textsuperscript{***} & 1.294\textsuperscript{***} & 1.237\textsuperscript{***} & 0.911\textsuperscript{***} & 1.027\textsuperscript{ } \\
							MVTRV   & 1.13\textsuperscript{ } & 1.314\textsuperscript{***} & 1.293\textsuperscript{***} & 1.237\textsuperscript{***} & 0.906\textsuperscript{***} & 1.029\textsuperscript{ } \\
							MVBPV  & 1.145\textsuperscript{ } & 1.314\textsuperscript{***} & 1.299\textsuperscript{***} & 1.245\textsuperscript{***} & 0.913\textsuperscript{***} & 1.03\textsuperscript{ } \\
							MVJV   & 0.993\textsuperscript{***} & 1.315\textsuperscript{***} & 1.195\textsuperscript{***} & 1.159\textsuperscript{***} & 0.919\textsuperscript{***} & 1\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			\newpage
			\renewcommand{\thetable}{A2C} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Nonfarm Payroll Employment (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA2C}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 77.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							MMF  & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & \textbf{72.2\%\textsuperscript{***}} & \textbf{75.9\%\textsuperscript{***}} & 74.7\%\textsuperscript{***} \\
							RV   & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							TRV   & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							BPV  & 75.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							JV  & 65.8\%\textsuperscript{***} & 58.2\%\textsuperscript{*} & 63.3\%\textsuperscript{***} & 62\%\textsuperscript{***} & 59.5\%\textsuperscript{**} & 64.6\%\textsuperscript{***} \\
							CMRV1   & 74.7\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							CMTRV1   & 73.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							CMBPV1   & 74.7\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							CMJV1  & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMRV2   & 73.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & \textbf{75.9\%\textsuperscript{***}} \\
							CMTRV2   & 75.9\%\textsuperscript{***} & \textbf{81\%\textsuperscript{***}} & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMBPV2  & 74.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 75.9\%\textsuperscript{***} \\
							CMJV2  & 70.9\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 75.9\%\textsuperscript{***} \\
							VRV   & 72.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							VTRV  & 72.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							VBPV   & 72.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							VJV  & 73.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							MRV  & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							MTRV  & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							MBPV   & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							MJV   & 77.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							MVRV  & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MVTRV   & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MVBPV  & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MVJV   & \textbf{78.5\%\textsuperscript{***}} & 77.2\%\textsuperscript{***} & \textbf{72.2\%\textsuperscript{***}} & 72.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 75.9\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & 62\%\textsuperscript{***} \\
							MMF  & 78.5\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & \textbf{79.7\%\textsuperscript{***}} \\
							RV   & 73.4\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & \textbf{73.4\%\textsuperscript{***}} & 79.7\%\textsuperscript{***} \\
							TRV   & 69.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 79.7\%\textsuperscript{***} \\
							BPV  & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 79.7\%\textsuperscript{***} \\
							JV  & 62\%\textsuperscript{***} & 59.5\%\textsuperscript{***} & 59.5\%\textsuperscript{**} & 58.2\%\textsuperscript{**} & 67.1\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							CMRV1   & 74.7\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 63.3\%\textsuperscript{***} \\
							CMTRV1   & 65.8\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 60.8\%\textsuperscript{**} & 59.5\%\textsuperscript{**} & 58.2\%\textsuperscript{**} \\
							CMBPV1   & 75.9\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} \\
							CMJV1  & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 62\%\textsuperscript{***} \\
							CMRV2   & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 59.5\%\textsuperscript{**} & 59.5\%\textsuperscript{**} \\
							CMTRV2   & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 62\%\textsuperscript{**} & 59.5\%\textsuperscript{**} & 59.5\%\textsuperscript{**} \\
							CMBPV2  & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 59.5\%\textsuperscript{**} & 58.2\%\textsuperscript{**} \\
							CMJV2  & 72.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							VRV   & 75.9\%\textsuperscript{***} & \textbf{77.2\%\textsuperscript{***}} & 67.1\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							VTRV  & \textbf{79.7\%\textsuperscript{***}} & 77.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							VBPV   & 77.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							VJV  & 75.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							MRV  & 77.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 77.2\%\textsuperscript{***} \\
							MTRV  & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 75.9\%\textsuperscript{***} \\
							MBPV   & 77.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 77.2\%\textsuperscript{***} \\
							MJV   & 77.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & \textbf{77.2\%\textsuperscript{***}} & 72.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							MVRV  & 77.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 75.9\%\textsuperscript{***} \\
							MVTRV   & 77.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & \textbf{77.2\%\textsuperscript{***}} & 70.9\%\textsuperscript{***} & 75.9\%\textsuperscript{***} \\
							MVBPV  & 77.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 75.9\%\textsuperscript{***} \\
							MVJV   & 77.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 78.5\%\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------			
			
			
			
			\newpage
			\renewcommand{\thetable}{A2D} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Nonfarm Payroll Employment (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA2D}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & \textbf{83.7\%\textsuperscript{***}} & \textbf{86\%\textsuperscript{***}} & \textbf{72.1\%\textsuperscript{***}} & \textbf{69.8\%\textsuperscript{***}} & 76.7\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MMF  & 76.7\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & \textbf{76.7\%\textsuperscript{***}} & 74.4\%\textsuperscript{***} \\
							RV   & 81.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							TRV   & 81.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							BPV  & 83.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							JV  & 67.4\%\textsuperscript{***} & 53.5\%\textsuperscript{ } & 58.1\%\textsuperscript{ } & 58.1\%\textsuperscript{ } & 60.5\%\textsuperscript{*} & 62.8\%\textsuperscript{**} \\
							CMRV1   & 76.7\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMTRV1   & 79.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							CMBPV1   & 76.7\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMJV1  & 72.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMRV2   & 81.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							CMTRV2   & 81.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMBPV2  & 81.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							CMJV2  & 74.4\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & \textbf{81.4\%\textsuperscript{***}} \\
							VRV   & 72.1\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							VTRV  & 72.1\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} \\
							VBPV   & 72.1\%\textsuperscript{***} & 86\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							VJV  & 74.4\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MRV  & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MTRV  & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MBPV   & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MJV   & 81.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 65.1\%\textsuperscript{**} & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVRV  & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MVTRV   & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MVBPV  & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MVJV   & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & \textbf{81.4\%\textsuperscript{***}} & 72.1\%\textsuperscript{***} \\
							
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 81.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							MMF  & 79.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & \textbf{79.1\%\textsuperscript{***}} & 81.4\%\textsuperscript{***} \\
							RV   & 81.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & \textbf{83.7\%\textsuperscript{***}} \\
							TRV   & 81.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} \\
							BPV  & 81.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} \\
							JV  & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 62.8\%\textsuperscript{**} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMRV1   & 83.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & \textbf{81.4\%\textsuperscript{***}} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMTRV1   & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMBPV1   & 83.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMJV1  & 81.4\%\textsuperscript{***} & \textbf{86\%\textsuperscript{***}} & 81.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMRV2   & 83.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMTRV2   & 79.1\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMBPV2  & \textbf{86\%\textsuperscript{***}} & 81.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMJV2  & 81.4\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & \textbf{74.4\%\textsuperscript{***}} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							VRV   & 79.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							VTRV  & 79.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} \\
							VBPV   & 81.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							VJV  & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 81.4\%\textsuperscript{***} \\
							MRV  & 79.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MTRV  & 79.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MBPV   & 79.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MJV   & 83.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							MVRV  & 79.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MVTRV   & 79.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MVBPV  & 79.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MVJV   & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------		
			
			\newpage
			\renewcommand{\thetable}{A3A} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Consumer Price Index (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA3A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.09\textsuperscript{***} & 1.028\textsuperscript{ } & 1.013\textsuperscript{ } & 1.046\textsuperscript{ } & 1.122\textsuperscript{***} & 1.221\textsuperscript{***} \\
							RV   & 1.127\textsuperscript{***} & 1.152\textsuperscript{***} & 1.181\textsuperscript{***} & 1.223\textsuperscript{***} & 1.096\textsuperscript{***} & 1.17\textsuperscript{***} \\
							TRV   & 1.127\textsuperscript{***} & 1.16\textsuperscript{***} & 1.191\textsuperscript{***} & 1.226\textsuperscript{***} & 1.104\textsuperscript{***} & 1.18\textsuperscript{***} \\
							BPV  & 1.133\textsuperscript{***} & 1.148\textsuperscript{***} & 1.171\textsuperscript{***} & 1.213\textsuperscript{***} & 1.09\textsuperscript{***} & 1.16\textsuperscript{***} \\
							JV  & 1.893\textsuperscript{***} & 1.891\textsuperscript{***} & 1.976\textsuperscript{***} & 2.112\textsuperscript{***} & 2.523\textsuperscript{***} & 3.048\textsuperscript{***} \\
							CMRV1   & 1.138\textsuperscript{***} & 1.078\textsuperscript{***} & 1.013\textsuperscript{ } & 1.235\textsuperscript{***} & 0.916\textsuperscript{***} & 1.05\textsuperscript{ } \\
							CMTRV1   & 1.162\textsuperscript{***} & 1.085\textsuperscript{***} & 1.038\textsuperscript{***} & 1.045\textsuperscript{ } & 0.942\textsuperscript{***} & 1.065\textsuperscript{***} \\
							CMBPV1   & 1.137\textsuperscript{***} & 1.066\textsuperscript{***} & 1.058\textsuperscript{ } & 1.251\textsuperscript{***} & 0.914\textsuperscript{***} & 1.048\textsuperscript{ } \\
							CMJV1  & 1.088\textsuperscript{***} & 1.064\textsuperscript{***} & 1.014\textsuperscript{ } & 1.003\textsuperscript{**} & 0.907\textsuperscript{***} & 1.112\textsuperscript{***} \\
							CMRV2   & 1.106\textsuperscript{***} & 1.07\textsuperscript{***} & 1.008\textsuperscript{ } & 1.044\textsuperscript{ } & \textbf{0.904\textsuperscript{***}} & 1.078\textsuperscript{***} \\
							CMTRV2   & 1.106\textsuperscript{***} & 1.08\textsuperscript{***} & 1.005\textsuperscript{ } & 1.078\textsuperscript{***} & 0.982\textsuperscript{***} & 1.074\textsuperscript{***} \\
							CMBPV2  & 1.137\textsuperscript{***} & 1.071\textsuperscript{***} & 1.02\textsuperscript{ } & 1.036\textsuperscript{ } & 0.922\textsuperscript{***} & 1.103\textsuperscript{***} \\
							CMJV2  & 1.031\textsuperscript{***} & 1.026\textsuperscript{***} & \textbf{0.995\textsuperscript{***}} & \textbf{0.972\textsuperscript{***}} & 0.943\textsuperscript{***} & 1.075\textsuperscript{***} \\
							VRV   & 1.037\textsuperscript{***} & 1.077\textsuperscript{**} & 1.034\textsuperscript{ } & 0.996\textsuperscript{***} & 0.992\textsuperscript{***} & 1.029\textsuperscript{ } \\
							VTRV  & 1.038\textsuperscript{***} & 1.078\textsuperscript{***} & 1.034\textsuperscript{ } & 1.001\textsuperscript{***} & 0.989\textsuperscript{***} & 1.03\textsuperscript{ } \\
							VBPV   & 1.037\textsuperscript{***} & 1.081\textsuperscript{***} & 1.031\textsuperscript{ } & 0.996\textsuperscript{***} & 0.993\textsuperscript{***} & \textbf{1.024\textsuperscript{ }} \\
							VJV  & \textbf{1.025\textsuperscript{***}} & \textbf{0.998\textsuperscript{***}} & 1.052\textsuperscript{***} & 0.998\textsuperscript{***} & 1.001\textsuperscript{**} & 1.086\textsuperscript{***} \\
							MRV  & 1.138\textsuperscript{***} & 1.078\textsuperscript{***} & 1.142\textsuperscript{***} & 1.071\textsuperscript{ } & 1.258\textsuperscript{***} & 1.399\textsuperscript{***} \\
							MTRV  & 1.14\textsuperscript{***} & 1.083\textsuperscript{***} & 1.147\textsuperscript{***} & 1.074\textsuperscript{ } & 1.269\textsuperscript{***} & 1.407\textsuperscript{***} \\
							MBPV   & 1.181\textsuperscript{***} & 1.104\textsuperscript{***} & 1.133\textsuperscript{***} & 1.072\textsuperscript{ } & 1.257\textsuperscript{***} & 1.391\textsuperscript{***} \\
							MJV   & 1.416\textsuperscript{***} & 1.266\textsuperscript{***} & 1.316\textsuperscript{***} & 1.287\textsuperscript{***} & 1.587\textsuperscript{***} & 1.79\textsuperscript{***} \\
							MVRV  & 1.09\textsuperscript{***} & 1.079\textsuperscript{***} & 1.003\textsuperscript{**} & 1.089\textsuperscript{*} & 1.244\textsuperscript{***} & 1.316\textsuperscript{***} \\
							MVTRV   & 1.093\textsuperscript{***} & 1.08\textsuperscript{***} & 1.004\textsuperscript{**} & 1.088\textsuperscript{ } & 1.248\textsuperscript{***} & 1.329\textsuperscript{***} \\
							MVBPV  & 1.089\textsuperscript{***} & 1.075\textsuperscript{**} & 1.002\textsuperscript{**} & 1.091\textsuperscript{*} & 1.239\textsuperscript{***} & 1.312\textsuperscript{***} \\
							MVJV   & 1.09\textsuperscript{***} & 1.085\textsuperscript{***} & 1.018\textsuperscript{ } & 1.058\textsuperscript{ } & 1.268\textsuperscript{***} & 1.302\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.01\textsuperscript{ } & 1.013\textsuperscript{ } & 1.047\textsuperscript{***} & 1.009\textsuperscript{ } & 0.989\textsuperscript{***} & 1.045\textsuperscript{***} \\
							RV   & 1.036\textsuperscript{ } & 1.083\textsuperscript{***} & 1.084\textsuperscript{***} & 1.039\textsuperscript{ } & 1.015\textsuperscript{ } & 1.01\textsuperscript{ } \\
							TRV   & 1.037\textsuperscript{ } & 1.083\textsuperscript{***} & 1.083\textsuperscript{***} & 1.04\textsuperscript{ } & 1.015\textsuperscript{ } & 1.003\textsuperscript{*} \\
							BPV  & 1.036\textsuperscript{ } & 1.085\textsuperscript{***} & 1.085\textsuperscript{***} & 1.04\textsuperscript{ } & 1.016\textsuperscript{ } & 1.011\textsuperscript{ } \\
							JV  & 1.086\textsuperscript{ } & 1.116\textsuperscript{***} & 1.144\textsuperscript{***} & 1.152\textsuperscript{***} & 1.146\textsuperscript{***} & 1.153\textsuperscript{***} \\
							CMRV1   & \textbf{0.98\textsuperscript{***}} & 1.006\textsuperscript{ } & 1.018\textsuperscript{ } & \textbf{0.993\textsuperscript{***}} & 0.985\textsuperscript{***} & 1.028\textsuperscript{***} \\
							CMTRV1   & 1.03\textsuperscript{***} & 1.025\textsuperscript{***} & 1.013\textsuperscript{ } & 1.02\textsuperscript{***} & 0.984\textsuperscript{***} & 1.018\textsuperscript{ } \\
							CMBPV1   & 0.98\textsuperscript{***} & 1.006\textsuperscript{ } & 1.018\textsuperscript{ } & 0.993\textsuperscript{***} & 0.984\textsuperscript{***} & 1.029\textsuperscript{***} \\
							CMJV1  & 0.983\textsuperscript{***} & 1.007\textsuperscript{ } & 1.016\textsuperscript{ } & 1.009\textsuperscript{ } & 0.981\textsuperscript{***} & 1.013\textsuperscript{***} \\
							CMRV2   & 1.014\textsuperscript{***} & 1.034\textsuperscript{***} & 1.013\textsuperscript{***} & 0.995\textsuperscript{***} & \textbf{0.949\textsuperscript{***}} & 1.035\textsuperscript{***} \\
							CMTRV2   & 1.007\textsuperscript{ } & \textbf{1\textsuperscript{***}} & 1.018\textsuperscript{***} & 1.013\textsuperscript{ } & 1.009\textsuperscript{ } & 1.042\textsuperscript{***} \\
							CMBPV2  & 1.008\textsuperscript{ } & 1.025\textsuperscript{***} & \textbf{1.007\textsuperscript{ }} & 1.013\textsuperscript{ } & 0.972\textsuperscript{***} & 1.056\textsuperscript{***} \\
							CMJV2  & 0.985\textsuperscript{***} & 1.023\textsuperscript{***} & 1.031\textsuperscript{***} & 1.019\textsuperscript{**} & 1.005\textsuperscript{ } & \textbf{1.001\textsuperscript{**}} \\
							VRV   & 0.989\textsuperscript{***} & 1.028\textsuperscript{*} & 1.031\textsuperscript{*} & 1.019\textsuperscript{ } & 0.985\textsuperscript{***} & 1.02\textsuperscript{***} \\
							VTRV  & 0.989\textsuperscript{***} & 1.03\textsuperscript{**} & 1.028\textsuperscript{ } & 1.019\textsuperscript{ } & 0.986\textsuperscript{***} & 1.02\textsuperscript{***} \\
							VBPV   & 0.989\textsuperscript{***} & 1.028\textsuperscript{*} & 1.031\textsuperscript{ } & 1.018\textsuperscript{ } & 0.986\textsuperscript{***} & 1.02\textsuperscript{***} \\
							VJV  & 0.994\textsuperscript{***} & 1.023\textsuperscript{***} & 1.041\textsuperscript{***} & 1.012\textsuperscript{ } & 1\textsuperscript{***} & 1.037\textsuperscript{***} \\
							MRV  & 1.068\textsuperscript{***} & 1.085\textsuperscript{***} & 1.109\textsuperscript{***} & 1.033\textsuperscript{ } & 1.018\textsuperscript{ } & 1.09\textsuperscript{***} \\
							MTRV  & 1.069\textsuperscript{***} & 1.083\textsuperscript{***} & 1.114\textsuperscript{***} & 1.031\textsuperscript{ } & 1.021\textsuperscript{ } & 1.093\textsuperscript{***} \\
							MBPV   & 1.068\textsuperscript{***} & 1.094\textsuperscript{***} & 1.109\textsuperscript{***} & 1.031\textsuperscript{ } & 1.009\textsuperscript{ } & 1.092\textsuperscript{***} \\
							MJV   & 1.124\textsuperscript{***} & 1.143\textsuperscript{***} & 1.277\textsuperscript{***} & 1.249\textsuperscript{***} & 1.148\textsuperscript{***} & 1.178\textsuperscript{***} \\
							MVRV  & 1.026\textsuperscript{ } & 1.043\textsuperscript{*} & 1.058\textsuperscript{***} & 1.027\textsuperscript{ } & 0.981\textsuperscript{***} & 1.047\textsuperscript{***} \\
							MVTRV   & 1.026\textsuperscript{ } & 1.039\textsuperscript{ } & 1.057\textsuperscript{***} & 1.027\textsuperscript{ } & 0.978\textsuperscript{***} & 1.043\textsuperscript{***} \\
							MVBPV  & 1.026\textsuperscript{ } & 1.044\textsuperscript{*} & 1.057\textsuperscript{***} & 1.031\textsuperscript{*} & 0.983\textsuperscript{***} & 1.048\textsuperscript{***} \\
							MVJV   & 1.016\textsuperscript{ } & 1.035\textsuperscript{ } & 1.048\textsuperscript{***} & 1.053\textsuperscript{***} & 1.005\textsuperscript{*} & 1.008\textsuperscript{ } \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			\newpage
			\renewcommand{\thetable}{A3B} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Consumer Price Index (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA3B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.107\textsuperscript{***} & 1.046\textsuperscript{ } & 1.113\textsuperscript{**} & 1.127\textsuperscript{**} & 1.166\textsuperscript{***} & 1.211\textsuperscript{***} \\
							RV   & 1.175\textsuperscript{***} & 1.207\textsuperscript{***} & 1.238\textsuperscript{***} & 1.29\textsuperscript{***} & 1.2\textsuperscript{***} & 1.213\textsuperscript{***} \\
							TRV   & 1.172\textsuperscript{***} & 1.216\textsuperscript{***} & 1.249\textsuperscript{***} & 1.293\textsuperscript{***} & 1.212\textsuperscript{***} & 1.227\textsuperscript{***} \\
							BPV  & 1.183\textsuperscript{***} & 1.2\textsuperscript{***} & 1.224\textsuperscript{***} & 1.274\textsuperscript{***} & 1.191\textsuperscript{***} & 1.198\textsuperscript{***} \\
							JV  & 1.862\textsuperscript{***} & 1.52\textsuperscript{***} & 1.799\textsuperscript{***} & 2.138\textsuperscript{***} & 2.905\textsuperscript{***} & 3.411\textsuperscript{***} \\
							CMRV1   & 1.16\textsuperscript{***} & 1.071\textsuperscript{ } & 1.004\textsuperscript{**} & 1.314\textsuperscript{ } & \textbf{0.954\textsuperscript{***}} & 1.105\textsuperscript{***} \\
							CMTRV1   & 1.179\textsuperscript{***} & 1.053\textsuperscript{***} & 1.023\textsuperscript{ } & 1.068\textsuperscript{ } & 1.02\textsuperscript{ } & 1.052\textsuperscript{***} \\
							CMBPV1   & 1.156\textsuperscript{***} & 1.063\textsuperscript{ } & 1.072\textsuperscript{ } & 1.339\textsuperscript{ } & 0.954\textsuperscript{***} & 1.1\textsuperscript{***} \\
							CMJV1  & 1.074\textsuperscript{***} & 1.052\textsuperscript{*} & 1.007\textsuperscript{ } & \textbf{0.946\textsuperscript{***}} & 0.962\textsuperscript{***} & 1.193\textsuperscript{***} \\
							CMRV2   & 1.101\textsuperscript{***} & 1.045\textsuperscript{ } & 0.988\textsuperscript{***} & 1.061\textsuperscript{ } & 0.956\textsuperscript{***} & 1.072\textsuperscript{***} \\
							CMTRV2   & 1.107\textsuperscript{***} & 1.037\textsuperscript{ } & \textbf{0.986\textsuperscript{***}} & 1.103\textsuperscript{***} & 1.046\textsuperscript{ } & 1.061\textsuperscript{***} \\
							CMBPV2  & 1.138\textsuperscript{***} & 1.02\textsuperscript{ } & 1.018\textsuperscript{ } & 1.051\textsuperscript{ } & 0.996\textsuperscript{***} & 1.11\textsuperscript{***} \\
							CMJV2  & \textbf{1.015\textsuperscript{***}} & 1.001\textsuperscript{**} & 0.995\textsuperscript{***} & 0.952\textsuperscript{***} & 0.987\textsuperscript{***} & 1.127\textsuperscript{***} \\
							VRV   & 1.049\textsuperscript{***} & 1.079\textsuperscript{ } & 1.045\textsuperscript{ } & 1.006\textsuperscript{*} & 1.013\textsuperscript{ } & 1.05\textsuperscript{ } \\
							VTRV  & 1.051\textsuperscript{***} & 1.078\textsuperscript{ } & 1.045\textsuperscript{ } & 1.01\textsuperscript{ } & 1.015\textsuperscript{ } & 1.056\textsuperscript{ } \\
							VBPV   & 1.051\textsuperscript{***} & 1.083\textsuperscript{ } & 1.044\textsuperscript{ } & 1.004\textsuperscript{*} & 1.015\textsuperscript{ } & \textbf{1.043\textsuperscript{ }} \\
							VJV  & 1.025\textsuperscript{***} & \textbf{0.988\textsuperscript{***}} & 1.043\textsuperscript{***} & 1.03\textsuperscript{ } & 1.047\textsuperscript{***} & 1.13\textsuperscript{***} \\
							MRV  & 1.194\textsuperscript{***} & 1.107\textsuperscript{***} & 1.275\textsuperscript{***} & 1.156\textsuperscript{***} & 1.336\textsuperscript{***} & 1.446\textsuperscript{***} \\
							MTRV  & 1.197\textsuperscript{***} & 1.112\textsuperscript{***} & 1.282\textsuperscript{***} & 1.162\textsuperscript{***} & 1.346\textsuperscript{***} & 1.457\textsuperscript{***} \\
							MBPV   & 1.257\textsuperscript{***} & 1.147\textsuperscript{***} & 1.262\textsuperscript{***} & 1.153\textsuperscript{***} & 1.333\textsuperscript{***} & 1.434\textsuperscript{***} \\
							MJV   & 1.347\textsuperscript{***} & 1.191\textsuperscript{***} & 1.361\textsuperscript{***} & 1.408\textsuperscript{***} & 1.833\textsuperscript{***} & 2.031\textsuperscript{***} \\
							MVRV  & 1.084\textsuperscript{ } & 1.11\textsuperscript{***} & 1.085\textsuperscript{ } & 1.165\textsuperscript{***} & 1.302\textsuperscript{***} & 1.336\textsuperscript{***} \\
							MVTRV   & 1.087\textsuperscript{ } & 1.111\textsuperscript{***} & 1.086\textsuperscript{ } & 1.167\textsuperscript{***} & 1.306\textsuperscript{***} & 1.356\textsuperscript{***} \\
							MVBPV  & 1.083\textsuperscript{ } & 1.105\textsuperscript{***} & 1.083\textsuperscript{ } & 1.167\textsuperscript{***} & 1.294\textsuperscript{***} & 1.328\textsuperscript{***} \\
							MVJV   & 1.117\textsuperscript{**} & 1.1\textsuperscript{***} & 1.107\textsuperscript{***} & 1.149\textsuperscript{***} & 1.386\textsuperscript{***} & 1.328\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.001\textsuperscript{*} & 1.011\textsuperscript{ } & 1.049\textsuperscript{***} & 0.99\textsuperscript{***} & 0.954\textsuperscript{***} & 1.028\textsuperscript{ } \\
							RV   & 1.036\textsuperscript{ } & 1.106\textsuperscript{***} & 1.099\textsuperscript{*} & 1.052\textsuperscript{ } & 1.021\textsuperscript{ } & 0.997\textsuperscript{***} \\
							TRV   & 1.038\textsuperscript{ } & 1.106\textsuperscript{***} & 1.099\textsuperscript{*} & 1.053\textsuperscript{ } & 1.021\textsuperscript{ } & \textbf{0.995\textsuperscript{***}} \\
							BPV  & 1.037\textsuperscript{ } & 1.108\textsuperscript{***} & 1.101\textsuperscript{**} & 1.054\textsuperscript{ } & 1.023\textsuperscript{ } & 0.998\textsuperscript{***} \\
							JV  & 1.089\textsuperscript{ } & 1.139\textsuperscript{ } & 1.147\textsuperscript{*} & 1.162\textsuperscript{**} & 1.176\textsuperscript{***} & 1.139\textsuperscript{*} \\
							CMRV1   & \textbf{0.97\textsuperscript{***}} & 0.998\textsuperscript{***} & 1.005\textsuperscript{ } & 0.992\textsuperscript{***} & 0.999\textsuperscript{***} & 1.029\textsuperscript{***} \\
							CMTRV1   & 1.052\textsuperscript{***} & 1.011\textsuperscript{***} & 0.992\textsuperscript{***} & 1.013\textsuperscript{ } & 0.996\textsuperscript{***} & 1.016\textsuperscript{ } \\
							CMBPV1   & 0.97\textsuperscript{***} & 0.999\textsuperscript{***} & 1.005\textsuperscript{ } & 0.992\textsuperscript{***} & 0.999\textsuperscript{***} & 1.031\textsuperscript{***} \\
							CMJV1  & 0.977\textsuperscript{***} & 0.999\textsuperscript{***} & 1.009\textsuperscript{ } & 1.009\textsuperscript{ } & 0.991\textsuperscript{***} & 1.005\textsuperscript{ } \\
							CMRV2   & 1.022\textsuperscript{***} & 1.029\textsuperscript{***} & 0.992\textsuperscript{***} & \textbf{0.983\textsuperscript{***}} & \textbf{0.946\textsuperscript{***}} & 1.039\textsuperscript{ } \\
							CMTRV2   & 1.018\textsuperscript{***} & \textbf{0.993\textsuperscript{***}} & 0.999\textsuperscript{***} & 0.999\textsuperscript{***} & 1.036\textsuperscript{ } & 1.058\textsuperscript{***} \\
							CMBPV2  & 1.016\textsuperscript{***} & 1.014\textsuperscript{***} & \textbf{0.985\textsuperscript{***}} & 0.993\textsuperscript{***} & 0.978\textsuperscript{***} & 1.078\textsuperscript{***} \\
							CMJV2  & 0.973\textsuperscript{***} & 1.019\textsuperscript{ } & 1.011\textsuperscript{ } & 1.022\textsuperscript{ } & 1.009\textsuperscript{ } & 0.995\textsuperscript{***} \\
							VRV   & 0.977\textsuperscript{***} & 1.031\textsuperscript{ } & 1.042\textsuperscript{ } & 1.022\textsuperscript{ } & 0.992\textsuperscript{***} & 1.021\textsuperscript{***} \\
							VTRV  & 0.977\textsuperscript{***} & 1.032\textsuperscript{ } & 1.039\textsuperscript{ } & 1.022\textsuperscript{ } & 0.993\textsuperscript{***} & 1.021\textsuperscript{***} \\
							VBPV   & 0.976\textsuperscript{***} & 1.031\textsuperscript{ } & 1.043\textsuperscript{ } & 1.022\textsuperscript{ } & 0.993\textsuperscript{***} & 1.021\textsuperscript{***} \\
							VJV  & 0.983\textsuperscript{***} & 1.02\textsuperscript{ } & 1.032\textsuperscript{***} & 1.007\textsuperscript{ } & 0.999\textsuperscript{***} & 1.044\textsuperscript{***} \\
							MRV  & 1.088\textsuperscript{***} & 1.116\textsuperscript{***} & 1.146\textsuperscript{***} & 1.048\textsuperscript{*} & 1.031\textsuperscript{ } & 1.089\textsuperscript{***} \\
							MTRV  & 1.091\textsuperscript{***} & 1.118\textsuperscript{***} & 1.154\textsuperscript{***} & 1.041\textsuperscript{ } & 1.034\textsuperscript{ } & 1.092\textsuperscript{***} \\
							MBPV   & 1.087\textsuperscript{***} & 1.13\textsuperscript{***} & 1.145\textsuperscript{***} & 1.043\textsuperscript{ } & 1.021\textsuperscript{ } & 1.09\textsuperscript{***} \\
							MJV   & 1.166\textsuperscript{***} & 1.175\textsuperscript{***} & 1.284\textsuperscript{***} & 1.229\textsuperscript{***} & 1.17\textsuperscript{***} & 1.173\textsuperscript{***} \\
							MVRV  & 1.02\textsuperscript{ } & 1.058\textsuperscript{ } & 1.067\textsuperscript{***} & 0.998\textsuperscript{***} & 0.975\textsuperscript{***} & 1.04\textsuperscript{***} \\
							MVTRV   & 1.02\textsuperscript{ } & 1.055\textsuperscript{ } & 1.07\textsuperscript{***} & 0.996\textsuperscript{***} & 0.975\textsuperscript{***} & 1.038\textsuperscript{***} \\
							MVBPV  & 1.021\textsuperscript{ } & 1.059\textsuperscript{ } & 1.065\textsuperscript{***} & 0.997\textsuperscript{***} & 0.979\textsuperscript{***} & 1.043\textsuperscript{***} \\
							MVJV   & 1.01\textsuperscript{ } & 1.039\textsuperscript{ } & 1.065\textsuperscript{***} & 1.006\textsuperscript{ } & 0.983\textsuperscript{***} & 1.031\textsuperscript{ } \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			\newpage
			\renewcommand{\thetable}{A3C} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Consumer Price Index (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA3C}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & \textbf{72.2\%\textsuperscript{***}} & 75.9\%\textsuperscript{***} & \textbf{81\%\textsuperscript{***}} & 79.7\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & \textbf{77.2\%\textsuperscript{***}} \\
							MMF  & 65.8\%\textsuperscript{***} & \textbf{81\%\textsuperscript{***}} & 75.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							RV   & 65.8\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & \textbf{82.3\%\textsuperscript{***}} & 73.4\%\textsuperscript{***} \\
							TRV   & 63.3\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 82.3\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							BPV  & 64.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 82.3\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							JV  & 60.8\%\textsuperscript{**} & 62\%\textsuperscript{***} & 60.8\%\textsuperscript{**} & 64.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 63.3\%\textsuperscript{***} \\
							CMRV1   & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 81\%\textsuperscript{***} & 82.3\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMTRV1   & 65.8\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 81\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMBPV1   & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & \textbf{83.5\%\textsuperscript{***}} & 82.3\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMJV1  & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 82.3\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							CMRV2   & 69.6\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 82.3\%\textsuperscript{***} & 82.3\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMTRV2   & 67.1\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 81\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMBPV2  & 67.1\%\textsuperscript{***} & 81\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 82.3\%\textsuperscript{***} & 81\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMJV2  & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 81\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							VRV   & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 77.2\%\textsuperscript{***} \\
							VTRV  & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 77.2\%\textsuperscript{***} \\
							VBPV   & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 75.9\%\textsuperscript{***} \\
							VJV  & 68.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 75.9\%\textsuperscript{***} \\
							MRV  & 65.8\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							MTRV  & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							MBPV   & 65.8\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							MJV   & 59.5\%\textsuperscript{**} & 69.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MVRV  & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							MVTRV   & 68.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							MVBPV  & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							MVJV   & 72.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 68.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & \textbf{79.7\%\textsuperscript{***}} & 75.9\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							MMF  & 68.4\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							RV   & 65.8\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							TRV   & 65.8\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							BPV  & 65.8\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							JV  & 67.1\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							CMRV1   & 68.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMTRV1   & 67.1\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							CMBPV1   & 68.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMJV1  & \textbf{69.6\%\textsuperscript{***}} & 78.5\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							CMRV2   & 68.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & \textbf{78.5\%\textsuperscript{***}} & 77.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							CMTRV2   & 69.6\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} \\
							CMBPV2  & 67.1\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							CMJV2  & 69.6\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							VRV   & 69.6\%\textsuperscript{***} & \textbf{81\%\textsuperscript{***}} & 78.5\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							VTRV  & 69.6\%\textsuperscript{***} & 81\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							VBPV   & 69.6\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							VJV  & 69.6\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							MRV  & 63.3\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & \textbf{81\%\textsuperscript{***}} & 74.7\%\textsuperscript{***} \\
							MTRV  & 63.3\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 81\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							MBPV   & 63.3\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 81\%\textsuperscript{***} & 74.7\%\textsuperscript{***} \\
							MJV   & 60.8\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 81\%\textsuperscript{***} & \textbf{78.5\%\textsuperscript{***}} \\
							MVRV  & 68.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							MVTRV   & 68.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							MVBPV  & 68.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							MVJV   & 68.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} \\
							
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			\newpage
			\renewcommand{\thetable}{A3D} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Consumer Price Index (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA3D}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & \textbf{72.1\%\textsuperscript{***}} & 74.4\%\textsuperscript{***} & \textbf{81.4\%\textsuperscript{***}} & \textbf{79.1\%\textsuperscript{***}} & 79.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							MMF  & 62.8\%\textsuperscript{**} & \textbf{81.4\%\textsuperscript{***}} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & \textbf{79.1\%\textsuperscript{***}} \\
							RV   & 58.1\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & \textbf{81.4\%\textsuperscript{***}} & 74.4\%\textsuperscript{***} \\
							TRV   & 55.8\%\textsuperscript{*} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							BPV  & 55.8\%\textsuperscript{*} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							JV  & 60.5\%\textsuperscript{*} & 62.8\%\textsuperscript{**} & 65.1\%\textsuperscript{***} & 58.1\%\textsuperscript{*} & 62.8\%\textsuperscript{**} & 67.4\%\textsuperscript{***} \\
							CMRV1   & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMTRV1   & 62.8\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMBPV1   & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMJV1  & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMRV2   & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMTRV2   & 65.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMBPV2  & 65.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMJV2  & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							VRV   & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							VTRV  & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							VBPV   & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							VJV  & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MRV  & 60.5\%\textsuperscript{**} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MTRV  & 62.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MBPV   & 60.5\%\textsuperscript{**} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MJV   & 55.8\%\textsuperscript{ } & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 62.8\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							MVRV  & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MVTRV   & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MVBPV  & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							MVJV   & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 69.8\%\textsuperscript{***} & \textbf{81.4\%\textsuperscript{***}} & \textbf{83.7\%\textsuperscript{***}} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							MMF  & 69.8\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & \textbf{74.4\%\textsuperscript{***}} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							RV   & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							TRV   & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							BPV  & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							JV  & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & \textbf{81.4\%\textsuperscript{***}} & 79.1\%\textsuperscript{***} \\
							CMRV1   & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							CMTRV1   & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMBPV1   & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							CMJV1  & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMRV2   & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} \\
							CMTRV2   & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMBPV2  & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							CMJV2  & 72.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							VRV   & \textbf{74.4\%\textsuperscript{***}} & 81.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							VTRV  & 74.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							VBPV   & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							VJV  & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 83.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							MRV  & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MTRV  & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MBPV   & 65.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MJV   & 58.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & \textbf{81.4\%\textsuperscript{***}} \\
							MVRV  & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MVTRV   & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MVBPV  & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 81.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} \\
							MVJV   & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------			
			
			
			
			\newpage
			\renewcommand{\thetable}{A4A} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Personal Consumption Expenditures (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA4A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.156\textsuperscript{***} & 1.041\textsuperscript{ } & 1.074\textsuperscript{ } & 1.063\textsuperscript{ } & 0.986\textsuperscript{***} & 1.111\textsuperscript{ } \\
							RV   & 1.096\textsuperscript{***} & 1.03\textsuperscript{ } & 1.044\textsuperscript{ } & 1.036\textsuperscript{ } & 1.055\textsuperscript{ } & 1.17\textsuperscript{***} \\
							TRV   & 1.119\textsuperscript{***} & 1.029\textsuperscript{ } & 1.047\textsuperscript{ } & 1.043\textsuperscript{ } & 1.07\textsuperscript{ } & 1.182\textsuperscript{***} \\
							BPV  & 1.093\textsuperscript{***} & 1.031\textsuperscript{ } & 1.044\textsuperscript{ } & 1.034\textsuperscript{ } & 1.052\textsuperscript{ } & 1.162\textsuperscript{***} \\
							JV  & 2.033\textsuperscript{***} & 1.702\textsuperscript{***} & 1.654\textsuperscript{***} & 1.889\textsuperscript{***} & 2.573\textsuperscript{***} & 2.674\textsuperscript{***} \\
							CMRV1   & 1.041\textsuperscript{***} & 1.004\textsuperscript{ } & 1.091\textsuperscript{***} & 1.016\textsuperscript{ } & 0.953\textsuperscript{***} & 1.075\textsuperscript{ } \\
							CMTRV1   & 1.048\textsuperscript{***} & 1.04\textsuperscript{ } & 1.098\textsuperscript{***} & 1.064\textsuperscript{***} & 1.028\textsuperscript{ } & 0.982\textsuperscript{***} \\
							CMBPV1   & 1.03\textsuperscript{ } & \textbf{1\textsuperscript{***}} & 1.088\textsuperscript{***} & 1.019\textsuperscript{ } & 0.954\textsuperscript{***} & 1.078\textsuperscript{ } \\
							CMJV1  & 1.062\textsuperscript{***} & 1.005\textsuperscript{ } & 1.025\textsuperscript{ } & 0.997\textsuperscript{***} & 0.98\textsuperscript{***} & 0.974\textsuperscript{***} \\
							CMRV2   & \textbf{1.008\textsuperscript{ }} & 1.03\textsuperscript{ } & 1.083\textsuperscript{***} & 1.027\textsuperscript{***} & 1.005\textsuperscript{ } & 0.998\textsuperscript{***} \\
							CMTRV2   & 1.031\textsuperscript{***} & 1.04\textsuperscript{ } & 1.098\textsuperscript{***} & 1.057\textsuperscript{***} & 1.059\textsuperscript{***} & 1.001\textsuperscript{***} \\
							CMBPV2  & 1.043\textsuperscript{*} & 1.072\textsuperscript{***} & 1.106\textsuperscript{***} & 1.035\textsuperscript{***} & 1.031\textsuperscript{ } & 0.995\textsuperscript{***} \\
							CMJV2  & 1.035\textsuperscript{ } & 1.011\textsuperscript{ } & 1.024\textsuperscript{ } & \textbf{0.986\textsuperscript{***}} & 0.957\textsuperscript{***} & \textbf{0.973\textsuperscript{***}} \\
							VRV   & 1.044\textsuperscript{*} & 1.047\textsuperscript{***} & 1.048\textsuperscript{*} & 1.067\textsuperscript{***} & 0.945\textsuperscript{***} & 1.055\textsuperscript{ } \\
							VTRV  & 1.043\textsuperscript{ } & 1.05\textsuperscript{***} & 1.043\textsuperscript{ } & 1.069\textsuperscript{***} & 0.946\textsuperscript{***} & 1.055\textsuperscript{ } \\
							VBPV   & 1.044\textsuperscript{*} & 1.046\textsuperscript{***} & 1.052\textsuperscript{**} & 1.069\textsuperscript{***} & 0.947\textsuperscript{***} & 1.06\textsuperscript{ } \\
							VJV  & 1.022\textsuperscript{ } & 1.029\textsuperscript{**} & \textbf{1.02\textsuperscript{ }} & 1.019\textsuperscript{ } & \textbf{0.943\textsuperscript{***}} & 1.045\textsuperscript{ } \\
							MRV  & 1.3\textsuperscript{***} & 1.082\textsuperscript{**} & 1.089\textsuperscript{ } & 1.111\textsuperscript{ } & 1.045\textsuperscript{ } & 1.24\textsuperscript{***} \\
							MTRV  & 1.31\textsuperscript{***} & 1.079\textsuperscript{**} & 1.102\textsuperscript{***} & 1.117\textsuperscript{ } & 1.051\textsuperscript{ } & 1.241\textsuperscript{***} \\
							MBPV   & 1.305\textsuperscript{***} & 1.084\textsuperscript{***} & 1.102\textsuperscript{**} & 1.113\textsuperscript{ } & 1.044\textsuperscript{ } & 1.239\textsuperscript{***} \\
							MJV   & 1.528\textsuperscript{***} & 1.205\textsuperscript{***} & 1.339\textsuperscript{***} & 1.329\textsuperscript{***} & 1.47\textsuperscript{***} & 1.573\textsuperscript{***} \\
							MVRV  & 1.185\textsuperscript{***} & 1.101\textsuperscript{***} & 1.146\textsuperscript{***} & 1.076\textsuperscript{ } & 1.01\textsuperscript{*} & 1.154\textsuperscript{ } \\
							MVTRV   & 1.191\textsuperscript{***} & 1.091\textsuperscript{**} & 1.151\textsuperscript{***} & 1.075\textsuperscript{ } & 1.012\textsuperscript{*} & 1.15\textsuperscript{ } \\
							MVBPV  & 1.181\textsuperscript{***} & 1.105\textsuperscript{***} & 1.145\textsuperscript{***} & 1.079\textsuperscript{ } & 1.001\textsuperscript{***} & 1.158\textsuperscript{ } \\
							MVJV   & 1.203\textsuperscript{***} & 1.071\textsuperscript{ } & 1.181\textsuperscript{***} & 1.124\textsuperscript{ } & 0.992\textsuperscript{***} & 1.186\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.034\textsuperscript{ } & 1.044\textsuperscript{ } & 1.015\textsuperscript{ } & 1.043\textsuperscript{ } & 0.998\textsuperscript{***} & \textbf{0.952\textsuperscript{***}} \\
							RV   & 1.099\textsuperscript{***} & 1.141\textsuperscript{***} & 1.161\textsuperscript{***} & 1.196\textsuperscript{***} & 1.142\textsuperscript{***} & 1.201\textsuperscript{***} \\
							TRV   & 1.101\textsuperscript{***} & 1.142\textsuperscript{***} & 1.16\textsuperscript{***} & 1.196\textsuperscript{***} & 1.146\textsuperscript{***} & 1.205\textsuperscript{***} \\
							BPV  & 1.101\textsuperscript{***} & 1.142\textsuperscript{***} & 1.162\textsuperscript{***} & 1.195\textsuperscript{***} & 1.14\textsuperscript{***} & 1.191\textsuperscript{***} \\
							JV  & 1.304\textsuperscript{***} & 1.376\textsuperscript{***} & 1.424\textsuperscript{***} & 1.58\textsuperscript{***} & 1.629\textsuperscript{***} & 1.586\textsuperscript{***} \\
							CMRV1   & 1.029\textsuperscript{***} & 1.021\textsuperscript{ } & 1.069\textsuperscript{***} & 1.045\textsuperscript{***} & 1.005\textsuperscript{ } & 1.012\textsuperscript{ } \\
							CMTRV1   & 0.988\textsuperscript{***} & 1.049\textsuperscript{***} & 1.054\textsuperscript{***} & 1.041\textsuperscript{***} & 1.002\textsuperscript{**} & 0.988\textsuperscript{***} \\
							CMBPV1   & 1.026\textsuperscript{**} & 1.02\textsuperscript{ } & 1.07\textsuperscript{***} & 1.033\textsuperscript{***} & 1.006\textsuperscript{ } & 1.013\textsuperscript{ } \\
							CMJV1  & 1.025\textsuperscript{*} & 1.019\textsuperscript{ } & 1.027\textsuperscript{***} & 1.029\textsuperscript{ } & 0.955\textsuperscript{***} & 1.014\textsuperscript{ } \\
							CMRV2   & 0.996\textsuperscript{***} & 1.067\textsuperscript{***} & 1.054\textsuperscript{***} & 1.031\textsuperscript{**} & 1.004\textsuperscript{ } & 0.972\textsuperscript{***} \\
							CMTRV2   & 0.995\textsuperscript{***} & \textbf{1.008\textsuperscript{ }} & 1.079\textsuperscript{***} & 1.055\textsuperscript{***} & 1.031\textsuperscript{***} & 1.012\textsuperscript{ } \\
							CMBPV2  & \textbf{0.977\textsuperscript{***}} & 1.063\textsuperscript{***} & 1.061\textsuperscript{***} & 1.031\textsuperscript{***} & 1.029\textsuperscript{*} & 0.987\textsuperscript{***} \\
							CMJV2  & 1.028\textsuperscript{ } & 1.038\textsuperscript{***} & 1.047\textsuperscript{***} & 1.048\textsuperscript{***} & 1.03\textsuperscript{ } & 1.014\textsuperscript{ } \\
							VRV   & 1.069\textsuperscript{***} & 1.086\textsuperscript{***} & 1.07\textsuperscript{***} & 1.089\textsuperscript{***} & 1.029\textsuperscript{ } & 1.098\textsuperscript{***} \\
							VTRV  & 1.069\textsuperscript{***} & 1.089\textsuperscript{***} & 1.067\textsuperscript{***} & 1.087\textsuperscript{***} & 1.029\textsuperscript{ } & 1.097\textsuperscript{***} \\
							VBPV   & 1.068\textsuperscript{***} & 1.086\textsuperscript{***} & 1.068\textsuperscript{***} & 1.089\textsuperscript{***} & 1.026\textsuperscript{ } & 1.098\textsuperscript{***} \\
							VJV  & 1.08\textsuperscript{ } & 1.058\textsuperscript{***} & 1.069\textsuperscript{***} & 1.046\textsuperscript{***} & 1.087\textsuperscript{***} & 1.022\textsuperscript{ } \\
							MRV  & 1.086\textsuperscript{***} & 1.115\textsuperscript{***} & 1.046\textsuperscript{*} & 1.064\textsuperscript{***} & 0.994\textsuperscript{***} & 0.985\textsuperscript{***} \\
							MTRV  & 1.089\textsuperscript{***} & 1.113\textsuperscript{***} & 1.044\textsuperscript{ } & 1.057\textsuperscript{***} & 0.995\textsuperscript{***} & 0.987\textsuperscript{***} \\
							MBPV   & 1.086\textsuperscript{***} & 1.115\textsuperscript{***} & 1.045\textsuperscript{*} & 1.064\textsuperscript{***} & 0.993\textsuperscript{***} & 0.986\textsuperscript{***} \\
							MJV   & 1.164\textsuperscript{***} & 1.156\textsuperscript{***} & 1.106\textsuperscript{***} & 1.184\textsuperscript{***} & 1.182\textsuperscript{***} & 1.175\textsuperscript{***} \\
							MVRV  & 1.032\textsuperscript{ } & 1.047\textsuperscript{*} & \textbf{0.991\textsuperscript{***}} & 1.028\textsuperscript{ } & 0.969\textsuperscript{***} & 0.96\textsuperscript{***} \\
							MVTRV   & 1.034\textsuperscript{ } & 1.047\textsuperscript{*} & 0.993\textsuperscript{***} & \textbf{1.025\textsuperscript{ }} & 0.966\textsuperscript{***} & 0.956\textsuperscript{***} \\
							MVBPV  & 1.032\textsuperscript{ } & 1.047\textsuperscript{*} & 0.991\textsuperscript{***} & 1.028\textsuperscript{ } & \textbf{0.948\textsuperscript{***}} & 0.965\textsuperscript{***} \\
							MVJV   & 1.029\textsuperscript{ } & 1.029\textsuperscript{ } & 1.009\textsuperscript{ } & 1.046\textsuperscript{***} & 0.976\textsuperscript{***} & 0.96\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes on Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			\newpage
			\renewcommand{\thetable}{A4B} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Personal Consumption Expenditures (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA4B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.172\textsuperscript{***} & 1.013\textsuperscript{ } & 1.095\textsuperscript{ } & 1.063\textsuperscript{ } & 0.994\textsuperscript{***} & 1.153\textsuperscript{ } \\
							RV   & 1.115\textsuperscript{**} & 1.055\textsuperscript{**} & 1.092\textsuperscript{***} & 1.101\textsuperscript{***} & 1.158\textsuperscript{***} & 1.331\textsuperscript{***} \\
							TRV   & 1.15\textsuperscript{***} & 1.064\textsuperscript{***} & 1.099\textsuperscript{***} & 1.108\textsuperscript{***} & 1.175\textsuperscript{***} & 1.346\textsuperscript{***} \\
							BPV  & 1.113\textsuperscript{***} & 1.054\textsuperscript{**} & 1.092\textsuperscript{***} & 1.096\textsuperscript{***} & 1.146\textsuperscript{***} & 1.315\textsuperscript{***} \\
							JV  & 2.274\textsuperscript{***} & 1.581\textsuperscript{***} & 1.583\textsuperscript{***} & 1.871\textsuperscript{***} & 3.079\textsuperscript{***} & 3.348\textsuperscript{***} \\
							CMRV1   & 1.037\textsuperscript{ } & 0.989\textsuperscript{***} & 1.102\textsuperscript{***} & 1.033\textsuperscript{***} & 1.04\textsuperscript{***} & 1.094\textsuperscript{ } \\
							CMTRV1   & 1.046\textsuperscript{***} & 0.997\textsuperscript{***} & 1.059\textsuperscript{**} & 1.063\textsuperscript{***} & 1.033\textsuperscript{ } & \textbf{0.962\textsuperscript{***}} \\
							CMBPV1   & 1.025\textsuperscript{ } & 0.985\textsuperscript{***} & 1.103\textsuperscript{***} & 1.035\textsuperscript{***} & 1.041\textsuperscript{***} & 1.092\textsuperscript{ } \\
							CMJV1  & 1.061\textsuperscript{ } & 1.003\textsuperscript{*} & 1.034\textsuperscript{*} & 1.02\textsuperscript{ } & 1.083\textsuperscript{**} & 1.051\textsuperscript{ } \\
							CMRV2   & \textbf{0.992\textsuperscript{***}} & \textbf{0.977\textsuperscript{***}} & 1.065\textsuperscript{***} & 1.022\textsuperscript{ } & 1.009\textsuperscript{ } & 0.976\textsuperscript{***} \\
							CMTRV2   & 1.004\textsuperscript{ } & 1.005\textsuperscript{*} & 1.07\textsuperscript{***} & 1.042\textsuperscript{***} & 1.095\textsuperscript{***} & 0.996\textsuperscript{***} \\
							CMBPV2  & 1.003\textsuperscript{*} & 1.043\textsuperscript{ } & 1.074\textsuperscript{***} & 1.029\textsuperscript{ } & 1.047\textsuperscript{ } & 0.968\textsuperscript{***} \\
							CMJV2  & 1.02\textsuperscript{ } & 0.997\textsuperscript{***} & \textbf{1.011\textsuperscript{ }} & \textbf{1.016\textsuperscript{ }} & 1.02\textsuperscript{ } & 1.087\textsuperscript{ } \\
							VRV   & 1.058\textsuperscript{ } & 1.03\textsuperscript{ } & 1.105\textsuperscript{***} & 1.067\textsuperscript{***} & \textbf{0.992\textsuperscript{***}} & 1.114\textsuperscript{ } \\
							VTRV  & 1.057\textsuperscript{ } & 1.034\textsuperscript{*} & 1.097\textsuperscript{***} & 1.07\textsuperscript{***} & 0.994\textsuperscript{***} & 1.114\textsuperscript{ } \\
							VBPV   & 1.058\textsuperscript{ } & 1.031\textsuperscript{ } & 1.108\textsuperscript{***} & 1.069\textsuperscript{***} & 0.992\textsuperscript{***} & 1.113\textsuperscript{*} \\
							VJV  & 1.043\textsuperscript{ } & 0.991\textsuperscript{***} & 1.045\textsuperscript{***} & 1.016\textsuperscript{ } & 1.011\textsuperscript{ } & 1.116\textsuperscript{ } \\
							MRV  & 1.384\textsuperscript{***} & 1.102\textsuperscript{**} & 1.147\textsuperscript{***} & 1.192\textsuperscript{***} & 1.122\textsuperscript{**} & 1.374\textsuperscript{***} \\
							MTRV  & 1.403\textsuperscript{***} & 1.102\textsuperscript{***} & 1.152\textsuperscript{***} & 1.2\textsuperscript{***} & 1.129\textsuperscript{***} & 1.375\textsuperscript{***} \\
							MBPV   & 1.389\textsuperscript{***} & 1.103\textsuperscript{**} & 1.147\textsuperscript{***} & 1.194\textsuperscript{***} & 1.119\textsuperscript{*} & 1.371\textsuperscript{***} \\
							MJV   & 1.696\textsuperscript{***} & 1.205\textsuperscript{***} & 1.441\textsuperscript{***} & 1.421\textsuperscript{***} & 1.649\textsuperscript{***} & 1.825\textsuperscript{***} \\
							MVRV  & 1.147\textsuperscript{**} & 1.093\textsuperscript{ } & 1.143\textsuperscript{ } & 1.108\textsuperscript{ } & 1.077\textsuperscript{ } & 1.249\textsuperscript{ } \\
							MVTRV   & 1.154\textsuperscript{***} & 1.08\textsuperscript{ } & 1.15\textsuperscript{ } & 1.108\textsuperscript{ } & 1.08\textsuperscript{ } & 1.243\textsuperscript{ } \\
							MVBPV  & 1.144\textsuperscript{**} & 1.1\textsuperscript{ } & 1.142\textsuperscript{ } & 1.109\textsuperscript{ } & 1.074\textsuperscript{ } & 1.254\textsuperscript{*} \\
							MVJV   & 1.16\textsuperscript{***} & 1.049\textsuperscript{ } & 1.23\textsuperscript{***} & 1.098\textsuperscript{ } & 1.024\textsuperscript{ } & 1.343\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1\textsuperscript{***} & 1.017\textsuperscript{ } & 0.966\textsuperscript{***} & 0.968\textsuperscript{***} & 0.941\textsuperscript{***} & \textbf{0.858\textsuperscript{***}} \\
							RV   & 0.983\textsuperscript{***} & 1\textsuperscript{***} & 1.068\textsuperscript{***} & 1.148\textsuperscript{***} & 1.171\textsuperscript{***} & 1.289\textsuperscript{***} \\
							TRV   & 0.982\textsuperscript{***} & 1.001\textsuperscript{**} & 1.07\textsuperscript{***} & 1.153\textsuperscript{***} & 1.179\textsuperscript{***} & 1.295\textsuperscript{***} \\
							BPV  & 0.984\textsuperscript{***} & 1\textsuperscript{***} & 1.067\textsuperscript{***} & 1.145\textsuperscript{***} & 1.167\textsuperscript{***} & 1.274\textsuperscript{***} \\
							JV  & 1.133\textsuperscript{**} & 1.177\textsuperscript{***} & 1.307\textsuperscript{***} & 1.494\textsuperscript{***} & 1.73\textsuperscript{***} & 1.747\textsuperscript{***} \\
							CMRV1   & 1.023\textsuperscript{***} & 0.999\textsuperscript{***} & 1.056\textsuperscript{***} & 1.015\textsuperscript{ } & 0.995\textsuperscript{***} & 1.017\textsuperscript{ } \\
							CMTRV1   & 0.993\textsuperscript{***} & 1.023\textsuperscript{ } & 1.018\textsuperscript{*} & 0.993\textsuperscript{***} & 0.955\textsuperscript{***} & 0.967\textsuperscript{***} \\
							CMBPV1   & 1.019\textsuperscript{***} & 0.997\textsuperscript{***} & 1.05\textsuperscript{***} & 0.998\textsuperscript{***} & 0.995\textsuperscript{***} & 1.018\textsuperscript{ } \\
							CMJV1  & 1.018\textsuperscript{ } & 1.008\textsuperscript{ } & 1.004\textsuperscript{ } & 0.994\textsuperscript{***} & 0.919\textsuperscript{***} & 1.017\textsuperscript{ } \\
							CMRV2   & 0.993\textsuperscript{***} & 1.034\textsuperscript{ } & 1.03\textsuperscript{***} & 0.996\textsuperscript{***} & 0.967\textsuperscript{***} & 0.941\textsuperscript{***} \\
							CMTRV2   & 0.988\textsuperscript{***} & \textbf{0.994\textsuperscript{***}} & 1.04\textsuperscript{***} & 0.996\textsuperscript{***} & 1.007\textsuperscript{ } & 1.002\textsuperscript{**} \\
							CMBPV2  & 0.98\textsuperscript{***} & 1.05\textsuperscript{ } & 1.025\textsuperscript{***} & 0.983\textsuperscript{***} & 0.99\textsuperscript{***} & 0.969\textsuperscript{***} \\
							CMJV2  & 0.99\textsuperscript{***} & 1.015\textsuperscript{ } & 1.019\textsuperscript{ } & 1.008\textsuperscript{ } & 1.036\textsuperscript{ } & 1.021\textsuperscript{ } \\
							VRV   & 1.045\textsuperscript{***} & 1.052\textsuperscript{***} & 1.031\textsuperscript{***} & 1.083\textsuperscript{***} & 1.026\textsuperscript{ } & 1.146\textsuperscript{***} \\
							VTRV  & 1.044\textsuperscript{***} & 1.052\textsuperscript{***} & 1.029\textsuperscript{ } & 1.082\textsuperscript{***} & 1.027\textsuperscript{ } & 1.146\textsuperscript{***} \\
							VBPV   & 1.043\textsuperscript{***} & 1.054\textsuperscript{***} & 1.028\textsuperscript{**} & 1.085\textsuperscript{***} & 1.023\textsuperscript{ } & 1.146\textsuperscript{***} \\
							VJV  & 1.101\textsuperscript{ } & 1.014\textsuperscript{ } & 1.073\textsuperscript{***} & 1.005\textsuperscript{ } & 1.111\textsuperscript{***} & 1.023\textsuperscript{ } \\
							MRV  & 0.998\textsuperscript{***} & 1.051\textsuperscript{ } & 0.995\textsuperscript{***} & 1.039\textsuperscript{ } & 0.968\textsuperscript{***} & 0.94\textsuperscript{***} \\
							MTRV  & 1\textsuperscript{***} & 1.053\textsuperscript{ } & 1\textsuperscript{***} & 1.041\textsuperscript{ } & 0.971\textsuperscript{***} & 0.94\textsuperscript{***} \\
							MBPV   & 0.998\textsuperscript{***} & 1.049\textsuperscript{ } & 0.994\textsuperscript{***} & 1.039\textsuperscript{ } & 0.967\textsuperscript{***} & 0.94\textsuperscript{***} \\
							MJV   & 1.047\textsuperscript{ } & 1.114\textsuperscript{***} & 1.126\textsuperscript{***} & 1.196\textsuperscript{***} & 1.151\textsuperscript{***} & 1.123\textsuperscript{**} \\
							MVRV  & 0.993\textsuperscript{***} & 1.006\textsuperscript{ } & \textbf{0.934\textsuperscript{***}} & 0.963\textsuperscript{***} & 0.922\textsuperscript{***} & 0.903\textsuperscript{***} \\
							MVTRV   & 0.993\textsuperscript{***} & 1.006\textsuperscript{ } & 0.936\textsuperscript{***} & 0.963\textsuperscript{***} & 0.921\textsuperscript{***} & 0.898\textsuperscript{***} \\
							MVBPV  & 0.993\textsuperscript{***} & 1.005\textsuperscript{*} & 0.934\textsuperscript{***} & \textbf{0.962\textsuperscript{***}} & \textbf{0.894\textsuperscript{***}} & 0.906\textsuperscript{***} \\
							MVJV   & \textbf{0.979\textsuperscript{***}} & 1.009\textsuperscript{ } & 0.957\textsuperscript{***} & 0.996\textsuperscript{***} & 0.908\textsuperscript{***} & 0.963\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			\newpage
			\renewcommand{\thetable}{A4C} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Personal Consumption Expenditures (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA4C}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & \textbf{75.9\%\textsuperscript{***}} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & \textbf{81\%\textsuperscript{***}} & 72.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MMF  & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & \textbf{72.2\%\textsuperscript{***}} \\
							RV   & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							TRV   & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							BPV  & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & \textbf{77.2\%\textsuperscript{***}} & 67.1\%\textsuperscript{***} \\
							JV  & 63.3\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 59.5\%\textsuperscript{**} & 67.1\%\textsuperscript{***} & 64.6\%\textsuperscript{***} \\
							CMRV1   & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							CMTRV1   & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & \textbf{74.7\%\textsuperscript{***}} & 74.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							CMBPV1   & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							CMJV1  & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 81\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							CMRV2   & 72.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							CMTRV2   & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMBPV2  & 72.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							CMJV2  & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							VRV   & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							VTRV  & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							VBPV   & 72.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							VJV  & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 79.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MRV  & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 63.3\%\textsuperscript{***} \\
							MTRV  & 73.4\%\textsuperscript{***} & \textbf{74.7\%\textsuperscript{***}} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 63.3\%\textsuperscript{***} \\
							MBPV   & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 63.3\%\textsuperscript{***} \\
							MJV   & 65.8\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MVRV  & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							MVTRV   & 72.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MVBPV  & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							MVJV   & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & \textbf{78.5\%\textsuperscript{***}} & 67.1\%\textsuperscript{***} & \textbf{72.2\%\textsuperscript{***}} \\
							MMF  & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							RV   & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							TRV   & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							BPV  & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							JV  & 64.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & 64.6\%\textsuperscript{***} \\
							CMRV1   & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							CMTRV1   & \textbf{77.2\%\textsuperscript{***}} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							CMBPV1   & 74.7\%\textsuperscript{***} & \textbf{70.9\%\textsuperscript{***}} & 69.6\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							CMJV1  & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							CMRV2   & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***ss} \\
							CMTRV2   & 77.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMBPV2  & 77.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							CMJV2  & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							VRV   & 75.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & \textbf{74.7\%\textsuperscript{***}} & 75.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							VTRV  & 75.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							VBPV   & 75.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							VJV  & 74.7\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							MRV  & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							MTRV  & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & \textbf{75.9\%\textsuperscript{***}} & 69.6\%\textsuperscript{***} \\
							MBPV   & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							MJV   & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MVRV  & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MVTRV   & 72.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MVBPV  & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MVJV   & 72.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			\newpage
			\renewcommand{\thetable}{A4D} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Personal Consumption Expenditures (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA4D}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & \textbf{81.4\%\textsuperscript{***}} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{***} & \textbf{79.1\%\textsuperscript{***}} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							MMF  & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & \textbf{72.1\%\textsuperscript{***}} \\
							RV   & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							TRV   & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 58.1\%\textsuperscript{*} \\
							BPV  & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							JV  & 62.8\%\textsuperscript{**} & 60.5\%\textsuperscript{*} & 62.8\%\textsuperscript{**} & 55.8\%\textsuperscript{ } & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{***} \\
							CMRV1   & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							CMTRV1   & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & \textbf{72.1\%\textsuperscript{***}} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							CMBPV1   & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							CMJV1  & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							CMRV2   & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{**} & 74.4\%\textsuperscript{***} & \textbf{79.1\%\textsuperscript{***}} & 67.4\%\textsuperscript{***} \\
							CMTRV2   & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							CMBPV2  & 76.7\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMJV2  & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 62.8\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 60.5\%\textsuperscript{*} \\
							VRV   & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{***} \\
							VTRV  & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{***} \\
							VBPV   & 74.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 65.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{***} \\
							VJV  & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 62.8\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							MRV  & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							MTRV  & 74.4\%\textsuperscript{***} & \textbf{72.1\%\textsuperscript{***}} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							MBPV   & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 55.8\%\textsuperscript{ } \\
							MJV   & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{**} & 58.1\%\textsuperscript{ } & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							MVRV  & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							MVTRV   & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MVBPV  & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							MVJV   & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 79.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MMF  & 72.1\%\textsuperscript{***} & \textbf{69.8\%\textsuperscript{***}} & 65.1\%\textsuperscript{**} & \textbf{79.1\%\textsuperscript{***}} & 69.8\%\textsuperscript{***} & \textbf{72.1\%\textsuperscript{***}} \\
							RV   & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 60.5\%\textsuperscript{**} \\
							TRV   & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 60.5\%\textsuperscript{**} \\
							BPV  & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 60.5\%\textsuperscript{**} \\
							JV  & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{***} & 65.1\%\textsuperscript{***} \\
							CMRV1   & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							CMTRV1   & \textbf{81.4\%\textsuperscript{***}} & 65.1\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							CMBPV1   & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							CMJV1  & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							CMRV2   & 79.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							CMTRV2   & 81.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 62.8\%\textsuperscript{**} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMBPV2  & 81.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							CMJV2  & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 65.1\%\textsuperscript{***} \\
							VRV   & 81.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & \textbf{69.8\%\textsuperscript{***}} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							VTRV  & 81.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							VBPV   & 81.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							VJV  & 79.1\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MRV  & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & \textbf{76.7\%\textsuperscript{***}} & 62.8\%\textsuperscript{**} \\
							MTRV  & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							MBPV   & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							MJV   & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{***} \\
							MVRV  & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 60.5\%\textsuperscript{*} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MVTRV   & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MVBPV  & 74.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 60.5\%\textsuperscript{*} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MVJV   & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{**} & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------	
			
			
			\newpage
			\renewcommand{\thetable}{A5A} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Consumer Sentiment Index (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA5A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.041\textsuperscript{**} & 1.166\textsuperscript{***} & 1.053\textsuperscript{***} & \textbf{1.022\textsuperscript{ }} & 1.07\textsuperscript{***} & 1.029\textsuperscript{*} \\
							RV   & 1.162\textsuperscript{***} & 1.082\textsuperscript{***} & 1.156\textsuperscript{***} & 1.227\textsuperscript{***} & 1.422\textsuperscript{***} & 1.335\textsuperscript{***} \\
							TRV   & 1.175\textsuperscript{***} & 1.085\textsuperscript{***} & 1.165\textsuperscript{***} & 1.239\textsuperscript{***} & 1.437\textsuperscript{***} & 1.347\textsuperscript{***} \\
							BPV  & 1.179\textsuperscript{***} & 1.084\textsuperscript{***} & 1.173\textsuperscript{***} & 1.223\textsuperscript{***} & 1.413\textsuperscript{***} & 1.338\textsuperscript{***} \\
							JV  & 1.797\textsuperscript{***} & 1.727\textsuperscript{***} & 1.994\textsuperscript{***} & 2.254\textsuperscript{***} & 2.802\textsuperscript{***} & 2.606\textsuperscript{***} \\
							CMRV1   & 1.138\textsuperscript{***} & 1.094\textsuperscript{***} & 1.051\textsuperscript{***} & 1.025\textsuperscript{ } & 1.156\textsuperscript{***} & 1.04\textsuperscript{ } \\
							CMTRV1   & 1.049\textsuperscript{*} & 1.121\textsuperscript{***} & 1.118\textsuperscript{***} & 1.077\textsuperscript{***} & 1.094\textsuperscript{***} & 1.027\textsuperscript{ } \\
							CMBPV1   & 1.137\textsuperscript{***} & 1.1\textsuperscript{***} & 1.05\textsuperscript{***} & 1.025\textsuperscript{ } & 1.162\textsuperscript{***} & 1.02\textsuperscript{ } \\
							CMJV1  & 1.097\textsuperscript{***} & 1.048\textsuperscript{***} & 1.057\textsuperscript{***} & 1.03\textsuperscript{ } & 1.209\textsuperscript{***} & 0.998\textsuperscript{***} \\
							CMRV2   & 1.033\textsuperscript{ } & 1.146\textsuperscript{***} & 1.092\textsuperscript{***} & 1.06\textsuperscript{***} & 1.105\textsuperscript{***} & 1.035\textsuperscript{ } \\
							CMTRV2   & 1.059\textsuperscript{***} & 1.096\textsuperscript{***} & 1.097\textsuperscript{***} & 1.081\textsuperscript{***} & \textbf{1.012\textsuperscript{ }} & 1.07\textsuperscript{***} \\
							CMBPV2  & 1.041\textsuperscript{ } & 1.157\textsuperscript{***} & 1.119\textsuperscript{***} & 1.069\textsuperscript{***} & 1.099\textsuperscript{***} & 1.014\textsuperscript{ } \\
							CMJV2  & 1.042\textsuperscript{***} & \textbf{0.998\textsuperscript{***}} & 1.053\textsuperscript{***} & 1.037\textsuperscript{*} & 1.205\textsuperscript{***} & \textbf{0.965\textsuperscript{***}} \\
							VRV   & 1.094\textsuperscript{***} & 1.048\textsuperscript{***} & \textbf{1.028\textsuperscript{***}} & 1.044\textsuperscript{ } & 1.258\textsuperscript{***} & 1.07\textsuperscript{***} \\
							VTRV  & 1.084\textsuperscript{***} & 1.048\textsuperscript{***} & 1.028\textsuperscript{***} & 1.046\textsuperscript{ } & 1.259\textsuperscript{***} & 1.069\textsuperscript{***} \\
							VBPV   & 1.099\textsuperscript{***} & 1.039\textsuperscript{***} & 1.028\textsuperscript{***} & 1.042\textsuperscript{ } & 1.258\textsuperscript{***} & 1.071\textsuperscript{***} \\
							VJV  & 1.081\textsuperscript{***} & 1.042\textsuperscript{***} & 1.032\textsuperscript{***} & 1.063\textsuperscript{***} & 1.223\textsuperscript{***} & 1.047\textsuperscript{***} \\
							MRV  & 1.147\textsuperscript{***} & 1.21\textsuperscript{***} & 1.344\textsuperscript{***} & 1.295\textsuperscript{***} & 1.349\textsuperscript{***} & 1.172\textsuperscript{***} \\
							MTRV  & 1.134\textsuperscript{***} & 1.217\textsuperscript{***} & 1.355\textsuperscript{***} & 1.299\textsuperscript{***} & 1.361\textsuperscript{***} & 1.179\textsuperscript{***} \\
							MBPV   & 1.164\textsuperscript{***} & 1.222\textsuperscript{***} & 1.336\textsuperscript{***} & 1.295\textsuperscript{***} & 1.353\textsuperscript{***} & 1.194\textsuperscript{***} \\
							MJV   & 1.612\textsuperscript{***} & 1.592\textsuperscript{***} & 1.91\textsuperscript{***} & 1.631\textsuperscript{***} & 1.598\textsuperscript{***} & 1.398\textsuperscript{***} \\
							MVRV  & \textbf{1.006\textsuperscript{ }} & 1.173\textsuperscript{***} & 1.134\textsuperscript{***} & 1.227\textsuperscript{***} & 1.189\textsuperscript{***} & 1.135\textsuperscript{***} \\
							MVTRV   & 1.006\textsuperscript{ } & 1.171\textsuperscript{***} & 1.138\textsuperscript{***} & 1.223\textsuperscript{***} & 1.188\textsuperscript{***} & 1.134\textsuperscript{***} \\
							MVBPV  & 1.006\textsuperscript{*} & 1.174\textsuperscript{***} & 1.13\textsuperscript{***} & 1.23\textsuperscript{***} & 1.184\textsuperscript{***} & 1.139\textsuperscript{***} \\
							MVJV   & 1.056\textsuperscript{***} & 1.133\textsuperscript{***} & 1.216\textsuperscript{***} & 1.272\textsuperscript{***} & 1.105\textsuperscript{***} & 1.077\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							CMRV1   & 0.95\textsuperscript{***} & 1.017\textsuperscript{***} & 1\textsuperscript{***} & 1.02\textsuperscript{ } & 1.015\textsuperscript{*} & 1.015\textsuperscript{ } \\
							CMTRV1   & 1.016\textsuperscript{***} & 1.011\textsuperscript{ } & 0.998\textsuperscript{***} & 1.017\textsuperscript{***} & 1.002\textsuperscript{ } & \textbf{0.985\textsuperscript{***}} \\
							CMBPV1   & \textbf{0.946\textsuperscript{***}} & 1.017\textsuperscript{***} & 1\textsuperscript{***} & 1.021\textsuperscript{*} & 1.015\textsuperscript{*} & 1.016\textsuperscript{ } \\
							CMJV1  & 0.987\textsuperscript{***} & 1.005\textsuperscript{ } & 1.071\textsuperscript{***} & \textbf{1.008\textsuperscript{ }} & 1.013\textsuperscript{ } & 1.012\textsuperscript{ } \\
							CMRV2   & 1.02\textsuperscript{***} & 1.032\textsuperscript{***} & 0.995\textsuperscript{***} & 1.049\textsuperscript{***} & 0.993\textsuperscript{***} & 1.011\textsuperscript{ } \\
							CMTRV2   & 1.013\textsuperscript{***} & 1.024\textsuperscript{***} & 0.993\textsuperscript{***} & 1.041\textsuperscript{***} & \textbf{0.984\textsuperscript{***}} & 1.001\textsuperscript{*} \\
							CMBPV2  & 1.026\textsuperscript{***} & 1.025\textsuperscript{***} & \textbf{0.991\textsuperscript{***}} & 1.033\textsuperscript{***} & 1.007\textsuperscript{ } & 1.01\textsuperscript{ } \\
							CMJV2  & 1.001\textsuperscript{**} & \textbf{1.001\textsuperscript{ }} & 1.019\textsuperscript{ } & 1.038\textsuperscript{***} & 1.032\textsuperscript{***} & 1.027\textsuperscript{***} \\
							VRV   & 0.988\textsuperscript{***} & 1.011\textsuperscript{ } & 1.015\textsuperscript{ } & 1.043\textsuperscript{ } & 1.008\textsuperscript{ } & 1.03\textsuperscript{***} \\
							VTRV  & 0.986\textsuperscript{***} & 1.009\textsuperscript{ } & 1.015\textsuperscript{ } & 1.045\textsuperscript{*} & 1.011\textsuperscript{ } & 1.033\textsuperscript{***} \\
							VBPV   & 0.988\textsuperscript{***} & 1.011\textsuperscript{ } & 1.015\textsuperscript{ } & 1.041\textsuperscript{ } & 1.007\textsuperscript{ } & 1.03\textsuperscript{***} \\
							VJV  & 1.033\textsuperscript{***} & 1.017\textsuperscript{***} & 1.02\textsuperscript{ } & 1.062\textsuperscript{***} & 1.037\textsuperscript{ } & 1.025\textsuperscript{***} \\
							MRV  & 1.049\textsuperscript{***} & 1.064\textsuperscript{***} & 1.122\textsuperscript{***} & 1.093\textsuperscript{***} & 1.101\textsuperscript{***} & 1.08\textsuperscript{***} \\
							MTRV  & 1.05\textsuperscript{***} & 1.069\textsuperscript{***} & 1.129\textsuperscript{***} & 1.103\textsuperscript{***} & 1.109\textsuperscript{***} & 1.087\textsuperscript{***} \\
							MBPV   & 1.048\textsuperscript{***} & 1.063\textsuperscript{***} & 1.119\textsuperscript{***} & 1.092\textsuperscript{***} & 1.101\textsuperscript{***} & 1.082\textsuperscript{***} \\
							MJV   & 1.125\textsuperscript{***} & 1.202\textsuperscript{***} & 1.386\textsuperscript{***} & 1.296\textsuperscript{***} & 1.174\textsuperscript{***} & 1.185\textsuperscript{***} \\
							MVRV  & 1.05\textsuperscript{***} & 1.065\textsuperscript{***} & 1.095\textsuperscript{***} & 1.034\textsuperscript{ } & 1.063\textsuperscript{***} & 1.051\textsuperscript{***} \\
							MVTRV   & 1.037\textsuperscript{***} & 1.06\textsuperscript{***} & 1.097\textsuperscript{***} & 1.038\textsuperscript{*} & 1.067\textsuperscript{***} & 1.055\textsuperscript{***} \\
							MVBPV  & 1.054\textsuperscript{***} & 1.066\textsuperscript{***} & 1.094\textsuperscript{***} & 1.033\textsuperscript{ } & 1.063\textsuperscript{***} & 1.051\textsuperscript{***} \\
							MVJV   & 1.028\textsuperscript{***} & 1.037\textsuperscript{ } & 1.042\textsuperscript{ } & 1.077\textsuperscript{***} & 1.036\textsuperscript{***} & 1.044\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------				
			
			
			\newpage
			\renewcommand{\thetable}{A5B} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Relative MSFEs for Consumer Sentiment Index (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA5B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.13\textsuperscript{***} & 1.262\textsuperscript{***} & 1.104\textsuperscript{***} & 1.049\textsuperscript{ } & 1.135\textsuperscript{***} & 1.023\textsuperscript{ } \\
							RV   & 1.101\textsuperscript{ } & 1.064\textsuperscript{ } & 1.037\textsuperscript{ } & 1.071\textsuperscript{***} & 1.341\textsuperscript{***} & 1.505\textsuperscript{***} \\
							TRV   & 1.134\textsuperscript{*} & 1.064\textsuperscript{ } & 1.04\textsuperscript{ } & 1.071\textsuperscript{***} & 1.351\textsuperscript{***} & 1.521\textsuperscript{***} \\
							BPV  & 1.119\textsuperscript{ } & 1.062\textsuperscript{ } & 1.089\textsuperscript{***} & 1.067\textsuperscript{***} & 1.322\textsuperscript{***} & 1.508\textsuperscript{***} \\
							JV  & 1.93\textsuperscript{***} & 1.872\textsuperscript{***} & 1.834\textsuperscript{***} & 1.999\textsuperscript{***} & 3.079\textsuperscript{***} & 3.611\textsuperscript{***} \\
							CMRV1   & 1.3\textsuperscript{***} & 1.199\textsuperscript{***} & 1.087\textsuperscript{***} & 1.076\textsuperscript{***} & 1.048\textsuperscript{***} & 1.119\textsuperscript{ } \\
							CMTRV1   & 1.109\textsuperscript{*} & 1.018\textsuperscript{ } & 1.06\textsuperscript{***} & 1.048\textsuperscript{***} & 1.022\textsuperscript{***} & 1.065\textsuperscript{ } \\
							CMBPV1   & 1.291\textsuperscript{***} & 1.204\textsuperscript{***} & 1.083\textsuperscript{***} & 1.082\textsuperscript{***} & 1.048\textsuperscript{***} & 1.064\textsuperscript{ } \\
							CMJV1  & 1.117\textsuperscript{*} & 1.11\textsuperscript{***} & 1.07\textsuperscript{***} & 1.11\textsuperscript{***} & 1.093\textsuperscript{***} & 0.991\textsuperscript{***} \\
							CMRV2   & 1.075\textsuperscript{ } & 1.087\textsuperscript{***} & 1.039\textsuperscript{**} & 1.068\textsuperscript{***} & 1.022\textsuperscript{***} & 1.066\textsuperscript{ } \\
							CMTRV2   & 1.095\textsuperscript{**} & 1.014\textsuperscript{ } & 1.046\textsuperscript{***} & 1.042\textsuperscript{***} & \textbf{0.993\textsuperscript{***}} & 1.09\textsuperscript{ } \\
							CMBPV2  & 1.06\textsuperscript{ } & 1.096\textsuperscript{***} & 1.079\textsuperscript{***} & 1.038\textsuperscript{ } & 1.013\textsuperscript{ } & 1.01\textsuperscript{*} \\
							CMJV2  & \textbf{1.036\textsuperscript{ }} & \textbf{1.013\textsuperscript{***}} & 1.05\textsuperscript{***} & \textbf{1.028\textsuperscript{***}} & 1.159\textsuperscript{***} & \textbf{0.976\textsuperscript{***}} \\
							VRV   & 1.214\textsuperscript{***} & 1.056\textsuperscript{ } & 1.033\textsuperscript{***} & 1.059\textsuperscript{***} & 1.37\textsuperscript{***} & 1.181\textsuperscript{***} \\
							VTRV  & 1.189\textsuperscript{***} & 1.059\textsuperscript{ } & 1.03\textsuperscript{***} & 1.059\textsuperscript{***} & 1.364\textsuperscript{***} & 1.182\textsuperscript{***} \\
							VBPV   & 1.226\textsuperscript{***} & 1.036\textsuperscript{ } & 1.033\textsuperscript{***} & 1.055\textsuperscript{***} & 1.381\textsuperscript{***} & 1.181\textsuperscript{***} \\
							VJV  & 1.042\textsuperscript{ } & 1.063\textsuperscript{***} & \textbf{1.012\textsuperscript{ }} & 1.081\textsuperscript{***} & 1.136\textsuperscript{***} & 1.167\textsuperscript{***} \\
							MRV  & 1.219\textsuperscript{***} & 1.315\textsuperscript{***} & 1.46\textsuperscript{***} & 1.396\textsuperscript{***} & 1.529\textsuperscript{***} & 1.31\textsuperscript{***} \\
							MTRV  & 1.175\textsuperscript{**} & 1.319\textsuperscript{***} & 1.465\textsuperscript{***} & 1.392\textsuperscript{***} & 1.547\textsuperscript{***} & 1.326\textsuperscript{***} \\
							MBPV   & 1.255\textsuperscript{***} & 1.338\textsuperscript{***} & 1.442\textsuperscript{***} & 1.396\textsuperscript{***} & 1.533\textsuperscript{***} & 1.362\textsuperscript{***} \\
							MJV   & 1.921\textsuperscript{***} & 1.772\textsuperscript{***} & 1.765\textsuperscript{***} & 1.754\textsuperscript{***} & 1.87\textsuperscript{***} & 1.697\textsuperscript{***} \\
							MVRV  & 1.053\textsuperscript{ } & 1.314\textsuperscript{***} & 1.246\textsuperscript{***} & 1.454\textsuperscript{***} & 1.312\textsuperscript{***} & 1.281\textsuperscript{***} \\
							MVTRV   & 1.052\textsuperscript{ } & 1.309\textsuperscript{***} & 1.252\textsuperscript{***} & 1.441\textsuperscript{***} & 1.311\textsuperscript{***} & 1.277\textsuperscript{***} \\
							MVBPV  & 1.05\textsuperscript{ } & 1.316\textsuperscript{***} & 1.236\textsuperscript{***} & 1.466\textsuperscript{***} & 1.302\textsuperscript{***} & 1.29\textsuperscript{***} \\
							MVJV   & 1.201\textsuperscript{***} & 1.231\textsuperscript{***} & 1.396\textsuperscript{***} & 1.233\textsuperscript{***} & 1.277\textsuperscript{***} & 1.123\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} & 1.000\textsuperscript{} \\
							MMF  & 1.053\textsuperscript{***} & 1.074\textsuperscript{***} & 1.008\textsuperscript{ } & \textbf{0.948\textsuperscript{***}} & 1.076\textsuperscript{***} & 1.01\textsuperscript{ } \\
							RV   & 1.123\textsuperscript{***} & 1.06\textsuperscript{***} & 1.043\textsuperscript{ } & 1.08\textsuperscript{ } & 1.069\textsuperscript{ } & 1.045\textsuperscript{ } \\
							TRV   & 1.111\textsuperscript{*} & 1.061\textsuperscript{***} & 1.044\textsuperscript{ } & 1.083\textsuperscript{ } & 1.071\textsuperscript{ } & 1.046\textsuperscript{ } \\
							BPV  & 1.106\textsuperscript{*} & 1.061\textsuperscript{***} & 1.04\textsuperscript{ } & 1.076\textsuperscript{ } & 1.066\textsuperscript{ } & 1.043\textsuperscript{ } \\
							JV  & 1.537\textsuperscript{***} & 1.241\textsuperscript{***} & 1.28\textsuperscript{***} & 1.487\textsuperscript{***} & 1.384\textsuperscript{***} & 1.279\textsuperscript{***} \\
							CMRV1   & 0.859\textsuperscript{***} & 1.037\textsuperscript{***} & 1.002\textsuperscript{ } & 0.983\textsuperscript{***} & 1.034\textsuperscript{ } & 1.01\textsuperscript{ } \\
							CMTRV1   & 1.032\textsuperscript{***} & 1.015\textsuperscript{ } & 1.015\textsuperscript{ } & 1.033\textsuperscript{ } & 0.998\textsuperscript{***} & \textbf{0.943\textsuperscript{***}} \\
							CMBPV1   & \textbf{0.853\textsuperscript{***}} & 1.038\textsuperscript{***} & 1.001\textsuperscript{ } & 0.985\textsuperscript{***} & 1.034\textsuperscript{ } & 1.009\textsuperscript{ } \\
							CMJV1  & 0.948\textsuperscript{***} & 1.012\textsuperscript{***} & 1.022\textsuperscript{***} & 0.957\textsuperscript{***} & 1.042\textsuperscript{ } & 1.007\textsuperscript{ } \\
							CMRV2   & 1.052\textsuperscript{***} & 1.05\textsuperscript{***} & 0.992\textsuperscript{***} & 1.07\textsuperscript{***} & \textbf{0.987\textsuperscript{***}} & 1.011\textsuperscript{ } \\
							CMTRV2   & 1.015\textsuperscript{***} & 1.009\textsuperscript{ } & 0.998\textsuperscript{***} & 1.086\textsuperscript{***} & 0.992\textsuperscript{***} & 0.967\textsuperscript{***} \\
							CMBPV2  & 1.056\textsuperscript{***} & 1.032\textsuperscript{*} & \textbf{0.982\textsuperscript{***}} & 1.04\textsuperscript{*} & 0.998\textsuperscript{***} & 0.998\textsuperscript{***} \\
							CMJV2  & 1.008\textsuperscript{ } & \textbf{1\textsuperscript{***}} & 1.031\textsuperscript{*} & 0.981\textsuperscript{***} & 1.027\textsuperscript{ } & 1.028\textsuperscript{***} \\
							VRV   & 0.954\textsuperscript{***} & 1.019\textsuperscript{ } & 0.995\textsuperscript{***} & 1.04\textsuperscript{ } & 0.997\textsuperscript{***} & 1.011\textsuperscript{ } \\
							VTRV  & 0.948\textsuperscript{***} & 1.014\textsuperscript{ } & 0.992\textsuperscript{***} & 1.041\textsuperscript{ } & 0.996\textsuperscript{***} & 1.01\textsuperscript{ } \\
							VBPV   & 0.953\textsuperscript{***} & 1.021\textsuperscript{ } & 0.997\textsuperscript{***} & 1.036\textsuperscript{ } & 0.997\textsuperscript{***} & 1.011\textsuperscript{ } \\
							VJV  & 1.08\textsuperscript{***} & 1.027\textsuperscript{***} & 0.982\textsuperscript{***} & 1.096\textsuperscript{***} & 1.028\textsuperscript{ } & 1.023\textsuperscript{***} \\
							MRV  & 1.106\textsuperscript{***} & 1.112\textsuperscript{*} & 1.123\textsuperscript{*} & 1.044\textsuperscript{ } & 1.106\textsuperscript{***} & 1.056\textsuperscript{ } \\
							MTRV  & 1.107\textsuperscript{***} & 1.116\textsuperscript{**} & 1.126\textsuperscript{**} & 1.047\textsuperscript{ } & 1.106\textsuperscript{***} & 1.055\textsuperscript{ } \\
							MBPV   & 1.104\textsuperscript{***} & 1.112\textsuperscript{**} & 1.117\textsuperscript{*} & 1.041\textsuperscript{ } & 1.105\textsuperscript{***} & 1.056\textsuperscript{ } \\
							MJV   & 1.152\textsuperscript{***} & 1.295\textsuperscript{***} & 1.404\textsuperscript{***} & 1.28\textsuperscript{***} & 1.2\textsuperscript{***} & 1.081\textsuperscript{ } \\
							MVRV  & 1.114\textsuperscript{***} & 1.082\textsuperscript{*} & 1.089\textsuperscript{ } & 0.959\textsuperscript{***} & 1.104\textsuperscript{***} & 1.087\textsuperscript{***} \\
							MVTRV   & 1.082\textsuperscript{***} & 1.08\textsuperscript{*} & 1.092\textsuperscript{ } & 0.958\textsuperscript{***} & 1.102\textsuperscript{***} & 1.077\textsuperscript{ } \\
							MVBPV  & 1.125\textsuperscript{***} & 1.084\textsuperscript{**} & 1.082\textsuperscript{ } & 0.958\textsuperscript{***} & 1.103\textsuperscript{***} & 1.077\textsuperscript{ } \\
							MVJV   & 1.055\textsuperscript{***} & 1.034\textsuperscript{ } & 1.157\textsuperscript{***} & 0.975\textsuperscript{***} & 1.098\textsuperscript{***} & 1.023\textsuperscript{ } \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------				
			
			\newpage
			\renewcommand{\thetable}{A5C} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Consumer Sentiment Index (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableA5C}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 73.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							MMF  & 73.4\%\textsuperscript{***} & \textbf{72.2\%\textsuperscript{***}} & 74.7\%\textsuperscript{***} & \textbf{75.9\%\textsuperscript{***}} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							RV   & 68.4\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 62\%\textsuperscript{**} \\
							TRV   & 67.1\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 60.8\%\textsuperscript{**} \\
							BPV  & 67.1\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 60.8\%\textsuperscript{**} \\
							JV  & 64.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 62\%\textsuperscript{**} & 69.6\%\textsuperscript{***} & 53.2\%\textsuperscript{ } \\
							CMRV1   & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							CMTRV1   & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							CMBPV1   & 69.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & \textbf{75.9\%\textsuperscript{***}} & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							CMJV1  & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							CMRV2   & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & \textbf{73.4\%\textsuperscript{***}} & \textbf{74.7\%\textsuperscript{***}} \\
							CMTRV2   & 70.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} \\
							CMBPV2  & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} \\
							CMJV2  & \textbf{75.9\%\textsuperscript{***}} & 65.8\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							VRV   & 69.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							VTRV  & 69.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							VBPV   & 69.6\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							VJV  & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							MRV  & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MTRV  & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MBPV   & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MJV   & 67.1\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 64.6\%\textsuperscript{***} \\
							MVRV  & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							MVTRV   & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							MVBPV  & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							MVJV   & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 72.2\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							MMF  & 72.2\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & \textbf{73.4\%\textsuperscript{***}} & 72.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							RV   & 72.2\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							TRV   & 72.2\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							BPV  & 72.2\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							JV  & 69.6\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							CMRV1   & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							CMTRV1   & 74.7\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							CMBPV1   & 70.9\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							CMJV1  & 74.7\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & \textbf{70.9\%\textsuperscript{***}} \\
							CMRV2   & 74.7\%\textsuperscript{***} & 65.8\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & \textbf{73.4\%\textsuperscript{***}} & 67.1\%\textsuperscript{***} \\
							CMTRV2   & 70.9\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							CMBPV2  & 74.7\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 68.4\%\textsuperscript{***} \\
							CMJV2  & \textbf{75.9\%\textsuperscript{***}} & 64.6\%\textsuperscript{***} & 77.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 69.6\%\textsuperscript{***} \\
							VRV   & 73.4\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							VTRV  & 73.4\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & 78.5\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							VBPV   & 73.4\%\textsuperscript{***} & 63.3\%\textsuperscript{***} & \textbf{79.7\%\textsuperscript{***}} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							VJV  & 72.2\%\textsuperscript{***} & 64.6\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 70.9\%\textsuperscript{***} \\
							MRV  & 73.4\%\textsuperscript{***} & \textbf{68.4\%\textsuperscript{***}} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MTRV  & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							MBPV   & 73.4\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 75.9\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MJV   & 73.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MVRV  & 73.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MVTRV   & 73.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MVBPV  & 73.4\%\textsuperscript{***} & 67.1\%\textsuperscript{***} & 74.7\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 72.2\%\textsuperscript{***} & 65.8\%\textsuperscript{***} \\
							MVJV   & 70.9\%\textsuperscript{***} & 68.4\%\textsuperscript{***} & 73.4\%\textsuperscript{***} & 69.6\%\textsuperscript{***} & 70.9\%\textsuperscript{***} & 67.1\%\textsuperscript{***} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			\newpage
			\renewcommand{\thetable}{A5D} 
			
			\begin{table}[h]
				\centering
				\caption{Ex-Ante Directional Accuracy Rate for Consumer Sentiment Index (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableA5D}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & \textbf{72.1\%\textsuperscript{***}} \\
							MMF  & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & \textbf{79.1\%\textsuperscript{***}} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							RV   & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							TRV   & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							BPV  & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 62.8\%\textsuperscript{**} \\
							JV  & 72.1\%\textsuperscript{***} & \textbf{74.4\%\textsuperscript{***}} & 65.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 53.5\%\textsuperscript{ } \\
							CMRV1   & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							CMTRV1   & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							CMBPV1   & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							CMJV1  & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMRV2   & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & \textbf{74.4\%\textsuperscript{***}} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							CMTRV2   & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMBPV2  & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							CMJV2  & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							VRV   & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 72.1\%\textsuperscript{***} \\
							VTRV  & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} \\
							VBPV   & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							VJV  & \textbf{79.1\%\textsuperscript{***}} & 67.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							MRV  & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{**} \\
							MTRV  & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{**} \\
							MBPV   & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 65.1\%\textsuperscript{**} \\
							MJV   & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 62.8\%\textsuperscript{**} & 65.1\%\textsuperscript{***} & 65.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVRV  & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & \textbf{76.7\%\textsuperscript{***}} & 65.1\%\textsuperscript{**} \\
							MVTRV   & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVBPV  & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVJV   & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 79.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MMF  & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & \textbf{79.1\%\textsuperscript{***}} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							RV   & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							TRV   & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							BPV  & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							JV  & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							CMRV1   & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMTRV1   & \textbf{76.7\%\textsuperscript{***}} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMBPV1   & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							CMJV1  & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							CMRV2   & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & \textbf{74.4\%\textsuperscript{***}} & 65.1\%\textsuperscript{**} \\
							CMTRV2   & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							CMBPV2  & 76.7\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							CMJV2  & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							VRV   & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & \textbf{72.1\%\textsuperscript{***}} \\
							VTRV  & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & 76.7\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							VBPV   & 74.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} & \textbf{79.1\%\textsuperscript{***}} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} \\
							VJV  & 72.1\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 69.8\%\textsuperscript{***} \\
							MRV  & 74.4\%\textsuperscript{***} & \textbf{74.4\%\textsuperscript{***}} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MTRV  & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 67.4\%\textsuperscript{***} \\
							MBPV   & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MJV   & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 67.4\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVRV  & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVTRV   & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVBPV  & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 76.7\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							MVJV   & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 72.1\%\textsuperscript{***} & 74.4\%\textsuperscript{***} & 69.8\%\textsuperscript{***} & 65.1\%\textsuperscript{**} \\
							
							\bottomrule
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Tables 3A and 3B.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			
	%----------------------------------------------------------------------------------------------------------------------------------------------------------------------
			
		
			
			\renewcommand{\thetable}{B1A} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Industrial Production (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableB1A}
				\footnotesize
					\begin{adjustbox}{width=\columnwidth,height=280pt}
				\begin{threeparttable}
					
				
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 0.001\textsuperscript{ } & 0.023\textsuperscript{ } & 0.01\textsuperscript{ } & 0.0615\textsuperscript{ } & 0.262\textsuperscript{ } & 0.502\textsuperscript{*} \\
							MMF & 0.001\textsuperscript{ } & 0.062\textsuperscript{ } & 0.01\textsuperscript{ } & 0.0615\textsuperscript{ } & 0.262\textsuperscript{ } & 0.502\textsuperscript{*} \\
							RV & 0.001\textsuperscript{ } & 0.062\textsuperscript{ } & 0.01\textsuperscript{ } & 0.0615\textsuperscript{ } & 0.262\textsuperscript{ } & 0.502\textsuperscript{*} \\
							TRV & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.01\textsuperscript{ } & 0.215\textsuperscript{ } & 0.262\textsuperscript{ } & 0.502\textsuperscript{*} \\
							BPV & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.01\textsuperscript{ } & 0.215\textsuperscript{ } & 0.262\textsuperscript{ } & 0.502\textsuperscript{*} \\
							JV & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.01\textsuperscript{ } & 0.215\textsuperscript{ } & 0.262\textsuperscript{ } & 0.502\textsuperscript{*} \\
							CMRV1 & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.1435\textsuperscript{ } & 0.215\textsuperscript{ } & 0.304\textsuperscript{ } & 0.502\textsuperscript{*} \\
							CMTRV1 & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.1435\textsuperscript{ } & 0.215\textsuperscript{ } & 0.304\textsuperscript{ } & 0.502\textsuperscript{*} \\
							CMBPV1 & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.3605\textsuperscript{ } & 0.215\textsuperscript{ } & 0.566\textsuperscript{*} & 0.502\textsuperscript{*} \\
							CMJV1 & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.3605\textsuperscript{ } & 0.215\textsuperscript{ } & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							CMRV2 & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.6085\textsuperscript{*} & 0.215\textsuperscript{ } & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							CMTRV2 & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.6085\textsuperscript{*} & 0.215\textsuperscript{ } & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							CMBPV2 & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.6085\textsuperscript{*} & 0.215\textsuperscript{ } & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							CMJV2 & 0.001\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.6085\textsuperscript{*} & 0.215\textsuperscript{ } & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							VRV & 0.21\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.6085\textsuperscript{*} & 0.3355\textsuperscript{ } & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							VTRV & 0.21\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.6085\textsuperscript{*} & 0.3355\textsuperscript{ } & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							VBPV & 0.21\textsuperscript{ } & 0.0725\textsuperscript{ } & 0.6085\textsuperscript{*} & 0.3355\textsuperscript{ } & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							VJV & 0.21\textsuperscript{ } & 0.1365\textsuperscript{ } & 0.6085\textsuperscript{*} & 0.3355\textsuperscript{ } & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							MRV & 0.21\textsuperscript{ } & 0.1365\textsuperscript{ } & 0.761\textsuperscript{*} & 0.5655\textsuperscript{*} & 0.651\textsuperscript{*} & 0.502\textsuperscript{*} \\
							MTRV & 0.21\textsuperscript{ } & 0.1365\textsuperscript{ } & 0.761\textsuperscript{*} & 0.5655\textsuperscript{*} & 0.651\textsuperscript{*} & 0.5115\textsuperscript{*} \\
							MBPV & 0.21\textsuperscript{ } & 0.1365\textsuperscript{ } & 0.761\textsuperscript{*} & 0.5895\textsuperscript{*} & 0.651\textsuperscript{*} & 0.5115\textsuperscript{*} \\
							MJV & 0.3215\textsuperscript{ } & 0.1365\textsuperscript{ } & 0.761\textsuperscript{*} & 0.5895\textsuperscript{*} & 0.651\textsuperscript{*} & 0.5115\textsuperscript{*} \\
							MVRV & 0.3215\textsuperscript{ } & 0.199\textsuperscript{ } & 0.761\textsuperscript{*} & 0.5895\textsuperscript{*} & 0.7205\textsuperscript{*} & 0.514\textsuperscript{*} \\
							MVTRV & 0.3215\textsuperscript{ } & 0.4085\textsuperscript{ } & 0.761\textsuperscript{*} & 0.969\textsuperscript{*} & 0.7205\textsuperscript{*} & 0.8105\textsuperscript{*} \\
							MVBPV & 0.3215\textsuperscript{ } & 0.4085\textsuperscript{ } & 0.761\textsuperscript{*} & 0.9995\textsuperscript{*} & 0.7205\textsuperscript{*} & 0.8105\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							MMF & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							RV & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							TRV & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							BPV & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							JV & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							CMRV1 & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							CMTRV1 & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							CMBPV1 & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							CMJV1 & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							CMRV2 & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							CMTRV2 & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							CMBPV2 & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							CMJV2 & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							VRV & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							VTRV & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							VBPV & 0.0025\textsuperscript{ } & 0.009\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.006\textsuperscript{ } & 0.008\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							VJV & 0.0025\textsuperscript{ } & 0.1095\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.1385\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							MRV & 0.0265\textsuperscript{ } & 0.297\textsuperscript{ } & 0.4205\textsuperscript{ } & 0.1385\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							MTRV & 0.027\textsuperscript{ } & 0.297\textsuperscript{ } & 0.4205\textsuperscript{ } & 0.1385\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							MBPV & 0.0325\textsuperscript{ } & 0.297\textsuperscript{ } & 0.4205\textsuperscript{ } & 0.1385\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							MJV & 0.0325\textsuperscript{ } & 0.297\textsuperscript{ } & 0.673\textsuperscript{*} & 0.1385\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							MVRV & 0.0325\textsuperscript{ } & 0.528\textsuperscript{*} & 0.673\textsuperscript{*} & 0.1385\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.0065\textsuperscript{ } \\
							MVTRV & 0.0855\textsuperscript{ } & 0.528\textsuperscript{*} & 0.673\textsuperscript{*} & 0.1385\textsuperscript{ } & 0.8135\textsuperscript{*} & 0.8555\textsuperscript{*} \\
							MVBPV & 0.279\textsuperscript{ } & 0.528\textsuperscript{*} & 0.673\textsuperscript{*} & 0.347\textsuperscript{ } & 0.8135\textsuperscript{*} & 0.9695\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\bottomrule
							
						\end{tabular}%
			
				
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize Entries in the table are model confidence set test probability values. Larger p-value indicate models appearing in the model confidence set. See Section 3 of the main paper for complete details.
					\end{tablenotes}
					
				\end{threeparttable}
			
			\end{adjustbox}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{B1B} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Industrial Production (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableB1B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0115\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.03\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							CMJV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0895\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							VRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.096\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							VTRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.003\textsuperscript{ } & 0.0075\textsuperscript{ } & 0.096\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							VBPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.006\textsuperscript{ } & 0.0075\textsuperscript{ } & 0.096\textsuperscript{ } & 0.074\textsuperscript{ } \\
							VJV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.009\textsuperscript{ } & 0.0075\textsuperscript{ } & 0.096\textsuperscript{ } & 0.126\textsuperscript{ } \\
							MRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0285\textsuperscript{ } & 0.0075\textsuperscript{ } & 0.1335\textsuperscript{ } & 0.126\textsuperscript{ } \\
							MTRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0285\textsuperscript{ } & 0.0075\textsuperscript{ } & 0.2575\textsuperscript{ } & 0.126\textsuperscript{ } \\
							MBPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0285\textsuperscript{ } & 0.0075\textsuperscript{ } & 0.2575\textsuperscript{ } & 0.126\textsuperscript{ } \\
							MJV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0285\textsuperscript{ } & 0.091\textsuperscript{ } & 0.3115\textsuperscript{ } & 0.126\textsuperscript{ } \\
							MVRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0285\textsuperscript{ } & 0.091\textsuperscript{ } & 0.3115\textsuperscript{ } & 0.541\textsuperscript{*} \\
							MVTRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0285\textsuperscript{ } & 0.302\textsuperscript{ } & 0.3115\textsuperscript{ } & 0.785\textsuperscript{*} \\
							MVBPV & 0.0000\textsuperscript{ } & 0.003\textsuperscript{ } & 0.0285\textsuperscript{ } & 0.302\textsuperscript{ } & 0.8445\textsuperscript{*} & 0.785\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\		
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0075\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MMF & 0.0075\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							RV & 0.0075\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							TRV & 0.0075\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0255\textsuperscript{ } & 0.001\textsuperscript{ } \\
							BPV & 0.0075\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0255\textsuperscript{ } & 0.001\textsuperscript{ } \\
							JV & 0.0075\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0255\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMRV1 & 0.014\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0255\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMTRV1 & 0.014\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMBPV1 & 0.014\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMJV1 & 0.0245\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMRV2 & 0.0245\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMTRV2 & 0.0245\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMBPV2 & 0.094\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0295\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMJV2 & 0.094\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.085\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							VRV & 0.094\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0885\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							VTRV & 0.094\textsuperscript{ } & 0.028\textsuperscript{ } & 0.049\textsuperscript{ } & 0.0885\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							VBPV & 0.094\textsuperscript{ } & 0.076\textsuperscript{ } & 0.049\textsuperscript{ } & 0.1385\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							VJV & 0.094\textsuperscript{ } & 0.197\textsuperscript{ } & 0.049\textsuperscript{ } & 0.1385\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MRV & 0.094\textsuperscript{ } & 0.2565\textsuperscript{ } & 0.049\textsuperscript{ } & 0.499\textsuperscript{ } & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MTRV & 0.094\textsuperscript{ } & 0.302\textsuperscript{ } & 0.049\textsuperscript{ } & 0.5015\textsuperscript{*} & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MBPV & 0.094\textsuperscript{ } & 0.304\textsuperscript{ } & 0.049\textsuperscript{ } & 0.5265\textsuperscript{*} & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MJV & 0.4265\textsuperscript{ } & 0.304\textsuperscript{ } & 0.049\textsuperscript{ } & 0.5325\textsuperscript{*} & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MVRV & 0.4265\textsuperscript{ } & 0.304\textsuperscript{ } & 0.48\textsuperscript{ } & 0.6245\textsuperscript{*} & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MVTRV & 0.4265\textsuperscript{ } & 0.304\textsuperscript{ } & 0.5585\textsuperscript{*} & 0.6245\textsuperscript{*} & 0.07\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MVBPV & 0.9435\textsuperscript{*} & 0.8385\textsuperscript{*} & 0.6525\textsuperscript{*} & 0.6945\textsuperscript{*} & 0.07\textsuperscript{ } & 0.0135\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			
			\newpage
			\renewcommand{\thetable}{B2A} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Non-Farm Payroll Employment (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableB2A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 0.031\textsuperscript{ } & 0.0355\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							MMF & 0.031\textsuperscript{ } & 0.04\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							RV & 0.031\textsuperscript{ } & 0.137\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0275\textsuperscript{ } \\
							TRV & 0.031\textsuperscript{ } & 0.137\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0275\textsuperscript{ } \\
							BPV & 0.031\textsuperscript{ } & 0.137\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							JV & 0.031\textsuperscript{ } & 0.167\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							CMRV1 & 0.031\textsuperscript{ } & 0.173\textsuperscript{ } & 0.022\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							CMTRV1 & 0.031\textsuperscript{ } & 0.173\textsuperscript{ } & 0.0285\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							CMBPV1 & 0.031\textsuperscript{ } & 0.2215\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.041\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							CMJV1 & 0.031\textsuperscript{ } & 0.2215\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.041\textsuperscript{ } & 0.0345\textsuperscript{ } \\
							CMRV2 & 0.031\textsuperscript{ } & 0.2215\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.041\textsuperscript{ } & 0.037\textsuperscript{ } \\
							CMTRV2 & 0.031\textsuperscript{ } & 0.2215\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.041\textsuperscript{ } & 0.037\textsuperscript{ } \\
							CMBPV2 & 0.031\textsuperscript{ } & 0.2215\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.055\textsuperscript{ } & 0.037\textsuperscript{ } \\
							CMJV2 & 0.031\textsuperscript{ } & 0.2215\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.055\textsuperscript{ } & 0.037\textsuperscript{ } \\
							VRV & 0.031\textsuperscript{ } & 0.2215\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.055\textsuperscript{ } & 0.037\textsuperscript{ } \\
							VTRV & 0.031\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.055\textsuperscript{ } & 0.6\textsuperscript{*} \\
							VBPV & 0.031\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.5955\textsuperscript{*} & 0.6\textsuperscript{*} \\
							VJV & 0.031\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.5955\textsuperscript{*} & 0.677\textsuperscript{*} \\
							MRV & 0.137\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.5955\textsuperscript{*} & 0.677\textsuperscript{*} \\
							MTRV & 0.137\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.8565\textsuperscript{*} & 0.677\textsuperscript{*} \\
							MBPV & 0.137\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.8565\textsuperscript{*} & 0.677\textsuperscript{*} \\
							MJV & 0.137\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.8565\textsuperscript{*} & 0.677\textsuperscript{*} \\
							MVRV & 0.4535\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2755\textsuperscript{ } & 0.8565\textsuperscript{*} & 0.677\textsuperscript{*} \\
							MVTRV & 0.4535\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2755\textsuperscript{ } & 0.8565\textsuperscript{*} & 0.677\textsuperscript{*} \\
							MVBPV & 0.4535\textsuperscript{ } & 0.2475\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.2755\textsuperscript{ } & 0.8565\textsuperscript{*} & 0.677\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.019\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMJV2 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							VRV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.021\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							VTRV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.021\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							VBPV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.021\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							VJV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.021\textsuperscript{ } & 0.0565\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							MRV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.021\textsuperscript{ } & 0.0595\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							MTRV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.022\textsuperscript{ } & 0.0595\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							MBPV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.022\textsuperscript{ } & 0.0595\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							MJV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.022\textsuperscript{ } & 0.0595\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							MVRV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.022\textsuperscript{ } & 0.0595\textsuperscript{ } & 0.0175\textsuperscript{ } \\
							MVTRV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.022\textsuperscript{ } & 0.0595\textsuperscript{ } & 0.0235\textsuperscript{ } \\
							MVBPV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.022\textsuperscript{ } & 0.0595\textsuperscript{ } & 0.0235\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			
			\newpage
			\renewcommand{\thetable}{B2B} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Non-Farm Payroll Employment (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableB2B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.002\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.017\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.002\textsuperscript{ } & 0.034\textsuperscript{ } & 0.0025\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0885\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.034\textsuperscript{ } & 0.0185\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.014\textsuperscript{ } & 0.0885\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.0185\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.014\textsuperscript{ } & 0.0885\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.0185\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.014\textsuperscript{ } & 0.192\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.022\textsuperscript{ } \\
							CMBPV2 & 0.0025\textsuperscript{ } & 0.014\textsuperscript{ } & 0.192\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.0275\textsuperscript{ } \\
							CMJV2 & 0.0025\textsuperscript{ } & 0.014\textsuperscript{ } & 0.196\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.107\textsuperscript{ } \\
							VRV & 0.0025\textsuperscript{ } & 0.014\textsuperscript{ } & 0.196\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.107\textsuperscript{ } \\
							VTRV & 0.0025\textsuperscript{ } & 0.014\textsuperscript{ } & 0.196\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.107\textsuperscript{ } \\
							VBPV & 0.003\textsuperscript{ } & 0.156\textsuperscript{ } & 0.2235\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.107\textsuperscript{ } \\
							VJV & 0.003\textsuperscript{ } & 0.156\textsuperscript{ } & 0.2235\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.107\textsuperscript{ } \\
							MRV & 0.4705\textsuperscript{ } & 0.156\textsuperscript{ } & 0.2235\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.107\textsuperscript{ } \\
							MTRV & 0.4705\textsuperscript{ } & 0.447\textsuperscript{ } & 0.2235\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.107\textsuperscript{ } \\
							MBPV & 0.4705\textsuperscript{ } & 0.447\textsuperscript{ } & 0.2595\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.107\textsuperscript{ } \\
							MJV & 0.4705\textsuperscript{ } & 0.447\textsuperscript{ } & 0.2595\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.318\textsuperscript{ } \\
							MVRV & 0.4705\textsuperscript{ } & 0.447\textsuperscript{ } & 0.2595\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.19\textsuperscript{ } & 0.3975\textsuperscript{ } \\
							MVTRV & 0.536\textsuperscript{*} & 0.447\textsuperscript{ } & 0.2595\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.4075\textsuperscript{ } & 0.474\textsuperscript{ } \\
							MVBPV & 0.876\textsuperscript{*} & 0.447\textsuperscript{ } & 0.2595\textsuperscript{ } & 0.105\textsuperscript{ } & 0.4235\textsuperscript{ } & 0.474\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.01\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0585\textsuperscript{ } & 0.212\textsuperscript{ } & 0.08\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.139\textsuperscript{ } & 0.212\textsuperscript{ } & 0.08\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.139\textsuperscript{ } & 0.212\textsuperscript{ } & 0.08\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.1655\textsuperscript{ } & 0.212\textsuperscript{ } & 0.08\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMJV2 & 0.0000\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.212\textsuperscript{ } & 0.08\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							VRV & 0.0000\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.212\textsuperscript{ } & 0.08\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							VTRV & 0.0000\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.212\textsuperscript{ } & 0.08\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							VBPV & 0.004\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.212\textsuperscript{ } & 0.08\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							VJV & 0.008\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.212\textsuperscript{ } & 0.08\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MRV & 0.008\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.212\textsuperscript{ } & 0.2495\textsuperscript{ } & 0.156\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MTRV & 0.008\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.212\textsuperscript{ } & 0.2495\textsuperscript{ } & 0.432\textsuperscript{ } & 0.025\textsuperscript{ } \\
							MBPV & 0.008\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.212\textsuperscript{ } & 0.2495\textsuperscript{ } & 0.432\textsuperscript{ } & 0.5195\textsuperscript{*} \\
							MJV & 0.008\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.3265\textsuperscript{ } & 0.2495\textsuperscript{ } & 0.432\textsuperscript{ } & 0.5195\textsuperscript{*} \\
							MVRV & 0.008\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.3265\textsuperscript{ } & 0.2495\textsuperscript{ } & 0.432\textsuperscript{ } & 0.5445\textsuperscript{*} \\
							MVTRV & 0.008\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.3265\textsuperscript{ } & 0.2495\textsuperscript{ } & 0.432\textsuperscript{ } & 0.5445\textsuperscript{*} \\
							MVBPV & 0.2485\textsuperscript{ } & 0.4285\textsuperscript{ } & 0.3265\textsuperscript{ } & 0.2495\textsuperscript{ } & 0.47\textsuperscript{ } & 0.5445\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{B3A} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Personal Consumption Expenditure (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableB3A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.0255\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.0255\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0815\textsuperscript{ } \\
							CMJV2 & 0.001\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							VRV & 0.001\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							VTRV & 0.004\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							VBPV & 0.004\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							VJV & 0.004\textsuperscript{ } & 0.161\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							MRV & 0.3725\textsuperscript{ } & 0.161\textsuperscript{ } & 0.03\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							MTRV & 0.4755\textsuperscript{ } & 0.161\textsuperscript{ } & 0.036\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							MBPV & 0.4755\textsuperscript{ } & 0.161\textsuperscript{ } & 0.036\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							MJV & 0.4755\textsuperscript{ } & 0.161\textsuperscript{ } & 0.036\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.1325\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							MVRV & 0.4755\textsuperscript{ } & 0.161\textsuperscript{ } & 0.2715\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.1325\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							MVTRV & 0.4755\textsuperscript{ } & 0.161\textsuperscript{ } & 0.2715\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.1325\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							MVBPV & 0.4755\textsuperscript{ } & 0.161\textsuperscript{ } & 0.4025\textsuperscript{ } & 0.2905\textsuperscript{ } & 0.1325\textsuperscript{ } & 0.1495\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.0175\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.001\textsuperscript{ } & 0.002\textsuperscript{ } \\
							CMJV2 & 0.015\textsuperscript{ } & 0.0175\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.001\textsuperscript{ } & 0.002\textsuperscript{ } \\
							VRV & 0.015\textsuperscript{ } & 0.0175\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.001\textsuperscript{ } & 0.008\textsuperscript{ } \\
							VTRV & 0.015\textsuperscript{ } & 0.0175\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.026\textsuperscript{ } & 0.008\textsuperscript{ } \\
							VBPV & 0.015\textsuperscript{ } & 0.0315\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.026\textsuperscript{ } & 0.0105\textsuperscript{ } \\
							VJV & 0.015\textsuperscript{ } & 0.0315\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.0385\textsuperscript{ } & 0.0105\textsuperscript{ } \\
							MRV & 0.015\textsuperscript{ } & 0.0315\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.067\textsuperscript{ } & 0.0105\textsuperscript{ } \\
							MTRV & 0.015\textsuperscript{ } & 0.059\textsuperscript{ } & 0.012\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.067\textsuperscript{ } & 0.0105\textsuperscript{ } \\
							MBPV & 0.015\textsuperscript{ } & 0.51\textsuperscript{*} & 0.012\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.067\textsuperscript{ } & 0.0105\textsuperscript{ } \\
							MJV & 0.015\textsuperscript{ } & 0.51\textsuperscript{*} & 0.1775\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.067\textsuperscript{ } & 0.0105\textsuperscript{ } \\
							MVRV & 0.15\textsuperscript{ } & 0.51\textsuperscript{*} & 0.1775\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.067\textsuperscript{ } & 0.0235\textsuperscript{ } \\
							MVTRV & 0.15\textsuperscript{ } & 0.6195\textsuperscript{*} & 0.1775\textsuperscript{ } & 0.0425\textsuperscript{ } & 0.067\textsuperscript{ } & 0.033\textsuperscript{ } \\
							MVBPV & 0.15\textsuperscript{ } & 0.6195\textsuperscript{*} & 0.9535\textsuperscript{*} & 0.0425\textsuperscript{ } & 0.067\textsuperscript{ } & 0.033\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{B3B} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Personal Consumption Expenditure (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableB3B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.0075\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMJV2 & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							VRV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							VTRV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.003\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							VBPV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.232\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							VJV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.232\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MRV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.232\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.177\textsuperscript{ } \\
							MTRV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.232\textsuperscript{ } & 0.049\textsuperscript{ } & 0.001\textsuperscript{ } & 0.293\textsuperscript{ } \\
							MBPV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.728\textsuperscript{*} & 0.049\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.293\textsuperscript{ } \\
							MJV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.728\textsuperscript{*} & 0.049\textsuperscript{ } & 0.0145\textsuperscript{ } & 0.5395\textsuperscript{*} \\
							MVRV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.728\textsuperscript{*} & 0.049\textsuperscript{ } & 0.1505\textsuperscript{ } & 0.5395\textsuperscript{*} \\
							MVTRV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.728\textsuperscript{*} & 0.049\textsuperscript{ } & 0.498\textsuperscript{ } & 0.5395\textsuperscript{*} \\
							MVBPV & 0.0000\textsuperscript{ } & 0.0265\textsuperscript{ } & 0.728\textsuperscript{*} & 0.049\textsuperscript{ } & 0.943\textsuperscript{*} & 0.5395\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMRV2 & 0.002\textsuperscript{ } & 0.003\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMTRV2 & 0.002\textsuperscript{ } & 0.02\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.1\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMBPV2 & 0.0185\textsuperscript{ } & 0.02\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.1\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							CMJV2 & 0.029\textsuperscript{ } & 0.094\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.122\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							VRV & 0.029\textsuperscript{ } & 0.094\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.2325\textsuperscript{ } & 0.309\textsuperscript{ } \\
							VTRV & 0.029\textsuperscript{ } & 0.094\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.2325\textsuperscript{ } & 0.309\textsuperscript{ } \\
							VBPV & 0.029\textsuperscript{ } & 0.094\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.159\textsuperscript{ } & 0.2325\textsuperscript{ } & 0.309\textsuperscript{ } \\
							VJV & 0.168\textsuperscript{ } & 0.094\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.159\textsuperscript{ } & 0.2325\textsuperscript{ } & 0.309\textsuperscript{ } \\
							MRV & 0.168\textsuperscript{ } & 0.111\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.159\textsuperscript{ } & 0.2325\textsuperscript{ } & 0.309\textsuperscript{ } \\
							MTRV & 0.168\textsuperscript{ } & 0.111\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.159\textsuperscript{ } & 0.2325\textsuperscript{ } & 0.309\textsuperscript{ } \\
							MBPV & 0.168\textsuperscript{ } & 0.111\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.159\textsuperscript{ } & 0.2325\textsuperscript{ } & 0.309\textsuperscript{ } \\
							MJV & 0.2725\textsuperscript{ } & 0.111\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.159\textsuperscript{ } & 0.2325\textsuperscript{ } & 0.309\textsuperscript{ } \\
							MVRV & 0.6045\textsuperscript{*} & 0.111\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.159\textsuperscript{ } & 0.2425\textsuperscript{ } & 0.309\textsuperscript{ } \\
							MVTRV & 0.6045\textsuperscript{*} & 0.774\textsuperscript{*} & 0.046\textsuperscript{ } & 0.159\textsuperscript{ } & 0.2425\textsuperscript{ } & 0.5365\textsuperscript{*} \\
							MVBPV & 0.6045\textsuperscript{*} & 0.93\textsuperscript{*} & 0.183\textsuperscript{ } & 0.159\textsuperscript{ } & 0.323\textsuperscript{ } & 0.5365\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{B4A} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Consumer Sentiment Index (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableB4A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.003\textsuperscript{ } \\
							MMF & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.003\textsuperscript{ } \\
							RV & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.003\textsuperscript{ } \\
							TRV & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.168\textsuperscript{ } \\
							BPV & 0.0005\textsuperscript{ } & 0.0335\textsuperscript{ } & 0.001\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.168\textsuperscript{ } \\
							JV & 0.0005\textsuperscript{ } & 0.0335\textsuperscript{ } & 0.001\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.168\textsuperscript{ } \\
							CMRV1 & 0.0015\textsuperscript{ } & 0.0335\textsuperscript{ } & 0.001\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.168\textsuperscript{ } \\
							CMTRV1 & 0.0015\textsuperscript{ } & 0.0335\textsuperscript{ } & 0.001\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.5015\textsuperscript{*} \\
							CMBPV1 & 0.0045\textsuperscript{ } & 0.4355\textsuperscript{ } & 0.001\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.583\textsuperscript{*} \\
							CMJV1 & 0.0045\textsuperscript{ } & 0.4355\textsuperscript{ } & 0.001\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							CMRV2 & 0.232\textsuperscript{ } & 0.4355\textsuperscript{ } & 0.001\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							CMTRV2 & 0.285\textsuperscript{ } & 0.4355\textsuperscript{ } & 0.001\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							CMBPV2 & 0.285\textsuperscript{ } & 0.4355\textsuperscript{ } & 0.003\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							CMJV2 & 0.285\textsuperscript{ } & 0.4355\textsuperscript{ } & 0.003\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							VRV & 0.285\textsuperscript{ } & 0.4355\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							VTRV & 0.285\textsuperscript{ } & 0.4355\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.095\textsuperscript{ } & 0.0685\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							VBPV & 0.806\textsuperscript{*} & 0.4355\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.095\textsuperscript{ } & 0.2975\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							VJV & 0.806\textsuperscript{*} & 0.4355\textsuperscript{ } & 0.0075\textsuperscript{ } & 0.095\textsuperscript{ } & 0.2975\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							MRV & 0.806\textsuperscript{*} & 0.4355\textsuperscript{ } & 0.0075\textsuperscript{ } & 0.095\textsuperscript{ } & 0.2975\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							MTRV & 0.806\textsuperscript{*} & 0.4355\textsuperscript{ } & 0.107\textsuperscript{ } & 0.095\textsuperscript{ } & 0.2975\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							MBPV & 0.806\textsuperscript{*} & 0.4355\textsuperscript{ } & 0.107\textsuperscript{ } & 0.0955\textsuperscript{ } & 0.2975\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							MJV & 0.806\textsuperscript{*} & 0.4355\textsuperscript{ } & 0.107\textsuperscript{ } & 0.0955\textsuperscript{ } & 0.2975\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							MVRV & 0.806\textsuperscript{*} & 0.4355\textsuperscript{ } & 0.107\textsuperscript{ } & 0.1185\textsuperscript{ } & 0.2975\textsuperscript{ } & 0.6565\textsuperscript{*} \\
							MVTRV & 0.806\textsuperscript{*} & 0.4355\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.144\textsuperscript{ } & 0.364\textsuperscript{ } & 0.914\textsuperscript{*} \\
							MVBPV & 0.806\textsuperscript{*} & 0.8015\textsuperscript{*} & 0.8785\textsuperscript{*} & 0.397\textsuperscript{ } & 0.946\textsuperscript{*} & 0.914\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							CMJV2 & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							VRV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							VTRV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } \\
							VBPV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.005\textsuperscript{ } \\
							VJV & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.029\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0605\textsuperscript{ } & 0.005\textsuperscript{ } \\
							MRV & 0.0005\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0825\textsuperscript{ } & 0.02\textsuperscript{ } & 0.2405\textsuperscript{ } & 0.005\textsuperscript{ } \\
							MTRV & 0.0805\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0825\textsuperscript{ } & 0.02\textsuperscript{ } & 0.2405\textsuperscript{ } & 0.132\textsuperscript{ } \\
							MBPV & 0.0805\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0825\textsuperscript{ } & 0.0395\textsuperscript{ } & 0.2405\textsuperscript{ } & 0.132\textsuperscript{ } \\
							MJV & 0.0805\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.675\textsuperscript{*} & 0.0705\textsuperscript{ } & 0.2405\textsuperscript{ } & 0.132\textsuperscript{ } \\
							MVRV & 0.0805\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.879\textsuperscript{*} & 0.1235\textsuperscript{ } & 0.2405\textsuperscript{ } & 0.132\textsuperscript{ } \\
							MVTRV & 0.0805\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.879\textsuperscript{*} & 0.1235\textsuperscript{ } & 0.2405\textsuperscript{ } & 0.354\textsuperscript{ } \\
							MVBPV & 0.568\textsuperscript{*} & 0.0005\textsuperscript{ } & 0.879\textsuperscript{*} & 0.335\textsuperscript{ } & 0.571\textsuperscript{*} & 0.354\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{B4B} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Consumer Sentiment Index (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableB4B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0315\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.034\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0345\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.046\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0505\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.057\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0665\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0175\textsuperscript{ } & 0.0665\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0175\textsuperscript{ } & 0.0665\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0445\textsuperscript{ } & 0.0765\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.045\textsuperscript{ } & 0.0765\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMTRV2 & 0.029\textsuperscript{ } & 0.045\textsuperscript{ } & 0.0765\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMBPV2 & 0.029\textsuperscript{ } & 0.045\textsuperscript{ } & 0.0765\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							CMJV2 & 0.3775\textsuperscript{ } & 0.045\textsuperscript{ } & 0.0765\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							VRV & 0.3775\textsuperscript{ } & 0.045\textsuperscript{ } & 0.0765\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							VTRV & 0.3775\textsuperscript{ } & 0.045\textsuperscript{ } & 0.0765\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							VBPV & 0.3775\textsuperscript{ } & 0.045\textsuperscript{ } & 0.0765\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							VJV & 0.7405\textsuperscript{*} & 0.045\textsuperscript{ } & 0.3255\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							MRV & 0.7405\textsuperscript{*} & 0.045\textsuperscript{ } & 0.3255\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							MTRV & 0.7405\textsuperscript{*} & 0.045\textsuperscript{ } & 0.3255\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							MBPV & 0.7405\textsuperscript{*} & 0.0455\textsuperscript{ } & 0.3255\textsuperscript{ } & 0.001\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							MJV & 0.9415\textsuperscript{*} & 0.0455\textsuperscript{ } & 0.3255\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							MVRV & 0.9415\textsuperscript{*} & 0.0455\textsuperscript{ } & 0.3255\textsuperscript{ } & 0.008\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } \\
							MVTRV & 0.9415\textsuperscript{*} & 0.689\textsuperscript{*} & 0.3255\textsuperscript{ } & 0.008\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0075\textsuperscript{ } \\
							MVBPV & 0.9415\textsuperscript{*} & 0.788\textsuperscript{*} & 0.3255\textsuperscript{ } & 0.653\textsuperscript{*} & 0.002\textsuperscript{ } & 0.061\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							BPV & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							JV & 0.001\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.003\textsuperscript{ } \\
							CMRV1 & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							CMTRV1 & 0.003\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.0105\textsuperscript{ } \\
							CMBPV1 & 0.0045\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.165\textsuperscript{ } \\
							CMJV1 & 0.0045\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.387\textsuperscript{ } \\
							CMRV2 & 0.0075\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0155\textsuperscript{ } & 0.407\textsuperscript{ } \\
							CMTRV2 & 0.01\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.016\textsuperscript{ } & 0.407\textsuperscript{ } \\
							CMBPV2 & 0.0105\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.026\textsuperscript{ } & 0.407\textsuperscript{ } \\
							CMJV2 & 0.0115\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.032\textsuperscript{ } & 0.407\textsuperscript{ } \\
							VRV & 0.0115\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.032\textsuperscript{ } & 0.407\textsuperscript{ } \\
							VTRV & 0.0135\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.016\textsuperscript{ } & 0.5575\textsuperscript{*} & 0.407\textsuperscript{ } \\
							VBPV & 0.0135\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0485\textsuperscript{ } & 0.5575\textsuperscript{*} & 0.407\textsuperscript{ } \\
							VJV & 0.0135\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0485\textsuperscript{ } & 0.5575\textsuperscript{*} & 0.407\textsuperscript{ } \\
							MRV & 0.0135\textsuperscript{ } & 0.0115\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0485\textsuperscript{ } & 0.5575\textsuperscript{*} & 0.407\textsuperscript{ } \\
							MTRV & 0.024\textsuperscript{ } & 0.0115\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0485\textsuperscript{ } & 0.5575\textsuperscript{*} & 0.407\textsuperscript{ } \\
							MBPV & 0.024\textsuperscript{ } & 0.0115\textsuperscript{ } & 0.4095\textsuperscript{ } & 0.0485\textsuperscript{ } & 0.5575\textsuperscript{*} & 0.7855\textsuperscript{*} \\
							MJV & 0.024\textsuperscript{ } & 0.0115\textsuperscript{ } & 0.522\textsuperscript{*} & 0.4785\textsuperscript{ } & 0.5575\textsuperscript{*} & 0.7855\textsuperscript{*} \\
							MVRV & 0.024\textsuperscript{ } & 0.0115\textsuperscript{ } & 0.522\textsuperscript{*} & 0.4785\textsuperscript{ } & 0.5575\textsuperscript{*} & 0.9255\textsuperscript{*} \\
							MVTRV & 0.024\textsuperscript{ } & 0.0115\textsuperscript{ } & 0.522\textsuperscript{*} & 0.4785\textsuperscript{ } & 0.5575\textsuperscript{*} & 0.9255\textsuperscript{*} \\
							MVBPV & 0.3715\textsuperscript{ } & 0.0115\textsuperscript{ } & 0.619\textsuperscript{*} & 0.4785\textsuperscript{ } & 0.64\textsuperscript{*} & 0.9255\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{B5A} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Consumer Price Index (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableB5A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
												
								AR  & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								MMF & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								RV & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								TRV & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								BPV & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								JV & 0.0000\textsuperscript{ } & 0.0235\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								CMRV1 & 0.0000\textsuperscript{ } & 0.0235\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0185\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								CMTRV1 & 0.0000\textsuperscript{ } & 0.1625\textsuperscript{ } & 0.055\textsuperscript{ } & 0.03\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								CMBPV1 & 0.0000\textsuperscript{ } & 0.276\textsuperscript{ } & 0.055\textsuperscript{ } & 0.03\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								CMJV1 & 0.0735\textsuperscript{ } & 0.276\textsuperscript{ } & 0.055\textsuperscript{ } & 0.03\textsuperscript{ } & 0.1465\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								CMRV2 & 0.0735\textsuperscript{ } & 0.276\textsuperscript{ } & 0.127\textsuperscript{ } & 0.03\textsuperscript{ } & 0.494\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								CMTRV2 & 0.0735\textsuperscript{ } & 0.276\textsuperscript{ } & 0.13\textsuperscript{ } & 0.03\textsuperscript{ } & 0.494\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								CMBPV2 & 0.0735\textsuperscript{ } & 0.276\textsuperscript{ } & 0.13\textsuperscript{ } & 0.03\textsuperscript{ } & 0.494\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								CMJV2 & 0.2895\textsuperscript{ } & 0.276\textsuperscript{ } & 0.13\textsuperscript{ } & 0.03\textsuperscript{ } & 0.494\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								VRV & 0.2895\textsuperscript{ } & 0.322\textsuperscript{ } & 0.296\textsuperscript{ } & 0.03\textsuperscript{ } & 0.494\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								VTRV & 0.373\textsuperscript{ } & 0.322\textsuperscript{ } & 0.296\textsuperscript{ } & 0.03\textsuperscript{ } & 0.4955\textsuperscript{ } & 0.2515\textsuperscript{ } \\
								VBPV & 0.373\textsuperscript{ } & 0.322\textsuperscript{ } & 0.507\textsuperscript{*} & 0.03\textsuperscript{ } & 0.532\textsuperscript{*} & 0.2515\textsuperscript{ } \\
								VJV & 0.373\textsuperscript{ } & 0.322\textsuperscript{ } & 0.6185\textsuperscript{*} & 0.03\textsuperscript{ } & 0.7075\textsuperscript{*} & 0.2515\textsuperscript{ } \\
								MRV & 0.471\textsuperscript{ } & 0.322\textsuperscript{ } & 0.6695\textsuperscript{*} & 0.03\textsuperscript{ } & 0.7075\textsuperscript{*} & 0.2515\textsuperscript{ } \\
								MTRV & 0.471\textsuperscript{ } & 0.592\textsuperscript{*} & 0.6695\textsuperscript{*} & 0.03\textsuperscript{ } & 0.726\textsuperscript{*} & 0.2515\textsuperscript{ } \\
								MBPV & 0.471\textsuperscript{ } & 0.592\textsuperscript{*} & 0.6695\textsuperscript{*} & 0.03\textsuperscript{ } & 0.726\textsuperscript{*} & 0.2515\textsuperscript{ } \\
								MJV & 0.471\textsuperscript{ } & 0.8255\textsuperscript{*} & 0.6695\textsuperscript{*} & 0.03\textsuperscript{ } & 0.726\textsuperscript{*} & 0.2515\textsuperscript{ } \\
								MVRV & 0.471\textsuperscript{ } & 0.8255\textsuperscript{*} & 0.827\textsuperscript{*} & 0.9125\textsuperscript{*} & 0.726\textsuperscript{*} & 0.2515\textsuperscript{ } \\
								MVTRV & 0.471\textsuperscript{ } & 0.8255\textsuperscript{*} & 0.827\textsuperscript{*} & 0.9125\textsuperscript{*} & 0.726\textsuperscript{*} & 0.2515\textsuperscript{ } \\
								MVBPV & 0.471\textsuperscript{ } & 0.8255\textsuperscript{*} & 0.827\textsuperscript{*} & 0.9125\textsuperscript{*} & 0.726\textsuperscript{*} & 0.873\textsuperscript{*} \\
								MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
				
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule

								AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								MMF & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								RV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								TRV & 0.0000\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								BPV & 0.0000\textsuperscript{ } & 0.009\textsuperscript{ } & 0.0095\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								JV & 0.0000\textsuperscript{ } & 0.045\textsuperscript{ } & 0.0095\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMRV1 & 0.0000\textsuperscript{ } & 0.045\textsuperscript{ } & 0.012\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMTRV1 & 0.0000\textsuperscript{ } & 0.045\textsuperscript{ } & 0.012\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMBPV1 & 0.0000\textsuperscript{ } & 0.045\textsuperscript{ } & 0.012\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMJV1 & 0.0000\textsuperscript{ } & 0.096\textsuperscript{ } & 0.012\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMRV2 & 0.0000\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.012\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMTRV2 & 0.0000\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.007\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMBPV2 & 0.0005\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.007\textsuperscript{ } & 0.006\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMJV2 & 0.002\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.0175\textsuperscript{ } & 0.006\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								VRV & 0.002\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.0185\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								VTRV & 0.002\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.0185\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								VBPV & 0.002\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.034\textsuperscript{ } & 0.304\textsuperscript{ } & 0.2085\textsuperscript{ } \\
								VJV & 0.002\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.034\textsuperscript{ } & 0.304\textsuperscript{ } & 0.2135\textsuperscript{ } \\
								MRV & 0.005\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.034\textsuperscript{ } & 0.3055\textsuperscript{ } & 0.2135\textsuperscript{ } \\
								MTRV & 0.0065\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0205\textsuperscript{ } & 0.0485\textsuperscript{ } & 0.3395\textsuperscript{ } & 0.2135\textsuperscript{ } \\
								MBPV & 0.0595\textsuperscript{ } & 0.2025\textsuperscript{ } & 0.0205\textsuperscript{ } & 0.247\textsuperscript{ } & 0.3415\textsuperscript{ } & 0.3325\textsuperscript{ } \\
								MJV & 0.0915\textsuperscript{ } & 0.52\textsuperscript{*} & 0.0225\textsuperscript{ } & 0.247\textsuperscript{ } & 0.654\textsuperscript{*} & 0.357\textsuperscript{ } \\
								MVRV & 0.0915\textsuperscript{ } & 0.52\textsuperscript{*} & 0.0225\textsuperscript{ } & 0.247\textsuperscript{ } & 0.6725\textsuperscript{*} & 0.3725\textsuperscript{ } \\
								MVTRV & 0.0915\textsuperscript{ } & 0.52\textsuperscript{*} & 0.3545\textsuperscript{ } & 0.2835\textsuperscript{ } & 0.6725\textsuperscript{*} & 0.654\textsuperscript{*} \\
								MVBPV & 0.1455\textsuperscript{ } & 0.9845\textsuperscript{*} & 0.8145\textsuperscript{*} & 0.7835\textsuperscript{*} & 0.6725\textsuperscript{*} & 0.654\textsuperscript{*} \\
								MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
			
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{B5B} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Consumer Price Index (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableB5B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
								AR  & 0.008\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								MMF & 0.008\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								RV & 0.008\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								TRV & 0.008\textsuperscript{ } & 0.0125\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								BPV & 0.008\textsuperscript{ } & 0.0635\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								JV & 0.01\textsuperscript{ } & 0.0635\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMRV1 & 0.01\textsuperscript{ } & 0.269\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMTRV1 & 0.043\textsuperscript{ } & 0.269\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMBPV1 & 0.043\textsuperscript{ } & 0.269\textsuperscript{ } & 0.0055\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								CMJV1 & 0.611\textsuperscript{*} & 0.269\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0065\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								CMRV2 & 0.611\textsuperscript{*} & 0.33\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.007\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								CMTRV2 & 0.611\textsuperscript{*} & 0.33\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.001\textsuperscript{ } & 0.007\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								CMBPV2 & 0.611\textsuperscript{*} & 0.33\textsuperscript{ } & 0.0165\textsuperscript{ } & 0.001\textsuperscript{ } & 0.007\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								CMJV2 & 0.611\textsuperscript{*} & 0.5895\textsuperscript{*} & 0.0165\textsuperscript{ } & 0.001\textsuperscript{ } & 0.007\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								VRV & 0.611\textsuperscript{*} & 0.5895\textsuperscript{*} & 0.0165\textsuperscript{ } & 0.01\textsuperscript{ } & 0.007\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								VTRV & 0.611\textsuperscript{*} & 0.5895\textsuperscript{*} & 0.0435\textsuperscript{ } & 0.01\textsuperscript{ } & 0.07\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								VBPV & 0.611\textsuperscript{*} & 0.607\textsuperscript{*} & 0.614\textsuperscript{*} & 0.01\textsuperscript{ } & 0.1585\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								VJV & 0.611\textsuperscript{*} & 0.7545\textsuperscript{*} & 0.614\textsuperscript{*} & 0.01\textsuperscript{ } & 0.1585\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								MRV & 0.611\textsuperscript{*} & 0.7545\textsuperscript{*} & 0.614\textsuperscript{*} & 0.01\textsuperscript{ } & 0.203\textsuperscript{ } & 0.0015\textsuperscript{ } \\
								MTRV & 0.611\textsuperscript{*} & 0.8915\textsuperscript{*} & 0.614\textsuperscript{*} & 0.111\textsuperscript{ } & 0.29\textsuperscript{ } & 0.2615\textsuperscript{ } \\
								MBPV & 0.611\textsuperscript{*} & 0.8915\textsuperscript{*} & 0.614\textsuperscript{*} & 0.111\textsuperscript{ } & 0.29\textsuperscript{ } & 0.2615\textsuperscript{ } \\
								MJV & 0.611\textsuperscript{*} & 0.906\textsuperscript{*} & 0.614\textsuperscript{*} & 0.4125\textsuperscript{ } & 0.569\textsuperscript{*} & 0.2615\textsuperscript{ } \\
								MVRV & 0.885\textsuperscript{*} & 0.906\textsuperscript{*} & 0.614\textsuperscript{*} & 0.4125\textsuperscript{ } & 0.569\textsuperscript{*} & 0.2615\textsuperscript{ } \\
								MVTRV & 0.885\textsuperscript{*} & 0.9615\textsuperscript{*} & 0.614\textsuperscript{*} & 0.687\textsuperscript{*} & 0.569\textsuperscript{*} & 0.2615\textsuperscript{ } \\
								MVBPV & 0.885\textsuperscript{*} & 0.9615\textsuperscript{*} & 0.7615\textsuperscript{*} & 0.687\textsuperscript{*} & 0.569\textsuperscript{*} & 0.8445\textsuperscript{*} \\
								MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\

														
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							

								AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								TRV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.002\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								BPV & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								JV & 0.0000\textsuperscript{ } & 0.003\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0000\textsuperscript{ } \\
								CMRV1 & 0.0000\textsuperscript{ } & 0.0045\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0005\textsuperscript{ } \\
								CMTRV1 & 0.0000\textsuperscript{ } & 0.046\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0005\textsuperscript{ } \\
								CMBPV1 & 0.0000\textsuperscript{ } & 0.046\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0005\textsuperscript{ } \\
								CMJV1 & 0.001\textsuperscript{ } & 0.046\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.011\textsuperscript{ } & 0.01\textsuperscript{ } \\
								CMRV2 & 0.061\textsuperscript{ } & 0.046\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.011\textsuperscript{ } & 0.01\textsuperscript{ } \\
								CMTRV2 & 0.061\textsuperscript{ } & 0.046\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0245\textsuperscript{ } & 0.01\textsuperscript{ } \\
								CMBPV2 & 0.061\textsuperscript{ } & 0.046\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0815\textsuperscript{ } & 0.024\textsuperscript{ } \\
								CMJV2 & 0.061\textsuperscript{ } & 0.046\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.2165\textsuperscript{ } & 0.0815\textsuperscript{ } & 0.024\textsuperscript{ } \\
								VRV & 0.061\textsuperscript{ } & 0.046\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.315\textsuperscript{ } & 0.0815\textsuperscript{ } & 0.16\textsuperscript{ } \\
								VTRV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.315\textsuperscript{ } & 0.0815\textsuperscript{ } & 0.16\textsuperscript{ } \\
								VBPV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.315\textsuperscript{ } & 0.33\textsuperscript{ } & 0.16\textsuperscript{ } \\
								VJV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.315\textsuperscript{ } & 0.33\textsuperscript{ } & 0.16\textsuperscript{ } \\
								MRV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.315\textsuperscript{ } & 0.33\textsuperscript{ } & 0.16\textsuperscript{ } \\
								MTRV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.8605\textsuperscript{*} & 0.6605\textsuperscript{*} & 0.9005\textsuperscript{*} \\
								MBPV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.8605\textsuperscript{*} & 0.709\textsuperscript{*} & 0.9005\textsuperscript{*} \\
								MJV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.8605\textsuperscript{*} & 0.709\textsuperscript{*} & 0.904\textsuperscript{*} \\
								MVRV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.9555\textsuperscript{*} & 0.8605\textsuperscript{*} & 0.803\textsuperscript{*} & 0.914\textsuperscript{*} \\
								MVTRV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.9555\textsuperscript{*} & 0.8605\textsuperscript{*} & 0.803\textsuperscript{*} & 0.914\textsuperscript{*} \\
								MVBPV & 0.061\textsuperscript{ } & 0.2785\textsuperscript{ } & 0.9555\textsuperscript{*} & 0.8605\textsuperscript{*} & 0.9155\textsuperscript{*} & 0.914\textsuperscript{*} \\
								MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
												
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			
				\newpage
			\renewcommand{\thetable}{B6A} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Housing Starts (Sample 1: 2006:1 - 2018:12)$^1$} 
				\label{table:tableB5A}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 0.0015\textsuperscript{ } & 0.007\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							MMF & 0.0015\textsuperscript{ } & 0.007\textsuperscript{ } & 0.013\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							RV & 0.0055\textsuperscript{ } & 0.0085\textsuperscript{ } & 0.1895\textsuperscript{ } & 0.0135\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							TRV & 0.0055\textsuperscript{ } & 0.015\textsuperscript{ } & 0.2065\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							BPV & 0.0055\textsuperscript{ } & 0.015\textsuperscript{ } & 0.2065\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							JV & 0.0055\textsuperscript{ } & 0.015\textsuperscript{ } & 0.2065\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							CMRV1 & 0.0165\textsuperscript{ } & 0.0375\textsuperscript{ } & 0.2065\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							CMTRV1 & 0.0165\textsuperscript{ } & 0.0655\textsuperscript{ } & 0.2065\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							CMBPV1 & 0.0165\textsuperscript{ } & 0.0655\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							CMJV1 & 0.02\textsuperscript{ } & 0.0655\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							CMRV2 & 0.0215\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							CMTRV2 & 0.026\textsuperscript{ } & 0.1235\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							CMBPV2 & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							CMJV2 & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							VRV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.0925\textsuperscript{ } \\
							VTRV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.0645\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							VBPV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.2655\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							VJV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.2655\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							MRV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.2655\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							MTRV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.2655\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							MBPV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.2655\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							MJV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.305\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.2655\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							MVRV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.386\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.4985\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							MVTRV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.386\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.4985\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							MVBPV & 0.072\textsuperscript{ } & 0.1695\textsuperscript{ } & 0.386\textsuperscript{ } & 0.3065\textsuperscript{ } & 0.4985\textsuperscript{ } & 0.2935\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							CMJV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							VRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0055\textsuperscript{ } \\
							VTRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0095\textsuperscript{ } \\
							VBPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.002\textsuperscript{ } & 0.0115\textsuperscript{ } \\
							VJV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0115\textsuperscript{ } \\
							MRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0525\textsuperscript{ } \\
							MTRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.009\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.01\textsuperscript{ } & 0.0525\textsuperscript{ } \\
							MBPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.009\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.01\textsuperscript{ } & 0.0525\textsuperscript{ } \\
							MJV & 0.0000\textsuperscript{ } & 0.0095\textsuperscript{ } & 0.009\textsuperscript{ } & 0.0035\textsuperscript{ } & 0.01\textsuperscript{ } & 0.0525\textsuperscript{ } \\
							MVRV & 0.002\textsuperscript{ } & 0.0105\textsuperscript{ } & 0.009\textsuperscript{ } & 0.0895\textsuperscript{ } & 0.01\textsuperscript{ } & 0.0525\textsuperscript{ } \\
							MVTRV & 0.002\textsuperscript{ } & 0.0105\textsuperscript{ } & 0.073\textsuperscript{ } & 0.0895\textsuperscript{ } & 0.0405\textsuperscript{ } & 0.0525\textsuperscript{ } \\
							MVBPV & 0.002\textsuperscript{ } & 0.0105\textsuperscript{ } & 0.073\textsuperscript{ } & 0.0895\textsuperscript{ } & 0.0405\textsuperscript{ } & 0.0525\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
			\newpage
			\renewcommand{\thetable}{B6B} 
			
			\begin{table}[h]
				\centering
				\caption{Model Confidence Set Results for Housing Starts (Sample 2: 2009:1 - 2018:12)$^1$} 
				\label{table:tableB5B}
				\begin{threeparttable}
					\begin{adjustbox}{width=\columnwidth,height=280pt}
						% Table generated by Excel2LaTeX from sheet '06'
						\begin{tabular}{lllllll}
							\toprule
							\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{6}{c}{Forecast horizon}\\
							&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
							\midrule
							\multicolumn{7}{c}{rolling window size = 36}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0005\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0035\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0035\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.011\textsuperscript{ } & 0.004\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0165\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0165\textsuperscript{ } \\
							CMJV2 & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.001\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0165\textsuperscript{ } \\
							VRV & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.001\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0165\textsuperscript{ } \\
							VTRV & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.001\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0165\textsuperscript{ } \\
							VBPV & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.001\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0165\textsuperscript{ } \\
							VJV & 0.0000\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.021\textsuperscript{ } & 0.011\textsuperscript{ } & 0.0165\textsuperscript{ } \\
							MRV & 0.036\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.021\textsuperscript{ } & 0.011\textsuperscript{ } & 0.2465\textsuperscript{ } \\
							MTRV & 0.036\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.021\textsuperscript{ } & 0.011\textsuperscript{ } & 0.2465\textsuperscript{ } \\
							MBPV & 0.036\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0015\textsuperscript{ } & 0.021\textsuperscript{ } & 0.011\textsuperscript{ } & 0.2465\textsuperscript{ } \\
							MJV & 0.036\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0105\textsuperscript{ } & 0.021\textsuperscript{ } & 0.011\textsuperscript{ } & 0.2465\textsuperscript{ } \\
							MVRV & 0.036\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0105\textsuperscript{ } & 0.13\textsuperscript{ } & 0.011\textsuperscript{ } & 0.2465\textsuperscript{ } \\
							MVTRV & 0.036\textsuperscript{ } & 0.001\textsuperscript{ } & 0.0105\textsuperscript{ } & 0.254\textsuperscript{ } & 0.376\textsuperscript{ } & 0.2465\textsuperscript{ } \\
							MVBPV & 0.036\textsuperscript{ } & 0.0025\textsuperscript{ } & 0.0105\textsuperscript{ } & 0.254\textsuperscript{ } & 0.376\textsuperscript{ } & 0.2595\textsuperscript{ } \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\midrule
							\multicolumn{7}{c}{rolling window size = 72}\\
							\midrule
							
							AR  & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							MMF & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							RV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							TRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							BPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							JV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							CMRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							CMTRV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							CMBPV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0005\textsuperscript{ } \\
							CMJV1 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.022\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMTRV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.022\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMBPV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.022\textsuperscript{ } & 0.001\textsuperscript{ } \\
							CMJV2 & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.022\textsuperscript{ } & 0.001\textsuperscript{ } \\
							VRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.005\textsuperscript{ } & 0.0285\textsuperscript{ } & 0.001\textsuperscript{ } \\
							VTRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0375\textsuperscript{ } & 0.005\textsuperscript{ } & 0.2685\textsuperscript{ } & 0.001\textsuperscript{ } \\
							VBPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0375\textsuperscript{ } & 0.005\textsuperscript{ } & 0.31\textsuperscript{ } & 0.001\textsuperscript{ } \\
							VJV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0375\textsuperscript{ } & 0.005\textsuperscript{ } & 0.467\textsuperscript{ } & 0.001\textsuperscript{ } \\
							MRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.0375\textsuperscript{ } & 0.005\textsuperscript{ } & 0.634\textsuperscript{*} & 0.001\textsuperscript{ } \\
							MTRV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.098\textsuperscript{ } & 0.005\textsuperscript{ } & 0.634\textsuperscript{*} & 0.01\textsuperscript{ } \\
							MBPV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.098\textsuperscript{ } & 0.005\textsuperscript{ } & 0.634\textsuperscript{*} & 0.499\textsuperscript{ } \\
							MJV & 0.0000\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.098\textsuperscript{ } & 0.005\textsuperscript{ } & 0.634\textsuperscript{*} & 0.6695\textsuperscript{*} \\
							MVRV & 0.0565\textsuperscript{ } & 0.0000\textsuperscript{ } & 0.098\textsuperscript{ } & 0.005\textsuperscript{ } & 0.634\textsuperscript{*} & 0.6695\textsuperscript{*} \\
							MVTRV & 0.0565\textsuperscript{ } & 0.229\textsuperscript{ } & 0.957\textsuperscript{*} & 0.005\textsuperscript{ } & 0.634\textsuperscript{*} & 0.6695\textsuperscript{*} \\
							MVBPV & 0.0565\textsuperscript{ } & 0.229\textsuperscript{ } & 0.957\textsuperscript{*} & 0.005\textsuperscript{ } & 0.902\textsuperscript{*} & 0.9475\textsuperscript{*} \\
							MVJV & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} & 1\textsuperscript{*} \\
							
							\bottomrule
							
						\end{tabular}%
					\end{adjustbox}
					\begin{tablenotes}[flushleft]
						\small
						\item[1] \footnotesize See notes to Table B1A.
					\end{tablenotes}
					
				\end{threeparttable}
			\end{table}
			
			%----------------------------------------------------------------------
			%----------------------------------------------------------------------
			
\newpage




\newpage
\newgeometry{top=2cm, bottom=2cm}
\renewcommand{\thetable}{RR1} 	
\begin{table}[h]
	\centering
	\caption{Ex-Ante Relative MSFEs of DLM vs Corresponding Linear Model for Housing Starts$^1$} 
	\label{table:tableRR1}
	\begin{threeparttable}
		\scriptsize
		\begin{tabular}{lllllll}
			\toprule
			\multicolumn{1}{c}{\multirow{2}[0]{*}{Forecasting Model}} & \multicolumn{6}{c}{Forecast horizon}\\
			&   1-month &  2-month &3-month &4-month &5-month &  6-month \\
			\midrule
			\multicolumn{7}{c}{rolling window size = 36}\\
			\midrule
			MAC   & 1.53  & 1.38  & 1.17  & 0.93  & 0.89  & 0.78 \\
			RV    & 1.26  & 2.86  & 4.45  & 4.76  & 5.14  & 4.24 \\
			BPV   & 1.04  & 2.40  & 3.85  & 4.34  & 4.76  & 4.05 \\
			TRV   & 1.19  & 2.73  & 4.23  & 4.53  & 4.92  & 4.07 \\
			JV    & 1.84  & 1.69  & 1.61  & 1.49  & 1.71  & 1.70 \\
			CMRV1 & 1.70  & 2.02  & 2.16  & 1.73  & 1.62  & 1.26 \\
			CMBPV1 & 3.77  & 3.16  & 2.73  & 1.97  & 1.65  & 1.43 \\
			CMTRV1 & 1.67  & 1.97  & 2.09  & 1.66  & 1.55  & 1.18 \\
			CMJV1 & 1.38  & 1.39  & 1.36  & 1.06  & 0.97  & 0.79 \\
			CMRV2 & 4.57  & 3.84  & 3.29  & 2.32  & 1.90  & 1.63 \\
			CMBPV2 & 3.94  & 3.29  & 2.87  & 1.98  & 1.65  & 1.55 \\
			CMTRV2 & 3.34  & 2.70  & 2.30  & 1.66  & 1.50  & 1.41 \\
			CMJV2 & 1.34  & 2.31  & 3.65  & 3.50  & 3.18  & 2.51 \\
			\bottomrule
			
		\end{tabular}%
		\begin{tablenotes}[flushleft]
			\scriptsize
			\item[1] This table reports mean square forecast errors (MSFEs) fro predictions made using a dynamic linear model (DLM) relative to those made using our linear model. The factor augmented forecasting models are given in the first column are defined in Table 2 of the main paper. The sample period used in the forecasting experiment is 2006:1-2018:12. The DLM is estimated using a rolling window size of 72 months.
		\end{tablenotes}
		
	\end{threeparttable}
\end{table}		

%--------------------------------------------------------------------------------------
\newpage
\newgeometry{top=2cm, bottom=2cm}
\renewcommand{\thetable}{RR2A} 

\begin{table}[h]
\centering
\caption{Ex-Ante Relative MSFEs for Housing Starts (Sample 1: 2006:1 - 2018:12)$^1$} 
\label{table:tableRR2A}
\begin{threeparttable}
\scriptsize

\begin{tabular}{lllllllll}
		\toprule
\multicolumn{1}{c}{\multirow{2}[0]{*}{Corresponding Model}} & \multicolumn{8}{c}{Forecast horizon}\\
	&   1-month &  2-month &3-month &4-month &5-month &  6-month & 12-month &  24-month\\
			\midrule
\multicolumn{7}{c}{rolling window size = 36}\\
\midrule
	AR & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 \\
	MMF & 1.173\textsuperscript{***} & 1.092\textsuperscript{***} & 1.104\textsuperscript{***} & 1.027 & 0.981\textsuperscript{***} & 0.938\textsuperscript{***} & 1.010 & 1.199 \\
	RV & 0.930\textsuperscript{***} & 0.897\textsuperscript{***} & 0.999\textsuperscript{***} & 1.006 & 1.037 & 1.038\textsuperscript{***} & 1.068 & 0.996 \\
	TRV & 0.930\textsuperscript{***} & 0.902\textsuperscript{***} & 1.015 & 1.013 & 1.043 & 1.040\textsuperscript{***} & 1.066 & 1.010 \\
	BPV & 0.931\textsuperscript{***} & 0.897\textsuperscript{***} & 1.012 & 1.002\textsuperscript{**} & 1.036 & 1.035\textsuperscript{***} & 1.070 & 1.001 \\
	JV & 2.277\textsuperscript{***} & 2.178\textsuperscript{***} & 2.010\textsuperscript{***} & 1.726\textsuperscript{***} & 1.747\textsuperscript{***} & 1.602\textsuperscript{***} & 1.861 & 4.349 \\
	CMRV1 & 0.999\textsuperscript{***} & 1.096\textsuperscript{***} & 1.161\textsuperscript{***} & 1.028\textsuperscript{***} & 1.004\textsuperscript{*} & 0.968\textsuperscript{***} & 1.118 & 1.061 \\
	CMTRV1 & 1.019 & 1.003\textsuperscript{*} & 0.998\textsuperscript{***} & 1.004\textsuperscript{*} & 1.058\textsuperscript{***} & 1.047 & 1.020 & 1.088 \\
	CMBPV1 & 0.997\textsuperscript{***} & 1.096\textsuperscript{**} & 1.158\textsuperscript{***} & 1.033\textsuperscript{***} & 1.032\textsuperscript{***} & 0.967\textsuperscript{***} & 1.129 & 1.065 \\
	CMJV1 & 1.011 & 1.133\textsuperscript{***} & 1.078\textsuperscript{***} & 1.022 & 0.979\textsuperscript{***} & 0.952\textsuperscript{***} & 1.073 & 1.096 \\
	CMRV2 & 0.992\textsuperscript{***} & 0.974\textsuperscript{***} & 1.011 & 0.982\textsuperscript{***} & 1.079\textsuperscript{***} & 1.031 & 0.997 & 1.111 \\
	CMTRV2 & 0.991\textsuperscript{***} & 0.989\textsuperscript{***} & 1.055\textsuperscript{***} & 1.004\textsuperscript{*} & 1.062\textsuperscript{***} & 1.044 & 0.997 & 1.081 \\
	CMBPV2 & 1.007 & 1.020 & 1.016 & 0.992\textsuperscript{***} & 1.076\textsuperscript{***} & 1.059 & 1.011 & 1.106 \\
	CMJV2 & 1.014 & 0.991\textsuperscript{***} & 1.048\textsuperscript{***} & 1.031\textsuperscript{***} & 0.962\textsuperscript{***} & 0.963\textsuperscript{***} & 0.995 & 1.083 \\
	VRV & 1.040\textsuperscript{***} & 1.022 & 1.052 & 1.041\textsuperscript{***} & 1.037\textsuperscript{***} & 0.983\textsuperscript{***} & 1.142 & 1.054 \\
	VTRV & 1.037\textsuperscript{***} & 1.021 & 1.053 & 1.041\textsuperscript{***} & 1.038\textsuperscript{***} & 0.985\textsuperscript{***} & 1.145 & 1.052 \\
	VBPV & 1.043\textsuperscript{***} & 1.023 & 1.058 & 1.049\textsuperscript{***} & 1.043\textsuperscript{***} & 0.982\textsuperscript{***} & 1.179 & 1.056 \\
	VJV & 1.044\textsuperscript{*} & 0.952\textsuperscript{***} & 0.999\textsuperscript{***} & 0.998\textsuperscript{***} & 0.962\textsuperscript{***} & 0.964\textsuperscript{***} & 1.057 & 1.087 \\
	MRV & 1.152\textsuperscript{***} & 1.090\textsuperscript{***} & 1.165\textsuperscript{***} & 1.321\textsuperscript{***} & 1.194\textsuperscript{***} & 1.208\textsuperscript{***} & 1.206 & 1.216 \\
	MTRV & 1.151\textsuperscript{***} & 1.091\textsuperscript{***} & 1.181\textsuperscript{***} & 1.336\textsuperscript{***} & 1.199\textsuperscript{***} & 1.218\textsuperscript{***} & 1.200 & 1.259 \\
	MBPV & 1.146\textsuperscript{***} & 1.075\textsuperscript{***} & 1.160\textsuperscript{***} & 1.326\textsuperscript{***} & 1.194\textsuperscript{***} & 1.193\textsuperscript{***} & 1.203 & 1.206 \\
	MJV & 1.253\textsuperscript{***} & 1.254\textsuperscript{***} & 1.096 & 1.174\textsuperscript{***} & 1.252\textsuperscript{***} & 1.286\textsuperscript{***} & 1.139 & 1.431 \\
	MVRV & 1.272\textsuperscript{***} & 1.197\textsuperscript{***} & 1.116\textsuperscript{***} & 1.129\textsuperscript{***} & 1.005\textsuperscript{*} & 1.037 & 1.169 & 1.353 \\
	MVTRV & 1.272\textsuperscript{***} & 1.200\textsuperscript{***} & 1.115\textsuperscript{***} & 1.132\textsuperscript{***} & 1.016 & 1.040 & 1.169 & 1.350 \\
	MVBPV & 1.272\textsuperscript{***} & 1.196\textsuperscript{***} & 1.119\textsuperscript{***} & 1.129\textsuperscript{***} & 1.011 & 1.032 & 1.166 & 1.327 \\
	MVJV & 1.253\textsuperscript{***} & 1.156\textsuperscript{***} & 1.103\textsuperscript{***} & 1.016 & 1.029 & 1.085 & 1.141 & 1.209 \\	
	
	\midrule
	\multicolumn{9}{c}{rolling window size = 72}\\
	\midrule
	AR    & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 \\
	MMF   & 0.925 & 0.851 & 0.841 & 0.700 & 0.623 & 0.591 & 0.585 & 0.535 \\
	RV    & 0.849 & 0.780 & 0.711 & 0.569 & 0.484 & 0.479 & 0.459 & 0.540 \\
	TRV   & 0.852 & 0.798 & 0.724 & 0.561 & 0.477 & 0.463 & 0.434 & 0.487 \\
	BPV   & 0.855 & 0.779 & 0.710 & 0.567 & 0.482 & 0.477 & 0.457 & 0.540 \\
	JV    & 1.081 & 1.061 & 1.034 & 0.796 & 0.630 & 0.559 & 0.387 & 0.573 \\
	CMRV1 & 0.920 & 0.882 & 0.841 & 0.760 & 0.709 & 0.741 & 0.944 & 0.963 \\
	CMTRV1 & 0.889 & 0.883 & 0.884 & 0.832 & 0.872 & 0.881 & 0.821 & 0.958 \\
	CMBPV1 & 0.916 & 0.877 & 0.833 & 0.754 & 0.704 & 0.749 & 0.937 & 0.970 \\
	CMJV1 & 0.906 & 0.892 & 0.880 & 0.812 & 0.756 & 0.792 & 0.950 & 0.985 \\
	CMRV2 & 0.910 & 0.922 & 0.919 & 0.853 & 0.875 & 0.857 & 0.723 & 0.941 \\
	CMTRV2 & 0.873 & 0.868 & 0.856 & 0.834 & 0.875 & 0.812 & 0.784 & 0.882 \\
	CMBPV2 & 0.866 & 0.877 & 0.899 & 0.866 & 0.872 & 0.832 & 0.753 & 0.973 \\
	CMJV2 & 0.922 & 0.915 & 0.911 & 0.805 & 0.721 & 0.770 & 0.799 & 0.924 \\
	VRV   & 0.922 & 0.836 & 0.766 & 0.753 & 0.642 & 0.664 & 0.767 & 0.861 \\
	VTRV  & 0.917 & 0.837 & 0.764 & 0.753 & 0.629 & 0.660 & 0.752 & 0.842 \\
	VBPV  & 0.923 & 0.837 & 0.764 & 0.754 & 0.637 & 0.667 & 0.793 & 0.865 \\
	VJV   & 0.938 & 0.863 & 0.883 & 0.794 & 0.698 & 0.723 & 0.811 & 0.888 \\
	MRV   & 0.886 & 0.806 & 0.785 & 0.660 & 0.607 & 0.615 & 0.714 & 0.541 \\
	MTRV  & 0.887 & 0.813 & 0.789 & 0.668 & 0.607 & 0.616 & 0.729 & 0.539 \\
	MBPV  & 0.884 & 0.804 & 0.782 & 0.655 & 0.605 & 0.610 & 0.712 & 0.541 \\
	MJV   & 1.011 & 0.894 & 0.801 & 0.712 & 0.631 & 0.658 & 1.118 & 0.647 \\
	MVRV  & 0.930 & 0.823 & 0.838 & 0.706 & 0.627 & 0.639 & 0.636 & 0.550 \\
	MVTRV & 0.928 & 0.825 & 0.842 & 0.706 & 0.627 & 0.633 & 0.638 & 0.549 \\
	MVBPV & 0.930 & 0.820 & 0.834 & 0.699 & 0.626 & 0.640 & 0.636 & 0.550 \\
	MVJV  & 0.920 & 0.880 & 0.839 & 0.727 & 0.629 & 0.632 & 0.650 & 0.544 \\
	
	\bottomrule
\end{tabular}%
%\end{adjustbox}
%}}
%\npnoround
\begin{tablenotes}[flushleft]
\scriptsize
\item[1] This table displays mean square forecast errors (MSFEs) of the listed models, relative to the AR benchmark model. The first column indicates the forecasting model. The sample period used in the forecasting experiment is 2006:1-2018:12.
\end{tablenotes}

\end{threeparttable}
\end{table}

%---------------------------------------------------------------

\newpage
\newgeometry{top=2cm, bottom=2cm}
\renewcommand{\thetable}{RR2B} 
\begin{table}[h]
\centering
\caption{Ex-Ante Relative MSFEs for Housing Starts (Sample 2: 2009:1 - 2018:12)$^1$} 
\label{table:tableRR2B}
\begin{threeparttable}
\scriptsize

\begin{tabular}{lllllllll}
\toprule
\multicolumn{1}{c}{\multirow{2}[0]{*}{Model}} & \multicolumn{8}{c}{Forecast horizon}\\
&   1-month &  2-month &3-month &4-month &5-month &  6-month &12-month &  24-month\\
\midrule
\multicolumn{9}{c}{rolling window size = 36}\\
\midrule	

AR    & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 \\
MMF   & 1.231 & 1.114 & 1.166 & 0.970 & 0.967 & 0.969 & 1.477 & 1.196 \\
RV    & 0.954 & 0.842 & 0.944 & 0.924 & 1.193 & 1.064 & 1.167 & 0.960 \\
TRV   & 0.950 & 0.846 & 0.981 & 0.938 & 1.205 & 1.061 & 1.171 & 0.951 \\
BPV   & 0.958 & 0.847 & 0.952 & 0.910 & 1.187 & 1.050 & 1.172 & 0.978 \\
JV    & 2.977 & 3.567 & 3.028 & 1.923 & 2.313 & 2.173 & 2.228 & 2.308 \\
CMRV1 & 1.121 & 1.191 & 1.304 & 1.056 & 1.147 & 0.924 & 1.077 & 1.074 \\
CMTRV1 & 1.030 & 0.993 & 0.927 & 1.074 & 1.050 & 0.990 & 1.180 & 1.045 \\
CMBPV1 & 1.122 & 1.181 & 1.296 & 1.074 & 1.149 & 0.920 & 1.072 & 1.073 \\
CMJV1 & 1.121 & 1.267 & 1.148 & 0.988 & 1.083 & 0.936 & 1.148 & 1.043 \\
CMRV2 & 0.958 & 0.995 & 0.944 & 1.023 & 1.114 & 0.986 & 1.213 & 1.035 \\
CMTRV2 & 0.994 & 0.984 & 1.081 & 1.052 & 1.061 & 1.009 & 1.145 & 1.047 \\
CMBPV2 & 1.003 & 0.987 & 0.970 & 1.030 & 1.098 & 0.988 & 1.275 & 1.027 \\
CMJV2 & 1.058 & 0.969 & 1.189 & 1.008 & 0.997 & 0.940 & 1.074 & 0.966 \\
VRV   & 1.117 & 1.145 & 1.262 & 1.023 & 1.047 & 1.007 & 1.187 & 1.108 \\
VTRV  & 1.107 & 1.136 & 1.259 & 1.021 & 1.045 & 1.008 & 1.241 & 1.105 \\
VBPV  & 1.125 & 1.153 & 1.279 & 1.032 & 1.061 & 1.012 & 1.180 & 1.111 \\
VJV   & 1.137 & 0.818 & 0.989 & 1.058 & 0.966 & 0.972 & 1.100 & 1.042 \\
MRV   & 1.231 & 1.123 & 1.259 & 1.479 & 1.474 & 1.637 & 1.771 & 1.786 \\
MTRV  & 1.232 & 1.121 & 1.316 & 1.512 & 1.476 & 1.652 & 1.764 & 1.972 \\
MBPV  & 1.231 & 1.099 & 1.243 & 1.489 & 1.473 & 1.588 & 1.766 & 1.748 \\
MJV   & 1.127 & 0.993 & 1.048 & 1.024 & 1.212 & 1.513 & 1.605 & 2.970 \\
MVRV  & 1.383 & 1.393 & 1.226 & 1.219 & 1.105 & 1.155 & 1.743 & 1.631 \\
MVTRV & 1.379 & 1.399 & 1.224 & 1.224 & 1.107 & 1.156 & 1.762 & 1.606 \\
MVBPV & 1.389 & 1.400 & 1.225 & 1.217 & 1.102 & 1.148 & 1.736 & 1.630 \\
MVJV  & 1.235 & 1.245 & 1.296 & 1.028 & 1.095 & 1.345 & 1.688 & 1.200 \\

\midrule
\multicolumn{9}{c}{rolling window size = 72}\\
\midrule

AR    & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 & 1.000 \\
MMF   & 1.064 & 1.043 & 1.030 & 1.020 & 1.050 & 0.949 & 1.918 & 1.128 \\
RV    & 0.989 & 0.963 & 0.998 & 1.001 & 0.994 & 0.971 & 1.060 & 1.131 \\
TRV   & 0.985 & 0.970 & 1.001 & 0.974 & 0.997 & 0.972 & 1.057 & 1.147 \\
BPV   & 1.014 & 0.958 & 0.994 & 0.996 & 0.992 & 0.971 & 1.056 & 1.123 \\
JV    & 1.420 & 1.447 & 1.356 & 1.239 & 1.192 & 1.117 & 2.078 & 1.229 \\
CMRV1 & 1.037 & 0.950 & 0.978 & 0.965 & 0.958 & 0.980 & 1.057 & 1.140 \\
CMTRV1 & 1.033 & 0.927 & 1.022 & 0.951 & 0.975 & 1.033 & 0.987 & 1.085 \\
CMBPV1 & 1.043 & 0.952 & 0.980 & 0.963 & 0.956 & 0.962 & 1.058 & 1.142 \\
CMJV1 & 0.938 & 0.958 & 1.009 & 1.049 & 0.991 & 1.079 & 0.977 & 1.208 \\
CMRV2 & 0.989 & 0.994 & 1.028 & 0.999 & 1.004 & 1.048 & 1.022 & 1.094 \\
CMTRV2 & 0.971 & 0.974 & 1.036 & 0.979 & 1.004 & 0.979 & 0.972 & 0.818 \\
CMBPV2 & 0.988 & 0.947 & 1.038 & 0.963 & 0.984 & 1.028 & 1.017 & 1.438 \\
CMJV2 & 0.955 & 0.943 & 1.024 & 1.036 & 0.983 & 1.083 & 1.026 & 1.207 \\
VRV   & 0.999 & 1.008 & 0.956 & 1.017 & 0.949 & 0.984 & 1.132 & 1.251 \\
VTRV  & 0.997 & 1.002 & 0.958 & 1.021 & 0.952 & 1.001 & 1.123 & 1.265 \\
VBPV  & 1.002 & 1.014 & 0.955 & 1.016 & 0.947 & 0.993 & 1.133 & 1.247 \\
VJV   & 1.019 & 0.961 & 1.026 & 0.998 & 1.006 & 1.032 & 1.040 & 1.210 \\
MRV   & 1.106 & 1.027 & 1.049 & 1.053 & 1.087 & 0.982 & 2.300 & 1.114 \\
MTRV  & 1.105 & 1.032 & 1.053 & 1.056 & 1.091 & 0.987 & 2.306 & 1.120 \\
MBPV  & 1.106 & 1.022 & 1.046 & 1.049 & 1.085 & 0.981 & 2.300 & 1.125 \\
MJV   & 1.267 & 1.332 & 1.188 & 1.222 & 1.141 & 1.144 & 2.791 & 1.035 \\
MVRV  & 1.147 & 0.991 & 1.040 & 0.984 & 1.060 & 0.986 & 2.223 & 1.230 \\
MVTRV & 1.141 & 0.990 & 1.042 & 0.985 & 1.058 & 1.009 & 2.214 & 1.225 \\
MVBPV & 1.153 & 0.993 & 1.040 & 0.984 & 1.057 & 0.988 & 2.223 & 1.236 \\
MVJV  & 1.008 & 1.087 & 0.976 & 1.026 & 1.008 & 0.983 & 2.141 & 1.124 \\

\bottomrule 
\end{tabular}%
%\end{adjustbox}
%}}
\begin{tablenotes}[flushleft]
\scriptsize
\item[1] The sample period used in the forecasting experiment is 2006:1 to 2018:12.
\end{tablenotes}

\end{threeparttable}
\end{table}

%---------------------------------------------------------------

\newpage
\newgeometry{top=2cm, bottom=2cm}
\renewcommand{\thetable}{RR3A} 

\begin{table}[h]
\centering
\caption{MSFE-Best Models (Sample 1: 2006:1 - 2018:12)} 
\label{table:tableRR3A}
\begin{threeparttable}
\scriptsize
%\footnotesize
\begin{tabular}{lllllllll}
\toprule
\multicolumn{1}{c}{\multirow{2}[0]{*}{Targets}} & \multicolumn{8}{c}{Forecast horizon}\\
&   1-month &  2-month &3-month &4-month &5-month &  6-month &12-month &  24-month \\
\midrule
\multicolumn{9}{c}{rolling window size = 36}\\
\midrule

\multicolumn{1}{l}{$HS$} & RV    & RV    & CMTRV1 & CMRV2 & CMJV2 & MAC   & \multicolumn{1}{l}{CMJV2} & \multicolumn{1}{l}{MAC} \\
& 0.930*** & 0.897*** & 0.998*** & 0.982*** & 0.962*** & 0.938*** & \multicolumn{1}{l}{0.995} & \multicolumn{1}{l}{1.199} \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$IP$} & CMTRV1 & MVJV  & MVRV  & MAC   & CMJV2 & TRV   & \multicolumn{1}{l}{MAC} & \multicolumn{1}{l}{VRV} \\
& 0.987*** & 0.939*** & 0.952*** & 1.010  & 0.973*** & 0.997*** & 0.879 & \multicolumn{1}{l}{0.983} \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$PAY$} & CMRV2 & VBPV  & MAC   & CMTRV1 & MAC   & VJV   & \multicolumn{1}{l}{VTRV} & \multicolumn{1}{l}{RV} \\
& 0.912*** & 1.024 & 0.978*** & 0.926*** & 0.956*** & 1.010 & \multicolumn{1}{l}{1.017} & \multicolumn{1}{l}{0.934} \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$CPI$} & VJV   & VJV   & CMJV2 & CMJV2 & CMRV2 & VBPV  & \multicolumn{1}{l}{VRV} & \multicolumn{1}{l}{CMBPV} \\
& 1.025*** & 0.998*** & 0.995*** & 0.972*** & 0.904*** & 1.024 & \multicolumn{1}{l}{1.010} & \multicolumn{1}{l}{0.975} \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$PCE$} & CMRV2 & CMBPV1 & VJV   & CMJV2 & VJV   & CMJV2 & \multicolumn{1}{l}{MAC} & \multicolumn{1}{l}{MVTRV} \\
& 1.008 & 1.000*** & 1.020  & 0.986*** & 0.943*** & 0.973*** & 1.015 & 0.919 \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$SI$} & MVRV  & CMJV2 & VRV   & MAC   & CMTRV2 & CMJV2 & \multicolumn{1}{l}{CMJV2} & \multicolumn{1}{l}{CMTRV} \\
& 1.006 & 0.998*** & 1.028*** & 1.022 & 1.012 & 0.965*** & 0.970 & 0.990 \\			

\midrule
\multicolumn{9}{c}{rolling window size = 72}\\
\midrule

\multicolumn{1}{l}{$HS$} & RV    & BPV   & BPV   & TRV   & TRV   & TRV   & \multicolumn{1}{l}{JV} & \multicolumn{1}{l}{TRV} \\
& 0.849*** & 0.779*** & 0.710*** & 0.561*** & 0.477*** & 0.463*** & 0.387 & 0.487 \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$IP$} & MAC   & CMRV2 & MVBPV & MVRV  & MVRV  & MVRV  & \multicolumn{1}{l}{MAC} & \multicolumn{1}{l}{CMJV} \\
& 0.954*** & 0.985*** & 0.890*** & 0.924*** & 0.956*** & 0.912*** & 0.838 & 0.954 \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$PAY$} & MAC   & VTRV  & VJV   & VTRV  & VBPV  & RV    & \multicolumn{1}{l}{TRV} & \multicolumn{1}{l}{MAC} \\
& 0.832*** & 0.931*** & 0.837*** & 0.795*** & 0.788*** & 0.678*** & 0.639 & 0.991 \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$CPI$} & CMRV1 & CMTRV2 & CMBPV2 & CMRV1 & CMRV2 & CMJV2 & \multicolumn{1}{l}{VJV} & \multicolumn{1}{l}{CMBPV} \\
& 0.980*** & 1.000*** & 1.007 & 0.993*** & 0.949*** & 1.001** & 0.941 & 0.902 \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$PCE$} & CMBPV2 & CMTRV2 & MVRV  & MVTRV & MVBPV & MAC   & \multicolumn{1}{l}{CMBPV} & \multicolumn{1}{l}{CMRV} \\
& 0.977*** & 1.008 & 0.991*** & 1.025 & 0.948*** & 0.952*** & 0.974 & 0.996 \\
&       &       &       &       &       &       &       &  \\

\multicolumn{1}{l}{$SI$} & CMBPV1 & CMJV2 & CMBPV2 & CMJV1 & CMTRV2 & CMTRV1 & \multicolumn{1}{l}{CMTRV2} & \multicolumn{1}{l}{VBPV} \\
& 0.946*** & 1.001 & 0.991*** & 1.008 & 0.984*** & 0.985*** & 1.017 & 1.005 \\

\bottomrule
\end{tabular}%
	\begin{tablenotes}[flushleft]
	\scriptsize
	\item[1] See notes to Table RR1 and Table 5A in the main paper.
\end{tablenotes}			
\end{threeparttable}
\end{table}


%---------------------------------------------------------------

\newpage
\newgeometry{top=2cm, bottom=2cm}
\renewcommand{\thetable}{RR3B} 

\begin{table}[h]
\centering
\caption{MSFE-Best Models (Sample 2: 2009:1 - 2018:12)} 
\label{table:tableRR3B}
\begin{threeparttable}
\scriptsize
%\footnotesize
\begin{tabular}{lllllllll}
\toprule
\multicolumn{1}{c}{\multirow{2}[0]{*}{Targets}} & \multicolumn{8}{c}{Forecast horizon}\\
&   1-month &  2-month &3-month &4-month &5-month &  6-month &12-month &  24-month \\
\midrule
\multicolumn{9}{c}{rolling window size = 36}\\
\midrule

$HS$  & TRV   & VJV   & CMTRV1 & BPV   & VJV   & CMBPV1 & CMBPV & TRV \\
& 0.950*** & 0.818*** & 0.927*** & 0.910*** & 0.966*** & 0.920*** & 1.072 & 0.951 \\
&       &       &       &       &       &       &       &  \\
$IP$  & CMTRV1 & MVJV  & MVRV  & CMRV2 & CMJV2 & TRV   & MVBPV & VRV \\
& 0.931*** & 0.876*** & 0.956*** & 1.018 & 0.975*** & 0.975*** & 0.715 & 0.971 \\
&       &       &       &       &       &       &       &  \\
$PAY$ & CMRV2 & VJV   & CMRV1 & CMTRV1 & MAC   & CMJV2 & CMJV2 & RV \\
& 0.828*** & 1.04  & 0.996*** & 0.910*** & 0.993*** & 0.994*** & 0.987 & 0.909 \\
&       &       &       &       &       &       &       &  \\
$CPI$ & CMJV2 & VJV   & CMTRV2 & CMJV1 & CMRV1 & VBPV  & VBPV  & MVBPV \\
& 1.015*** & 0.988*** & 0.986*** & 0.946*** & 0.954*** & 1.043 & 1.011 & 0.887 \\
&       &       &       &       &       &       &       &  \\
$PCE$ & CMRV2 & CMRV2 & CMJV2 & CMJV2 & VRV   & CMTRV1 & CMTRV & MVTRV \\
& 0.992*** & 0.977*** & 1.011 & 1.016 & 0.992*** & 0.962*** & 0.997 & 0.884 \\
&       &       &       &       &       &       &       &  \\
$SI$  & CMJV2 & CMJV2 & VJV   & CMJV2 & CMTRV2 & CMJV2 & CMTRV2 & CMBPV2 \\
& 1.036 & 1.013*** & 1.012 & 1.028*** & 0.993*** & 0.976*** & 0.808 & 0.993 \\

\midrule
\multicolumn{9}{c}{rolling window size = 72}\\
\midrule

$HS$  & CMJV1 & CMTRV1 & VBPV  & CMTRV1 & VBPV  & MAC   & CMTRV2 & CMTRV2 \\
& 0.938*** & 0.927*** & 0.955*** & 0.951*** & 0.947*** & 0.949*** & 0.972 & 0.818 \\
&       &       &       &       &       &       &       &  \\
$IP$  & MAC   & TRV   & MVBPV & VRV   & CMJV1 & MVJV  & MAC   & MAC \\
& 0.950*** & 0.962*** & 0.972*** & 0.963*** & 0.963*** & 0.938*** & 0.760 & 0.983 \\
&       &       &       &       &       &       &       &  \\
$PAY$ & CMTRV2 & CMJV2 & CMRV2 & CMJV2 & MRV   & VTRV  & CMTRV2 & CMRV \\
& 0.864*** & 1.048* & 0.975*** & 0.957*** & 0.902*** & 0.953*** & 0.995 & 0.942 \\
&       &       &       &       &       &       &       &  \\
$CPI$ & CMRV1 & CMTRV2 & CMBPV2 & CMRV2 & CMRV2 & TRV   & CMBPV2 & CMBPV \\
& 0.970*** & 0.993*** & 0.985*** & 0.983*** & 0.946*** & 0.995*** & 0.988 & 0.915 \\
&       &       &       &       &       &       &       &  \\
$PCE$ & MVJV  & CMTRV2 & MVRV  & MVBPV & MVBPV & MAC   & CMJV2 & CMBPV \\
& 0.979*** & 0.994*** & 0.934*** & 0.962*** & 0.894*** & 0.858*** & 0.956 & 0.985 \\
&       &       &       &       &       &       &       &  \\
$SI$  & CMBPV1 & CMJV2 & CMBPV2 & MAC   & CMRV2 & CMTRV1 & CMTRV2 & VBPV \\
& 0.853*** & 1.000*** & 0.982*** & 0.948*** & 0.987*** & 0.943*** & 0.970 & 1.014 \\

\bottomrule
\end{tabular}%	
	\begin{tablenotes}[flushleft]
	\scriptsize
	\item[1] See notes to Table RR1 and Table 5A in the main paper.
\end{tablenotes}		
\end{threeparttable}
\end{table}


%---------------------------------------------------------------



\newpage




\renewcommand{\baselinestretch}{1.0}%

%\nocite{*}
\bibliographystyle{agsm}
\bibliography{draft4bib2}

		\end{document}			
